### 2020-12-24 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/content.tex
Structured Changes and file settings

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                            %%
%% The Main Body begins here                  %%
%%                                            %%
%% Please refer to the instructions for       %%
%% authors on:                                %%
%% https://www.biomedcentral.com/getpublished %%
%% and include the section headings           %%
%% accordingly for your article type.         %%
%%                                            %%
%% See the Results and Discussion section     %%
%% for details on how to create sub-sections  %%
%%                                            %%
%% use \cite{...} to cite references          %%
%%  \cite{koon} and                           %%
%%  \cite{oreg,khar,zvai,xjon,schn,pond}      %%
%%                                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
% <put your article body there>

\input{introduction}
\input{relatedwork}

\section*{Content}
Text and results for this section, as per the individual journal's instructions for authors.

\section*{Section title}
Text for this section\ldots
\subsection*{Sub-heading for section}
Text for this sub-heading\ldots
\subsubsection*{Sub-sub heading for section}
Text for this sub-sub-heading\ldots
\paragraph*{Sub-sub-sub heading for section}
Text for this sub-sub-sub-heading\ldots

In this section we examine the growth rate of the mean of $Z_0$, $Z_1$ and $Z_2$. In
addition, we examine a common modeling assumption and note the
importance of considering the tails of the extinction time $T_x$ in
studies of escape dynamics.
We will first consider the expected resistant population at $vT_x$ for
some $v>0$, (and temporarily assume $\alpha=0$)
%
\[
E \bigl[Z_1(vT_x) \bigr]=
\int_0^{v\wedge
1}Z_0(uT_x)
\exp (\lambda_1)\,du .
\]
%
If we assume that sensitive cells follow a deterministic decay
$Z_0(t)=xe^{\lambda_0 t}$ and approximate their extinction time as
$T_x\approx-\frac{1}{\lambda_0}\log x$, then we can heuristically
estimate the expected value as
%
\begin{equation}\label{eqexpmuts}
\begin{aligned}[b]
&      E\bigl[Z_1(vT_x)\bigr]\\
&\quad      = \frac{\mu}{r}\log x
\int_0^{v\wedge1}x^{1-u}x^{({\lambda_1}/{r})(v-u)}\,du .
\end{aligned}
\end{equation}
%
Thus we observe that this expected value is finite for all $v>0$ (also see \cite{koon,xjon,marg,schn,koha,issnic}).

\section*{Appendix}
Text for this section\ldots

### 2020-12-24 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
Structured Changes and file settings

\section*{Introduction}
Data and Information modeling in the healthcare domain have witnessed significant improvements in the last decade owing to advances in the development of state-of-the-art information and communication technologies (ICT) and formalization of storage and messaging standards. Subsequently, the scope of Healthcare Management Information Systems (HMIS), medical ontologies, and Clinical Decision Support Systems (CDSS) has broadened, beyond the operational capabilities of traditional rule based systems.

### 2020-12-25 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/relatedwork.tex
related work updated

\section*{Related Work}
Althubait et al. \cite{althubaiti2020combining} proposed an ontology expansion methodology that identifies and extracts new class from text articles using word embedding and machine learning techniques. The authors identified the similarity of tokens and phrases of the text articles with the exiting classes of the ontology. The target ontology is expanded with classes from text articles having greater similarity with that of already added classes. A similar word embedding technique was also used by Nozaki et al. \cite{nozaki2019semantic}, where the authors used instance based schema matching technique to identify the semantic similarity between two instances. The results of the study showed the possibility of detecting similar string attributes of different schemas. Yousfi et al. \cite{yousfi2020xmatcher} also utilized semantic base techniques and proposed xMatcher XML schemas matching approach. xMatcher transforms schemas into a set of words, followed by measuring words context, and relatedness score using WordNet. The terms from different schemas having similarities greater or equal to 0.8 are considered similar.

Kersloot et al. \cite{kersloot2020natural} performed a comprehensive systematic review to evaluate natural language processing (NLP) algorithms used for clinical text mapping onto ontological concepts. The findings of the studies were evaluated with respect to five categories; use of NLP algorithms, data used, validation and evaluation performed, result presentation, and generalization of results. The authors revealed that over one-fourth of the NLP algorithms used were not evaluated and have no validation. The systems that claimed generalization, were self evaluated and having no external validation.

### 2020-12-25 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/relatedwork.tex
related changes

@@
 The terms from different schemas having similarities greater or equal to 0.8 are considered similar.
+Bylygin et al.
+\cite{bulygin2018combining} devised an ontology and schema matching approach by combining lexical and semantic similarity with machine learning approaches.
+The authors used lexical and semantic measures as features and trained various machine learning algorithms including Naive Bayes, logistic regression, and gradient boosted tree.
+The result achieved showed that the combination of algorithms outperformed the single modal.
 

### 2020-12-28 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
intro 2

@@
 Subsequently, the scope of Healthcare Management Information Systems (HMIS), medical ontologies, and Clinical Decision Support Systems (CDSS) has broadened, beyond the operational capabilities of traditional rule based systems.
+One of the major reasons behind this limitation is due to the numerous heterogeneities in healthcare at data, knowledge, and process level.
+Thus, healthcare interoperability which aims to provide a solution to this problem, can be compartmentalized into data interoperability, process interoperability, and knowledge interoperability.
+Data interoperability resolves the heterogeneity between data artificats, to enable, seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International HL7, and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
+On the other hand, process interoperability regulates the communication among organizational processes to provide compatability between process artifacts within and seamless transformations across different organizations\cite{khan2013process}.
+Lastly, knowledge interoperability provides a sharing mechanism for reusing interpretable medical knowledge, acquired through expert intervention and other mechanisms, across decision support systems \cite{ali2017multi}.
+
+Additionally, the operational capabilities of the current healthcare service delivery infrastructure has gone under tremendous stress due to Covid 19.
+World over, large primary healthcare units have managed to create separate units for managing patients, suffering from extreme cases of the novel coronavirus.
+For secondary and tertiary care units, government involvement has become necessary to filter coronavirus patients and adhering to a national pandemic response policy.
+These complex circumstances have enhanced the need for sharing patient data and state-of-the-art medical knowledge in real-time, to provide the Epidemiologists and other medical experts with a tool to make accurate and timely decisions.
+
+pharmacists and vaccinologists 
+Under these complex circumstances, a technical solution for healthcare interoperability, has become all the more necessary. While the standardization efforts by CIMI, SNOMED-CT, LOINC, yosemite group

### 2020-12-28 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
intro 3

@@
 
-Additionally, the operational capabilities of the current healthcare service delivery infrastructure has gone under tremendous stress due to Covid 19.
+In more tangible terms, healthcare interoperability at data, process, and knowledge level can be exemplified within the healthcare constraints experienced due to the emergence of Covid 19.
+The operational capabilities of the current healthcare service delivery infrastructure has gone under tremendous stress due to Covid 19.
 World over, large primary healthcare units have managed to create separate units for managing patients, suffering from extreme cases of the novel coronavirus.
 For secondary and tertiary care units, government involvement has become necessary to filter coronavirus patients and adhering to a national pandemic response policy.
-These complex circumstances have enhanced the need for sharing patient data and state-of-the-art medical knowledge in real-time, to provide the Epidemiologists and other medical experts with a tool to make accurate and timely decisions.
+These complex circumstances have enhanced the need for sharing patient data and state-of-the-art medical knowledge in real-time, to provide the medical experts with a tool to make accurate and timely decisions.
+Data interoperability can enable the front line medical workers to fetch, understand, and use patient data, especially comorbidities, across organizational and physical boundaries, without suffering from societal taboos that may prevent the patient from sharing their complete and accurate medical histories.
+Knowledge interoperability can improve the knowledge acquisition and sharing protocols to provide the medical experts such as epidieomologists and vaccinologist, with latest information on affected population trends, disease diagnosis, treatment, and followup procedures, and interpretable decisions leading to positive or negative outcomes.
+Process interoperability can help reduce and in some cases remove the operational redundancies between health centers.
+In this way, successive healthcare treatments can take benefit from earlier diagnosis, treatment, and followup procedures, thereby reducing the stress on healthcare experts and systems.
+
+Standards such as HL7 and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols such as HL7-FHIR, or the older HL7v2  HL7 v3.
+While Snomed-CT and LOINC provide a standard definition for clinical terminologies and lab tests, respectively.
+Similarly Medical Logic Module (MLM) provides a standardized way for expressing medical knowledge.
+However, the plethora of standards,n necessitates the creation of bridging standards, that can resolve the heterogeniety between medical standards.
+In this regard, CIMI has
+
+Cimi and Yosemite
+
+Uhp, previous paper
 

### 2020-12-28 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/content.tex
related work updated

@@
 \input{relatedwork}
-
-\section*{Content}
-Text and results for this section, as per the individual journal's instructions for authors.
-
-\section*{Section title}
-Text for this section\ldots
-\subsection*{Sub-heading for section}
-Text for this sub-heading\ldots
-\subsubsection*{Sub-sub heading for section}
-Text for this sub-sub-heading\ldots
-\paragraph*{Sub-sub-sub heading for section}
-Text for this sub-sub-sub-heading\ldots
-
-In this section we examine the growth rate of the mean of $Z_0$, $Z_1$ and $Z_2$. In
-addition, we examine a common modeling assumption and note the
-importance of considering the tails of the extinction time $T_x$ in
-studies of escape dynamics.
-We will first consider the expected resistant population at $vT_x$ for
-some $v>0$, (and temporarily assume $\alpha=0$)
-%
-\[
-E \bigl[Z_1(vT_x) \bigr]=
-\int_0^{v\wedge
-1}Z_0(uT_x)
-\exp (\lambda_1)\,du .
-\]
-%
-If we assume that sensitive cells follow a deterministic decay
-$Z_0(t)=xe^{\lambda_0 t}$ and approximate their extinction time as
-$T_x\approx-\frac{1}{\lambda_0}\log x$, then we can heuristically
-estimate the expected value as
-%
-\begin{equation}\label{eqexpmuts}
-\begin{aligned}[b]
-&      E\bigl[Z_1(vT_x)\bigr]\\
-&\quad      = \frac{\mu}{r}\log x
-\int_0^{v\wedge1}x^{1-u}x^{({\lambda_1}/{r})(v-u)}\,du .
-\end{aligned}
-\end{equation}
-%
-Thus we observe that this expected value is finite for all $v>0$ (also see \cite{koon,xjon,marg,schn,koha,issnic}).
-
-\section*{Appendix}
-Text for this section\ldots

### 2020-12-28 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/relatedwork.tex
related work updated

@@
 
+Alwan et al.
+\cite{alwan2017survey} have summarized the techniques used in the literature for schemas and instances based schema matching.
+The information used for schema matching is categories into  schema information, instance and auxiliary information.
+Most of the searchers have used syntactic techniques (including n-gram, and regular expression), semantic techniques (including Latent Semantic Analysis, WordNet/Thesaurus and Google Similarity) for schema level and instance level matching to achieve the final goal of data/information interoperability.
 Kersloot et al.

### 2020-12-28 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
intro 4
intro 5

@@
 
-Standards such as HL7 and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols such as HL7-FHIR, or the older HL7v2  HL7 v3.
-While Snomed-CT and LOINC provide a standard definition for clinical terminologies and lab tests, respectively.
+Standards such as Health Level Seven (HL7) Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
+While systematized nomenclature of medicine—clinical terms (Snomed-CT) \cite{snomedct_url} and logical observation identifiers names and codes (LOINC) \cite{loinc} provide a standard definition for clinical terminologies and laboratory tests, respectively.
 Similarly Medical Logic Module (MLM) provides a standardized way for expressing medical knowledge.
-However, the plethora of standards,n necessitates the creation of bridging standards, that can resolve the heterogeniety between medical standards.
-In this regard, CIMI has
-
-Cimi and Yosemite
+However, the plethora of standards, necessitates the creation of bridging standards, that can resolve the heterogeniety between the medical standards.
+Substantial effort has gone into this endeavor with the Clinical Information Modeling Initiative (CIMI) \cite{CIMI2015} taking the lead in bridging the gap between HL7v3 and openEHR.
+Similarly, SNOMED CT and LOINC are working to resolve the redundancies between the two terminological standards since 2013.
+This healthcare interoperability solution follows a formal, albiet long process, which is greatly dependent on the human factor.
+However, the current healthcare scenario, requires a quick solution to create a scaffolding of an interoperable bridge between various healthcare providers.
+It is also important to ensure that this scaffolding should be able to support the formal standardization processes of the future.
+In \cite{Satti2020}we have presented the Ubiquitous Health Platform (UHP), which provides semantic reconciliation-on-read based data curation for resolving data interoperability between various schema.
 
 Uhp, previous paper
-
-pharmacists and vaccinologists 
-Under these complex circumstances, a technical solution for healthcare interoperability, has become all the more necessary. While the standardization efforts by CIMI, SNOMED-CT, LOINC, yosemite group

### 2020-12-28 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/relatedwork.tex
related work changed

@@
 
+Martono et al.
+\cite{martono2017review} provided overview of previous studies related to linguistic approaches used for schema matching.
+Linguistic methods focused on finding strings and evaluate there similarity in different schemas.
+The string are normally normalized before to align both the strings before similarity comparison.
+The normalized strings are categories based on the information relatedness and element with similar category are compared using various similarity measure including  Jaro-distance, Lavenstein (edit-distance), and many more.
 Alwan et al.

### 2020-12-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
intro 7

@@
 \section*{Introduction}
+\label{intro}
 Data and Information modeling in the healthcare domain have witnessed significant improvements in the last decade owing to advances in the development of state-of-the-art information and communication technologies (ICT) and formalization of storage and messaging standards.
@@
 Lastly, knowledge interoperability provides a sharing mechanism for reusing interpretable medical knowledge, acquired through expert intervention and other mechanisms, across decision support systems \cite{ali2017multi}.
-
 In more tangible terms, healthcare interoperability at data, process, and knowledge level can be exemplified within the healthcare constraints experienced due to the emergence of Covid 19.
@@
 In this way, successive healthcare treatments can take benefit from earlier diagnosis, treatment, and followup procedures, thereby reducing the stress on healthcare experts and systems.
-
 Standards such as Health Level Seven (HL7) Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
@@
 In \cite{Satti2020}we have presented the Ubiquitous Health Platform (UHP), which provides semantic reconciliation-on-read based data curation for resolving data interoperability between various schema.
+This methodology is based on the creation and management of schema maps, that can provide the framework for transforming a source schema into a target schema.
+In the current manuscript, we will present our research work to build and manage the schema map knowledge base.
+Overall, our methodology has two major portions, firstly we apply a novel schema matching technique to create a transformation function $\sigma$ for the participating legacy schema, and secondly, we have used the Ripple Down Rules (RDR)  to manage our knwoledgebase, which will be presented in some detail, focusing primarily on the search and evolution services.
+In particular,
 
-Uhp, previous paper
+Section 2 contains the details of our methodology, where we aim to present a reproducible theoretical framework.
+
+Section 3 provides the experimental setup
+
+Section 4 presents the results
+
+Section \ref{relatedwork} presents the related work
+
+Section 6 concludes the paper.

### 2020-12-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
intro 8

@@
 
-Section 2 contains the details of our methodology, where we aim to present a reproducible theoretical framework.
-
-Section 3 provides the experimental setup
-
-Section 4 presents the results
-
-Section \ref{relatedwork} presents the related work
-
-Section 6 concludes the paper.
+\begin{itemize}
+\item[$-$] Section 2 contains the details of our methodology, where we aim to present a reproducible theoretical framework.
+\item[$-$] Section 3 provides the experimental setup
+\item[$-$] Section 4 presents the results
+\item[$-$] Section \ref{relatedwork} presents the related work
+\item[$-$] Section 6 concludes the paper.
+\end{itemize}

### 2020-12-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
add new section pages

\section*{Experimental Setup}
\label{experimentalSetup}
Experimental Setup goes here ....

### 2020-12-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
add new section pages

\section*{Methodology}
\label{methodology}
Methodology goes here ....

### 2020-12-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
add new section pages

\section*{Results}
\label{results}
Results goes here ....

### 2021-01-06 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
on ubuntu
methodology 0

@@
 \label{methodology}
+Healthcare interoperability, with a focus on non-standard compliant medical schema, is dependent on the generation and validation of schema maps, as discussed above.
+To this end, the creation of a cohesive workflow is of utmost importance.
+As a possible realization of this aim, and from a purely practical point of view, our methodology is presented in the following subsections.
+
+\subsection*{Schema acquisition}
+\label{schema_acq}
+In the first step of our semantic reconciliation methodology, we collect medical schema from three distinct information systems.
+
+\subsection*{Schema preprocessing}
+\label{schema_prepro}
+The medical schemas and their instances are converted into an interpretable form with each attribute containining:
+
+schema name, attribute name, min value, max value, type, semantic types[]
+
 Methodology goes here ....

### 2021-01-12 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
Update methodology.tex

@@
 To this end, the creation of a cohesive workflow is of utmost importance.
-As a possible realization of this aim, and from a purely practical point of view, our methodology is presented in the following subsections.
+In our earlier work \cite{Satti2020} we used maximum sequence identification and matching using suffix trees for syntactic matching of two distinctly sources data schemas.
+This was followed by semantic concept enrichment and subsequently concept matching, for creating rules in the form of schema maps.
+The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data, into a non-persisted, interpretable, model form.
+In our current methodology we have utilized state-of-the-art machine learning techniques for converting medical schemas into semi-structured form, which is then used to create embedding vectors.
+These vectors are then used for modeling and creating interpretable rules for applying semantic reconciliation in the form of schema matching and/or transformation.
+These rules are managed by the RDR which allows fast inference using the relevant knowledge sub-tree, and can well manage knowledge evolution to scale out (by incorporating new schema) and up (by incorporating changes and additions to existing schema)
+As a possible realization of this aim, and from a practical point of view, our methodology is presented in the following subsections.
 
@@
 \label{schema_acq}
-In the first step of our semantic reconciliation methodology, we collect medical schema from three distinct information systems.
+In the first step of our semantic reconciliation methodology, we collect medical schema from \textbf{three} distinct information systems. The include ....
 
-\subsection*{Schema preprocessing}
+\subsection*{Schema processing}
 \label{schema_prepro}

### 2021-01-12 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
manuscript updated

@@
 \label{schema_acq}
-In the first step of our semantic reconciliation methodology, we collect medical schema from \textbf{three} distinct information systems. The include ....
+In the first step of our semantic reconciliation methodology, we collect medical schema from five distinct EMR storage systems.
+These include patient reports from OpenEMR ($m_1$), 100,000 patient records from EMRBOTS ($m_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
+al($m_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($m_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($m_5$).
+In our earlier work \cite{Satti2020} $m_1$, $m_2$, and $m_3$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
+We extended the same setup to \textbf{further include}
 

### 2021-01-12 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 1

--- 2021-01-12 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
@@
 \label{schema_acq}
-In the first step of our semantic reconciliation methodology, we collect medical schema from \textbf{three} distinct information systems. The include ....
+In the first step of our semantic reconciliation methodology, we collect medical schema from five distinct EMR storage systems ($S$).
+These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
+al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$).
+These five schema follow relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
+Each of these schema, fulfills the need of their respective information processing applications, however the lack of interoperability is very much visible here.
+Here, heterogeneity is caused by various factors, including the lack of standard terminologies and different normalization level.
+While SNOMED-CT provides a mechanism for identifying the standard codes for clinical terms and LOINC can be used for laboratory related terms, most attribute names are created based on the gut feeling of the database designer.
+While this behavior is not wrong, it does create syntactic differences in the participating schema.
+Consider the terms ``name" and ``patientName", which refer to the same attribute of the patient entity, however there is no standard way to represent it, with both being correct.
+As a result, $m_1$ and $m_3$ use the former representation, while $m_2$ and $m_5$ use the latter.
+Differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others.
+Similarly, $m_1$ and $m_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $m_2$, $m_4$, $m_5$.
+Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for these EMR storage systems.
+In fact, the change in context of the EMR storage system from the initial time of development to a later stage of collaborative processing systems, is the main cause of heterogeneity.
+
+In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_3$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
+We extended the same setup to \textbf{further include}
 

### 2021-01-12 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 1.1

@@
 Consider the terms ``name" and ``patientName", which refer to the same attribute of the patient entity, however there is no standard way to represent it, with both being correct.
-As a result, $m_1$ and $m_3$ use the former representation, while $m_2$ and $m_5$ use the latter.
+As a result, $s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter.
 Differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others.
-Similarly, $m_1$ and $m_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $m_2$, $m_4$, $m_5$.
+Similarly, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, $s_5$.
 Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for these EMR storage systems.

### 2021-01-12 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 2

@@
 Differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others.
-Similarly, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, $s_5$.
+Similarly, ``EncounterDate" from $s_5$ is semantically similar to ``BeginDate" of ``openemr\_MedicalProblems" table in $s_1$, ``AdmissionStartDate" of ``LabsCorePopulatedTable" in $s_2$,
+``time" in ``Diagnosis" table of $s_3$, and  ``dateOfAdmission" in ``Diagnosis" and ``CareHistory" tables of $s_4$.
+Finally, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, $s_5$.
 Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for these EMR storage systems.
 In fact, the change in context of the EMR storage system from the initial time of development to a later stage of collaborative processing systems, is the main cause of heterogeneity.
+In order to provide an interoperable solution, it is therefore necessary to provide syntactic and semantic mappings, while taking the data instances (or tuples) into account.
 

### 2021-01-13 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex

@@
 In order to provide an interoperable solution, it is therefore necessary to provide syntactic and semantic mappings, while taking the data instances (or tuples) into account.
+Data instances are used to enrich the semantic context of an attribute ($a_i$) by establishing its probable data type and possible value set.
+In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_5$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
+We extended the same setup to \textbf{further include}
 
-In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_3$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
-We extended the same setup to \textbf{further include}
+In essence, the set of attribute ($A$) holds all unique attributes of all participating schema.
 

### 2021-01-15 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 3

@@
 These rules are managed by the RDR which allows fast inference using the relevant knowledge sub-tree, and can well manage knowledge evolution to scale out (by incorporating new schema) and up (by incorporating changes and additions to existing schema)
-As a possible realization of this aim, and from a practical point of view, our methodology is presented in the following subsections.
+In essence, the aim here is to define a uniqueness property ($\mathbb{P}$), as shown in Equation \eqref{uniquenessProp}, whereby the semantic and syntactic uniqueness of each attribute as a disjoint union, is used.
+
+\begin{equation}\label{uniquenessProp}
+range(\mathbb{P})= \tau_{syntatic} \uplus \tau_{semantic}
+\end{equation}
+
+The syntactic uniqueness as represented in Equation \eqref{synType}, is also a disjoint union of the measured attribute type, corresponding to one of integer, float, boolean, or string, and it valid values.
+The elements of the attribute type set have been determined based on the common primitive types available to the applications at an abstract level.
+While database schema used by EMR systems, correspond to the SQL datatypes\cite{SQLDataTypes}, the application of semantic reconciliation-on-read strategy, instead necessitates the usage of common programming primitive types.
+On the other hand, ``validValues" are determined based on what is contained in some sampled portion of the database.
+It is represented by the set of all possible categorical values (such as values of the attribute with type string which can be used to represent names, address, and others), the minimum and maximum values enclosed within open intervals (``\( \)") or closed intervals (``\[ \]") to represent a range of numerical values ( such as values of attributes with type float or integer ), and boolean values (such as values represented by 1/0 or True/False).
+\begin{equation}\label{synType}
+\tau_{syntatic}= \left \{ a \mid a \epsilon \left \{ \left \{ integer, float, boolean, string\right \} \uplus validValues \right \} \right \}
+\end{equation}
+
+The semantic type is represented by the Equation \eqref{semType}, which is the set of all concepts corresponding to the leaf nodes of the suffix tree, generated from the name of the attribute.
+Suffix trees are used to divide a string into components, which is a very useful base for quickly identifying the longest common subsequence between a pair of strings and data compression.
+In our case, these trees provide a manageable list of words, contained with the name of attribute.
+For each substring, represented by a path of the tree, we then identify the corresponding concept, if it exists, thereby producing a set of concepts which may represent the attribute.
+
+\begin{equation}\label{semType}
+\tau_{semantic}= \left \{b \mid b \epsilon \left \{ concept_{i,j} \mid i \leq width(suffixTree(b)) \wedge j \epsilon \left \{ substring_i \right \} \right \} \right \}
+\end{equation}
+
+Finally, the set of attribute ($A$) holds all unique attributes of participating schema, as shown in Equation \eqref{uniqueA}.
+For each element of this set, the attribute is unique if its properties from Equation \eqref{uniquenessProp}, are not similar to any other element of this set.
+The similarity function ``$\sim$" is a threshold based loose bound, on the disjoint elements of ``$\mathbb{P}$".
+
+\begin{equation}\label{uniqueA}
+\exists a \epsilon A \mid ( \mathbb{P}(a) \wedge \forall b \epsilon A \mid \mathbb{P}(b) \rightarrow a \sim b)
+\end{equation}
+
+As a possible realization of this theoretical set notation form, and from a practical point of view, our methodology is presented in the following subsections.
 
@@
 
-In essence, the set of attribute ($A$) holds all unique attributes of all participating schema.
-
 \subsection*{Schema processing}
 \label{schema_prepro}
-The medical schemas and their instances are converted into an interpretable form with each attribute containining:
 
-schema name, attribute name, min value, max value, type, semantic types[]
+In order to process the EMR schema set $S$, we use the methodology shown in \textbf{algorithm}.
+For each data representation $s_i$, we first serialize its tables into Comma Separated Value (CSV) formatted flat files.
+Each table has a separate file, which contains the attribute names in the header and the data instances (following the same format and CSV struture), in subsequent lines.
+Each file is loaded in memory and converted into an algorithmic iterable structure.
+For each attribute, we then generate the suffix tree, which provides all possible substring representations contained within the attribute name.
+Then for each node of this suffix tree, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS to retrieve its associated semantic concepts.
+\textbf{threshold}
+If atleast one semantic concepts is found for the substring, we enhance the suffix tree, to now store the substring and its associated semantic concepts.
+We continue this process, untill all substrings have been processed.
+This is followed by syntactic type check of the attribute, which is based on its data.
+Here we determine, if the attribute values correspond to one of Integer, Float, Boolean, or String types.
+Additionally, we collect the values of each corresponding data cell, and determine the set of possible values in each case.
+This semantic enrichment from UMLS concepts and syntactic enrichment from attribute types, is then saved into persistent storage for further processing.
 
-Methodology goes here ....
+Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
+The flat enriched schema, following the design shown in \textbf{enrichedSchemaPic} provides the input to our knowledge base, whose creation is described in the next section.
+
+\subsection*{Schema Map generation}
+\label{schema_map_gen}
+
+\subsection*{Schema Map evolution}
+\label{schema_map_evol}

### 2021-01-18 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
Update methodology.tex

@@
 \textbf{threshold}
-If atleast one semantic concepts is found for the substring, we enhance the suffix tree, to now store the substring and its associated semantic concepts.
+If atleast one semantic concepts is found for the substring, we replace the substring with these concepts, and discard the substring otherwise, creating the Suffix Concept Tree (SCT). 
+\textbf{Finally the equivalent embedding vector of each suffix's concept is placed in a structurally similar (to SCT)  tree embedding.
+}
 We continue this process, untill all substrings have been processed.
@@
 Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
-The flat enriched schema, following the design shown in \textbf{enrichedSchemaPic} provides the input to our knowledge base, whose creation is described in the next section.
+The flat enriched schema, following the design shown in \textbf{enrichedSchemaPic} provides the input to our knowledge base.
+The logical structure of the enriched attribute, is represented in \textbf{figAttributeRepresentation}.
+Here, the elements of this particular data-structure are categorized into three parts.
+``AttributeContext" contains the metadata conforming to an instance of the attribute's existence,  with its name, container table name and schema name, acting as a pointer, and schema version, source, and recorded date providing the version control features.
+In this manner, the attribute's fully qualified reference, along with its existential context is identified.
+``AttributeType" then encapsulates the data type features of this attribute's instances, with its primitive data type, and values providing a representation of the attribute's instance.
+Finally, ``Attribute Semantics" holds, the semantic information of this attribute, in the form of its suffix tree, SCT and Tree Embedding.
+A pair of this data-structure with distinct references, are then used as an input to the schema map generation process, which is explained in the next step.
 

### 2021-01-18 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 4

@@
 
-In order to process the EMR schema set $S$, we use the methodology shown in \textbf{algorithm}.
+In order to process the EMR schema set $S$, we use the methodology shown in \textbf{figAlgorithm}.
 For each data representation $s_i$, we first serialize its tables into Comma Separated Value (CSV) formatted flat files.
@@
 \textbf{threshold}
-If atleast one semantic concepts is found for the substring, we replace the substring with these concepts, and discard the substring otherwise, creating the Suffix Concept Tree (SCT). 
-\textbf{Finally the equivalent embedding vector of each suffix's concept is placed in a structurally similar (to SCT)  tree embedding.
-}
-We continue this process, untill all substrings have been processed.
+If atleast one semantic concept is found for the substring, we replace the substring with the \textbf{most relevant} concept, creating the Suffix Concept Tree (SCT).
+The SCT is structurally smaller than or equal to the suffix tree, since all suffix which are smaller than 2 and those without a qualifying semantic concept, are discarded.
+Finally for each node of the SCT, the substring from the suffix tree and its corresponding concept is placed into a sentence, which is converted into an embedding vector using \textbf{BioBERT}.
+This embedding vector represents the domain qualified semantics of the source attribute.
+
+We continue this process, until all substrings have been processed.
 This is followed by syntactic type check of the attribute, which is based on its data.
@@
 Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
-The flat enriched schema, following the design shown in \textbf{enrichedSchemaPic} provides the input to our knowledge base.
+The flat enriched schema, following the design shown in \textbf{figenrichedSchemaPic} provides the input to our knowledge base.
 The logical structure of the enriched attribute, is represented in \textbf{figAttributeRepresentation}.

### 2021-01-18 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 5

@@
 For each attribute, we then generate the suffix tree, which provides all possible substring representations contained within the attribute name.
-Then for each node of this suffix tree, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS to retrieve its associated semantic concepts.
-\textbf{threshold}
-If atleast one semantic concept is found for the substring, we replace the substring with the \textbf{most relevant} concept, creating the Suffix Concept Tree (SCT).
+Then for each node of this suffix tree, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS with approximate search strategy.Using Lexical Variant Generation (LVG) this strategy retrieves an expanded list of associated semantic concepts.
+If atleast one semantic concept is found for the substring, we replace the substring with the most relevant concept, based on the highest value of the confidence measure, creating the Suffix Concept Tree (SCT).
 The SCT is structurally smaller than or equal to the suffix tree, since all suffix which are smaller than 2 and those without a qualifying semantic concept, are discarded.
@@
 Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
-The flat enriched schema, following the design shown in \textbf{figenrichedSchemaPic} provides the input to our knowledge base.
+The flat enriched schema, following the design shown in \textbf{figEnrichedSchema} provides the input to our knowledge base.
 The logical structure of the enriched attribute, is represented in \textbf{figAttributeRepresentation}.

### 2021-01-18 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 5.1

@@
 On the other hand, ``validValues" are determined based on what is contained in some sampled portion of the database.
-It is represented by the set of all possible categorical values (such as values of the attribute with type string which can be used to represent names, address, and others), the minimum and maximum values enclosed within open intervals (``\( \)") or closed intervals (``\[ \]") to represent a range of numerical values ( such as values of attributes with type float or integer ), and boolean values (such as values represented by 1/0 or True/False).
+It is represented by the set of all possible categorical values (such as values of the attribute with type string which can be used to represent names, address, and others), the minimum and maximum values enclosed within open intervals (``( )") or closed intervals (``[ ]") to represent a range of numerical values ( such as values of attributes with type float or integer ), and boolean values (such as values represented by 1/0 or True/False).
 \begin{equation}\label{synType}

### 2021-01-18 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
Update methodology.tex

@@
 
-Finally, the set of attribute ($A$) holds all unique attributes of participating schema, as shown in Equation \eqref{uniqueA}.
+Finally, the set $AA$ of Amplified Attribute (AA), holds all unique attributes of participating schema, as shown in Equation \eqref{uniqueA}.
 For each element of this set, the attribute is unique if its properties from Equation \eqref{uniquenessProp}, are not similar to any other element of this set.
@@
 \begin{equation}\label{uniqueA}
-\exists a \epsilon A \mid ( \mathbb{P}(a) \wedge \forall b \epsilon A \mid \mathbb{P}(b) \rightarrow a \sim b)
+\exists a \epsilon AA \mid ( \mathbb{P}(a) \wedge \forall b \epsilon AA \mid \mathbb{P}(b) \rightarrow a \sim b)
 \end{equation}
@@
 The flat enriched schema, following the design shown in \textbf{figEnrichedSchema} provides the input to our knowledge base.
-The logical structure of the enriched attribute, is represented in \textbf{figAttributeRepresentation}.
-Here, the elements of this particular data-structure are categorized into three parts.
+The logically amplified structure of the attribute, AA, is represented in \textbf{figAttributeRepresentation}.
+Here, the elements of AA are categorized into three parts.
 ``AttributeContext" contains the metadata conforming to an instance of the attribute's existence,  with its name, container table name and schema name, acting as a pointer, and schema version, source, and recorded date providing the version control features.
@@
 Finally, ``Attribute Semantics" holds, the semantic information of this attribute, in the form of its suffix tree, SCT and Tree Embedding.
-A pair of this data-structure with distinct references, are then used as an input to the schema map generation process, which is explained in the next step.
+A pair of AA's with distinct references, are then used as an input to the schema map generation process, which is explained in the next step.
 

### 2021-01-19 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 5.2

@@
 \begin{equation}\label{synType}
-\tau_{syntatic}= \left \{ a \mid a \epsilon \left \{ \left \{ integer, float, boolean, string\right \} \uplus validValues \right \} \right \}
+\tau_{syntatic}= \left \{ t \mid t \epsilon \left \{ \left \{ integer, float, boolean, string\right \} \uplus validValues \right \} \right \}
 \end{equation}
@@
 \begin{equation}\label{semType}
-\tau_{semantic}= \left \{b \mid b \epsilon \left \{ concept_{i,j} \mid i \leq width(suffixTree(b)) \wedge j \epsilon \left \{ substring_i \right \} \right \} \right \}
+\tau_{semantic}= \left \{s \mid s \epsilon \left \{ concept_{i,j} \mid i \leq width(suffixTree(s)) \wedge j \epsilon \left \{ substring_i \right \} \right \} \right \}
 \end{equation}
@@
 \label{schema_map_gen}
+%Schema Maps, provide an interoperable bridge between two medical systems, by identifying the links between their participating attributes.
+This identification is based on the schema matching process, which process the cartesian product  of the two systems (le$).
+
+attribute set of bothTheoretically, for ``n" attributes in $s_i$ and ``m" attributes in $s_j$
 

### 2021-01-19 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 6

@@
 \label{schema_map_gen}
-%Schema Maps, provide an interoperable bridge between two medical systems, by identifying the links between their participating attributes.
-This identification is based on the schema matching process, which process the cartesian product  of the two systems (le$).
+Schema Maps, provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the links between their participating attributes.
+This identification is based on the schema matching process, shown in Algorithm \ref{knowledgeEvolAlgo}, which operates on a pair of amplified attributes, $\left ( aa_i,aa_j \right ) \mid aa_i \epsilon s_i \wedge aa_j \epsilon s_j$, and calculates the similarity score $S$.
 
-attribute set of bothTheoretically, for ``n" attributes in $s_i$ and ``m" attributes in $s_j$
+\begin{algorithm}
+	\textbf{Input}: AmplifiedAttributes $ aa_i, aa_j$ \\
+	\textbf{Output}: Similarity $S$ 
+	\begin{algorithmic}[1]
+		\State Similarity $S = 0$;
+		\If{$aa_i.AttributeContext == aa_j.AttributeContext$}:
+		\State $S = 1$;
+		\Else
+		% Checking Attribute Type
+		\State Syntactic Similarity $SynSim = 0 $
+		\State $at_i = aa_i.AttributeType$
+		\State $at_j = aa_j.AttributeType$
+
+		\If{$(at_i.DataType == at_j.DataType) || (at_i.DataType \Leftrightarrow at_j.DataType)$}: 
+		\State	$SynSim = 0.5$
+		\EndIf
+		\State Semantic Similarity $SemSim = 0 $
+		\State $\vec{ae_i} =  aa_i.Attribute Semantics
+		.TreeEmbedding$
+		\State $\vec{ae_j} =  aa_j.Attribute Semantics
+		.TreeEmbedding$
+
+		\State $SemSim = \frac{\vec{ae_i} \cdot \vec{ae_j}}{\|\vec{ae_i}\|\|\vec{ae_j}\|}$
+
+		\State $S = (0.5 * SynSim) + (0.5 * SemSim) $
+		\EndIf
+
+		\State return $S$
+		\caption{Attributes similarity identifier}
+		\label{knowledgeEvolAlgo}
+	\end{algorithmic}
+\end{algorithm}
 

### 2021-01-21 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 7

@@
 \label{schema_prepro}
-
+\textbf{metadata}
 In order to process the EMR schema set $S$, we use the methodology shown in \textbf{figAlgorithm}.
@@
 		\If{$(at_i.DataType == at_j.DataType) || (at_i.DataType \Leftrightarrow at_j.DataType)$}: 
-		\State	$SynSim = 0.5$
+		\State	$SynSim = 1$
 		\EndIf
@@
 
+This algorithmic process starts by comparing the metadata context of the two amplified attributes.
+The schema name, table name, attribute name, and version are used to establish the context of each attribute, which are then evaluated based on naive string matching of corresponding elements.
+If the pair refer to the same instance of the amplified attribute the process simply returns 1 as the similarity score.
+If however, the amplified attribute refer to separate instances, we then apply syntactic and semantic similarity on the pair.
+Firstly we compare the datatypes of the pair, to determine if they either have the same datatype or the datatypes are convertible.
+In our current approach \textit{float} and \textit{integer} datatypes are considered convertible, however this step is very much implementation specific and can be extended when the set of types is enhanced with newer data types, such as \textit{short} is convertible to \textit{integer} and vice versa, \textit{bit} is convertible to \textit{boolean} and vice versa, and so on.
+This test is used to set the ``SynSim" score to ``1", if the datatypes are equal or convertible, and ``0" otherwise.
+Secondly, we compare the semantic concepts of the two amplified attributes, by applying \textbf{cosine} similarity between their embedding vectors.
+Since the embedding vector is based on the amalgamation of the suffix strings and their corresponding suffix concepts, \textbf{cosine similarity can give a good measure of the direction of these vectors}.
+``SemSim", thereby obtained is then used in conjuction with previously obtained ``SynSim" to calculate the similarity of the two amplified attributes.
+Using equal weights for syntactic and semantic similarity, we then re-scale their individual values to finally provide a similarity score between ``0" and ``1".
+
 \subsection*{Schema Map evolution}

### 2021-01-28 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 8

@@
 
+The schema matching approach represented above, can be further improved by enwrapping the individual calls with memoization, which can avoid redundant checks.
+However, in practical terms, the creation of the schema map between two amplified attributes is rarer than its application to transform or link two distinct schemas.
+Additionally, just like its other schema/ontology matching counterparts, the presented Algorithm \ref{knowledgeEvolAlgo}, applies a one-way compression on the various matched factors to produce a similarity measure/ indicator.
+This operation is very useful for building unsupervised and semi-supervised automated systems, which base their decisions on a measured confidence score.
+However, in the healthcare domain, knowledge acquisition and application process, requires the use of supervised automated systems, which can provide strong traceability for the decision making process.
+Summarily, it is not enough for our schema matching process to simply return $S$.
+
+This is where, Ripple Down Rules (RDR) knowledge base, steps in.
+RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules.
+As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm.
+
 \subsection*{Schema Map evolution}

### 2021-01-29 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
Add Related work, RDR pic and references

@@
 This is where, Ripple Down Rules (RDR) knowledge base, steps in.
-RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules.
+RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules \cite{compton1992ripple, richards2009two, kim2018rdr}.
 As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm.

### 2021-01-29 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/relatedwork.tex
intro 7
on ubuntu
change attribute Rpresenation diagrame
Algorithm set
Add Related work, RDR pic and references

@@
 \section*{Related Work}
+\label{relatedwork}
 Althubait et al.
@@
 The systems that claimed generalization, were self evaluated and having no external validation.
+
+Xu et al.
+\cite{xu2003discovering} presented a framework for discovering indirect links besides direct links among schema elements.
+The indirect matches were detected for relations such as union, composition, decomposition, selection, and boolean.
+The indirect links are useful to handle concepts merge, split, generalization, and specialization.
+The matching techniques utilized in the study considered terminological relationships (word synonym and hypernym), structural characteristics, data-value characteristics, and expected data values.
+The experimental results revealed framework effectiveness by achieving more than 90\% precision and recall for direct and indirect link matching.

### 2021-02-01 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 9

@@
 As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm.
+Beyond the root node of the RDR, which represents the default condition, at lower depths, syntactic matching characteristics are represented, while semantic matching characteristics, such as the concepts associated with semantic types, follow thereafter.
+``AttributeType" elements representing the data types of the attributes as ``string", ``integer", ``double", and ``boolean" are placed in the first case, followed by convertible types, such as the case where the attribute values, in the form of integers are placed in a string (``\textit{1}",``\textit{2}", and so on).
+The ``Except" clauses then point towards various ``SemanticType", collected from UMLS.
+Here, the conditional part of the node refers to types such as (``\textit{Sign or Symptom}", ``\textit{Organism Function}", ``\textit{organism Attribute}", and so on), while the conclusion part refers to concepts, such as (``\textit{Fever}", ``\textit{blood pressure}", ``\textit{age}", and so on).
+In this way, the RDR based knowledge base, provides us with a concrete, memoized, tree data structure, that can be used for schema matching, on the fly.
 

### 2021-02-01 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 10

@@
 In this way, the RDR based knowledge base, provides us with a concrete, memoized, tree data structure, that can be used for schema matching, on the fly.
+In moving from root to the leaf nodes of this tree, we gain additional matching characteristics, which are all accumulated in the returned results to provide traceability for the decision makers.
+Additionally, the RDR creation and subsequently evolution process, is dependent on approval by the expert, in determining which cases can be added to the knowledge base.
+This combination of automated process for building the schema maps, followed by expert intervention to approve the results, enables a safe and consistent knowledge base.
 
-\subsection*{Schema Map evolution}
+\subsection*{Schema Map application}
 \label{schema_map_evol}

### 2021-02-23 Implemenation/similarity.py
images changed

@@ -1,0 +1,18 @@
+class Similarity:
+
+	def readData(self, url):
+		
+		data = []
+		file = open(url, "r")
+
+		for row in file:
+			data.append(row)
+
+		return data
+  		
+
+
+simObj = Similarity()
+data = simObj.readData('Data/attempt4.txt') 
+print(len(data))
+		

### 2021-02-23 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
updat aa

@@
 The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data, into a non-persisted, interpretable, model form.
-In our current methodology we have utilized state-of-the-art machine learning techniques for converting medical schemas into semi-structured form, which is then used to create embedding vectors.
-These vectors are then used for modeling and creating interpretable rules for applying semantic reconciliation in the form of schema matching and/or transformation.
+\textbf{In our current methodology we have utilized state-of-the-art machine learning techniques for converting medical schemas into semi-structured form, which is then used to create embedding vectors.
+These vectors are then used for} modeling and creating interpretable rules for applying semantic reconciliation in the form of schema matching and/or transformation.
 These rules are managed by the RDR which allows fast inference using the relevant knowledge sub-tree, and can well manage knowledge evolution to scale out (by incorporating new schema) and up (by incorporating changes and additions to existing schema)
@@
 
-The syntactic uniqueness as represented in Equation \eqref{synType}, is also a disjoint union of the measured attribute type, corresponding to one of integer, float, boolean, or string, and it valid values.
-The elements of the attribute type set have been determined based on the common primitive types available to the applications at an abstract level.
-While database schema used by EMR systems, correspond to the SQL datatypes\cite{SQLDataTypes}, the application of semantic reconciliation-on-read strategy, instead necessitates the usage of common programming primitive types.
+The syntactic uniqueness as represented in Equation \eqref{synType}, is also a disjoint union of the measured attribute type and its valid values.
+The type of the attribute can correspond to one of Long (signed decimal values), Double (signed floating point values), Date (yyyy-MM-dd), DateTime (yyyy-MM-dd'T'HH:mm:ss.
+SSSXXX) or String.
 On the other hand, ``validValues" are determined based on what is contained in some sampled portion of the database.
-It is represented by the set of all possible categorical values (such as values of the attribute with type string which can be used to represent names, address, and others), the minimum and maximum values enclosed within open intervals (``( )") or closed intervals (``[ ]") to represent a range of numerical values ( such as values of attributes with type float or integer ), and boolean values (such as values represented by 1/0 or True/False).
+It is represented by the set of all possible categorical values (such as values of the attribute with type Date, DateTime, and String which can be used to represent names, address, and others textual elements of the EMR), the minimum and maximum values enclosed within closed intervals (``[ ]") to represent a range of numerical values ( such as values of attributes with type Double or Long),
+
+The elements of $t$ set have been determined based on some common types available to our java application.
+This set can be further extended to include other types, such as ``Boolean", ``Long", ``UUID" and so on, however each type requires a parser, which can identify the type, based on the values in the instances.
+As an example, if we add the type ``Boolean" to the set $t$, then a parser must exist, which can at the very least validate, values such as ``True", ``T", ``1", as true, and ``False:, ``f", ``0" as false.
+However, the problem here lies in determining, if the string ``1" and ``0" really belongs to the type Boolean or Long?
+Therefore, in our current implementation, we have limited the attribute type set, as mentioned above.
+Additionally, while database schema used by EMR systems, correspond to the SQL datatypes\cite{SQLDataTypes}, the application of semantic reconciliation-on-read strategy, instead necessitates the usage of common programming primitive types.
+This ensures that the querying application is able to correctly transform the textual values into their most relevant, programming type counterparts.
+
 \begin{equation}\label{synType}
-\tau_{syntatic}= \left \{ t \mid t \epsilon \left \{ \left \{ integer, float, boolean, string\right \} \uplus validValues \right \} \right \}
+\tau_{syntatic}= \left \{ t \mid t \epsilon \left \{ \left \{ Long, Double, Date, DateTime, String \right \} \uplus validValues \right \} \right \}
 \end{equation}
@@
 While this behavior is not wrong, it does create syntactic differences in the participating schema.
-Consider the terms ``name" and ``patientName", which refer to the same attribute of the patient entity, however there is no standard way to represent it, with both being correct.
-As a result, $s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter.
+Consider the terms ``name" and ``patientName", which refer to the same attribute of the patient entity.
+However, since there is no standard way to represent this attribute, both are considered correct ($s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter).
 Differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others.
@@
 In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_5$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
-We extended the same setup to \textbf{further include}
+We extended the same setup to create an additional 80 thousand records, for 1000 patients and 80 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$.
+These fragments, follow various design elements, supporting a variety of valid relational storage architectures.
+Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
+\textbf{further include}
 
@@
 Each file is loaded in memory and converted into an algorithmic iterable structure.
-For each attribute, we then generate the suffix tree, which provides all possible substring representations contained within the attribute name.
-Then for each node of this suffix tree, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS with approximate search strategy.Using Lexical Variant Generation (LVG) this strategy retrieves an expanded list of associated semantic concepts.
-If atleast one semantic concept is found for the substring, we replace the substring with the most relevant concept, based on the highest value of the confidence measure, creating the Suffix Concept Tree (SCT).
-The SCT is structurally smaller than or equal to the suffix tree, since all suffix which are smaller than 2 and those without a qualifying semantic concept, are discarded.
-Finally for each node of the SCT, the substring from the suffix tree and its corresponding concept is placed into a sentence, which is converted into an embedding vector using \textbf{BioBERT}.
-This embedding vector represents the domain qualified semantics of the source attribute.
+For each attribute, we then generate the suffix array, which provides all possible substring representations contained within the attribute name.
+
+Then for each node of this suffix array, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS with approximate search strategy.Using Lexical Variant Generation (LVG) this strategy retrieves an expanded list of associated semantic concepts.
+If atleast one semantic concept is found for the substring, we replace the substring with the most relevant concept, based on the highest value of the confidence measure, creating the Concept Array (CA).
+The CA is structurally equal to or greater than the suffix array, since all suffix which are smaller than 2 and those without a qualifying semantic concept, are discarded.
+\textbf{Finally for each node of the CA, the substring from the suffix array and its corresponding concepts is placed into a sentence, which is converted into an embedding vector using \textbf{BioBERT}.
+This embedding vector represents the domain qualified semantics of the source attribute.}
 
@@
 This is followed by syntactic type check of the attribute, which is based on its data.
-Here we determine, if the attribute values correspond to one of Integer, Float, Boolean, or String types.
+Here we determine, if the attribute values correspond to one of the types from $t$ (Equation \eqref{synType}).
 Additionally, we collect the values of each corresponding data cell, and determine the set of possible values in each case.
@@
 ``AttributeType" then encapsulates the data type features of this attribute's instances, with its primitive data type, and values providing a representation of the attribute's instance.
-Finally, ``Attribute Semantics" holds, the semantic information of this attribute, in the form of its suffix tree, SCT and Tree Embedding.
+Finally, ``Attribute Semantics" holds, the semantic information of this attribute, in the form of its suffix array, CA and Embedding Vector.
 A pair of AA's with distinct references, are then used as an input to the schema map generation process, which is explained in the next step.
@@
 Firstly we compare the datatypes of the pair, to determine if they either have the same datatype or the datatypes are convertible.
-In our current approach \textit{float} and \textit{integer} datatypes are considered convertible, however this step is very much implementation specific and can be extended when the set of types is enhanced with newer data types, such as \textit{short} is convertible to \textit{integer} and vice versa, \textit{bit} is convertible to \textit{boolean} and vice versa, and so on.
+In our current approach \textit{Double} and \textit{Long} datatypes are considered convertible, however this step is very much implementation specific and can be extended if $t$ is enhanced with newer data types.
 This test is used to set the ``SynSim" score to ``1", if the datatypes are equal or convertible, and ``0" otherwise.
@@
 Beyond the root node of the RDR, which represents the default condition, at lower depths, syntactic matching characteristics are represented, while semantic matching characteristics, such as the concepts associated with semantic types, follow thereafter.
-``AttributeType" elements representing the data types of the attributes as ``string", ``integer", ``double", and ``boolean" are placed in the first case, followed by convertible types, such as the case where the attribute values, in the form of integers are placed in a string (``\textit{1}",``\textit{2}", and so on).
+``AttributeType" elements representing the data types of the attributes (from set $t$) are placed in the first case, followed by convertible types, such as the case where the attribute values, in the form of Long are placed in a string (``\textit{1}",``\textit{2}", and so on).
 The ``Except" clauses then point towards various ``SemanticType", collected from UMLS.

### 2021-02-24 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/relatedwork.tex
related work and some code added

@@
 The experimental results revealed framework effectiveness by achieving more than 90\% precision and recall for direct and indirect link matching.
+
+A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al.
+\cite{moll2020oncology} to check their perspectives regarding patient accessible electronic health record (PAEHR).
+The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations.
+The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions.
+However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.

### 2021-02-24 Implemenation/similarity.py

@@ -1,18 +1,33 @@
+import json
+from termSemanticType import *
+
 class Similarity:
 
-	def readData(self, url):
-		
-		data = []
-		file = open(url, "r")
+    def __init__(self):
+    	self.termSemanticTypeObj = TermSemanticType()
 
-		for row in file:
-			data.append(row)
+    def readData(self, url):
+    	data = []
+    	with open(url) as json_file:
+    		data = json.load(json_file)
 
-		return data
-  		
+    	return data
+
+    def calculateSimilarity(self, url):
+
+    	result = self.termSemanticTypeObj.getTermSemanticType('diabetes')
+    	print(result)
+    	exit()
+    	data = self.readData(url)
+    	print('Total Attribute: ', len(data))
+    	for attr in data:
+    		print('attr')
+    		print(attr)
+    		print(attr['schemaName'])
+    		exit()
 
 
 simObj = Similarity()
-data = simObj.readData('Data/attempt4.txt') 
-print(len(data))
+simObj.calculateSimilarity('Data/data.json') 
+
 		

### 2021-02-24 Implemenation/termSemanticType.py

@@ -1,0 +1,82 @@
+
+import requests
+import json
+import lxml.html as lh
+from lxml.html import fromstring
+
+profileKey = "ec98614f-6197-4a85-bf9e-1b20bef64670"
+baseURL = "https://utslogin.nlm.nih.gov"
+
+class TermSemanticType:
+
+	def __init__(self):
+
+		self.tgt = self.gettgt()
+
+	#  *********** TGT Ticket ********************
+	def gettgt(self):
+
+		params = {'apikey': profileKey}
+		response = requests.post(baseURL + "/cas/v1/tickets", data = {'apikey': profileKey})
+		response = fromstring(response.text)
+		tgt = response.xpath('//form/@action')[0]
+
+		return tgt
+
+	#  ********** Single use Service Ticket ********************
+	def getst(self):
+
+		params = {'service': 'http://umlsks.nlm.nih.gov'}
+		h = {"Content-type": "application/x-www-form-urlencoded", "Accept": "text/plain", "User-Agent":"python"}
+		r = requests.post(self.tgt,data=params,headers=h)
+		st = r.text
+
+		return st
+
+	#  **************** Search Term ***********************
+	def searchTerm(self, term):
+
+		singleUseTicket = self.getst()
+
+		r = requests.get('https://uts-ws.nlm.nih.gov/rest/search/current?string='+term+'&ticket='+singleUseTicket)
+		items  = json.loads(r.text)
+		jsonData = items['result']['results']
+
+		return jsonData
+
+	#  ***************** Get Term Semantic Type **************
+	def getTermSemanticType(self, term):
+
+		response = 'NONE'
+		try :
+			termId = self.searchTerm(term)[0]['ui']
+		except NameError:
+			termId = 'NONE'
+
+		if not termId == "NONE":
+			singleUseTicket = self.getst()
+			r = requests.get('https://uts-ws.nlm.nih.gov/rest/content/2015AA/CUI/'+termId+'?ticket='+singleUseTicket)
+			
+			if(r.status_code == 200):
+				items  = json.loads(r.text)
+				try:
+					response = items
+					# response = items['result']['semanticTypes'][0]['name']
+				except NameError:
+					response = 'NONE'
+					# response = 'NONE'
+
+		return response
+
+
+# termSemanticTypeObj = TermSemanticType()
+
+# print('Semantic Type')
[…]

### 2021-02-26 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 11

@@
 In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_5$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
-We extended the same setup to create an additional 80 thousand records, for 1000 patients and 80 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$.
+We extended the same setup to create an additional 100,000 records, for 1000 patients with 3 medical fragments for $s_1$, $s_2$, and $s_4$, and 97 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$.
 These fragments, follow various design elements, supporting a variety of valid relational storage architectures.
@@
 For each attribute, we then generate the suffix array, which provides all possible substring representations contained within the attribute name.
+In order to generate the set of suffixes, we employ three strategies, forward suffix generation, whereby for a word $w$ of length $n$, $n-1$ suffixes of size 2 to $n-1$ are produced, backward suffix generation, to produce $n-1$ suffixes in reverse order with size $n-1$ to 2, and regular expression based suffix generation, which splits each word on, change of case, special characters(such as -, \_, !, and others), and numbers.
+An example of this suffix generation process is shown in \textbf{figSuffixAttribute}.
+Here, the attribute ``DOB" in $s_1$, ``PatientDateOfBirth" appears in $s_2$, ``birthday" appears in $s_3$, ``DateOfBirth" in $s_5$, and ``birthDate" in $s_4$.
+These attributes refer to the same attribute of the patient entity, however, with the suffix generation process, our aim is to identify all words within these strings.
+While the forward and backward generation process, generates all possible sequences of characters as suffix, the regex based method, only identifies the changes in the string.
+In this way a large list of suffixes is generated, which is combined using a ``TreeSet" data structure of Java, which internally sorts this list as well.
 
-Then for each node of this suffix array, if its length is greater than 2 (to avoid lookups for alphabets), we then query UMLS with approximate search strategy.Using Lexical Variant Generation (LVG) this strategy retrieves an expanded list of associated semantic concepts.
-If atleast one semantic concept is found for the substring, we replace the substring with the most relevant concept, based on the highest value of the confidence measure, creating the Concept Array (CA).
-The CA is structurally equal to or greater than the suffix array, since all suffix which are smaller than 2 and those without a qualifying semantic concept, are discarded.
-\textbf{Finally for each node of the CA, the substring from the suffix array and its corresponding concepts is placed into a sentence, which is converted into an embedding vector using \textbf{BioBERT}.
+Similarly the attribute, ``dateOfAdmission" appears in $s_4$, while ``AdmissionStartDate".
+``diseaseNameOnAdmission", and ``AdmissionEndDate" appear in $s_2$.
+As evident within these strings, while they refer to semantically different entity attributes, syntactically they contain similar elements.
+The suffixes generated from these strings are shown in \textbf{figSuffixAttribute (b)}.
+The suffix generation process, identified thus far, is only able to generate syntactic suffixes, producing many incoherent and unrelated suffixes.
+In order to counter this problem, and to limit the list of suffixes within the domain, we then query UMLS, with exact search strategy, looking for the existence of any concepts, against each suffix.
+In case, no semantic concept is found for a particular suffix, it is removed from the final Suffix Array.
+On the other hand, if atleast one semantic concepts is found against the queried suffix, it is retained.
+The list of concepts thus found, are also added to Concept Array of the AA.
+
+\st{Finally for each node of the CA, the substring from the suffix array and its corresponding concepts is placed into a sentence, which is converted into an embedding vector using \textbf{BioBERT}.
 This embedding vector represents the domain qualified semantics of the source attribute.}

### 2021-03-02 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 12

@@
 \label{schema_acq}
-In the first step of our semantic reconciliation methodology, we collect medical schema from five distinct EMR storage systems ($S$).
+In the first step of our semantic reconciliation methodology, we simulate medical data acquisition from five distinct EMR storage systems ($S$).
 These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
 al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$).
-These five schema follow relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
-Each of these schema, fulfills the need of their respective information processing applications, however the lack of interoperability is very much visible here.
-Here, heterogeneity is caused by various factors, including the lack of standard terminologies and different normalization level.
-While SNOMED-CT provides a mechanism for identifying the standard codes for clinical terms and LOINC can be used for laboratory related terms, most attribute names are created based on the gut feeling of the database designer.
-While this behavior is not wrong, it does create syntactic differences in the participating schema.
+Each of these medical systems follow the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
+While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.
+A similar notion of data heterogeneity, in terms of medical data schema, is evident across the healthcare domain.
+This is caused by various factors, including the lack of one all-encompassing, and universally applicable terminological standard and different normalization level for representing attributes.\\
+In the former case, while SNOMED-CT provides a mechanism for identifying the standard codes for clinical terms and LOINC can be used for laboratory related terms, most attribute names are created based on the gut feeling of the database designer.
+Additionally, while these codes can be used to represent data instances, the data schema, achieves no benefit from the same.
 Consider the terms ``name" and ``patientName", which refer to the same attribute of the patient entity.
-However, since there is no standard way to represent this attribute, both are considered correct ($s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter).
-Differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others.
+However, since there is no standard way to represent this attribute, both are considered correct ($s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter).\\
+In the later case, differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others.
 Similarly, ``EncounterDate" from $s_5$ is semantically similar to ``BeginDate" of ``openemr\_MedicalProblems" table in $s_1$, ``AdmissionStartDate" of ``LabsCorePopulatedTable" in $s_2$,
@@
 
-\subsection*{Schema processing}
+\subsection*{From Attribute to Amplified Attribute}
 \label{schema_prepro}
@@
 In order to process the EMR schema set $S$, we use the methodology shown in \textbf{figAlgorithm}.
-For each data representation $s_i$, we first serialize its tables into Comma Separated Value (CSV) formatted flat files.
-Each table has a separate file, which contains the attribute names in the header and the data instances (following the same format and CSV struture), in subsequent lines.
-Each file is loaded in memory and converted into an algorithmic iterable structure.
+
+First we use the data representation $s_i$, generated through the process explained above (\ref{schema_acq}) to collect the various medical fragments in memory.
+We then iterate over these fragments, building a set of attributes (not AA), distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.
+This entails that ``PatientID" from each of the four tables in $s_2$, and ``patientID" from five tables in $s_4$, would result into nine attributes (assuming, as in the current case, of no differences in versions of these systems).
 For each attribute, we then generate the suffix array, which provides all possible substring representations contained within the attribute name.
@@
 The list of concepts thus found, are also added to Concept Array of the AA.
-
-\st{Finally for each node of the CA, the substring from the suffix array and its corresponding concepts is placed into a sentence, which is converted into an embedding vector using \textbf{BioBERT}.
-This embedding vector represents the domain qualified semantics of the source attribute.}
-
 We continue this process, until all substrings have been processed.
@@
 Here we determine, if the attribute values correspond to one of the types from $t$ (Equation \eqref{synType}).
-Additionally, we collect the values of each corresponding data cell, and determine the set of possible values in each case.
-This semantic enrichment from UMLS concepts and syntactic enrichment from attribute types, is then saved into persistent storage for further processing.
+Additionally, we collect the values of each corresponding data cell, and determine the list of possible values in each case.
 
@@
 Schema Maps, provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the links between their participating attributes.
-This identification is based on the schema matching process, shown in Algorithm \ref{knowledgeEvolAlgo}, which operates on a pair of amplified attributes, $\left ( aa_i,aa_j \right ) \mid aa_i \epsilon s_i \wedge aa_j \epsilon s_j$, and calculates the similarity score $S$.
+This identification is based on the schema matching process, shown in Algorithm \ref{knowledgeEvolAlgo}, which operates on a pair of AA, $\left ( aa_i,aa_j \right ) \mid aa_i \epsilon s_i \wedge aa_j \epsilon s_j$, and calculates the similarity score $S$.
 

### 2021-03-02 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
Update methodology.tex

@@
 Firstly we compare the datatypes of the pair, to determine if they either have the same datatype or the datatypes are convertible.
-In our current approach \textit{Double} and \textit{Long} datatypes are considered convertible, however this step is very much implementation specific and can be extended if $t$ is enhanced with newer data types.
+In our current approach \textit{Double} is convertible into \textit{Long} and vice versa, and \textit{Date} is convertible into \textit{DateTime} datatypes and vice versa.
+However, this step is very much implementation specific and can be extended if $t$ is enhanced with newer data types.
 This test is used to set the ``SynSim" score to ``1", if the datatypes are equal or convertible, and ``0" otherwise.

### 2021-03-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
on ubuntu
manuscript updated
method 1
experimental setup 1

@@
 \label{experimentalSetup}
-Experimental Setup goes here ....
+In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_5$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
+We extended the same setup to create an additional 100,000 records, for 1000 patients with 3 medical fragments for $s_1$, $s_2$, and $s_4$, and 97 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$.
+These fragments, follow various design elements, supporting a variety of valid relational storage architectures.
+Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
+The code to generate this data set is available at ``uhp\_map\_generation"\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhpr\_storage}.
+This application produces three custom formatted files, containing an index for patients, an index for their medical fragments, and the medical fragment, corresponding to the EMR data.
+Using the medical fragments file, we then generate the AA\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhp\_map\_generation}.
+The resulting set of AA are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps.
+This process, is used to create 34,642 distinct pairs of attributes, across $s$.
+Each pair also contains the ``relationshipList", which stores either the positive result of a case insensitive match between the attributes, in which case no further processing is performed, or the results of fuzzywuzzy matching between the attribute names.
+The ``json" file thus produced, is then used by a python script to perform the syntactic and semantic matching on the attributes.
+In this script we used the pre-trained \textbf{Bert base model with nli mean tokens}.
+For each AA in the schema map pair, we first, concatenate the name of the attribute, its suffix array, and its concept array, to create a sentence of the form:
+``Attribute\_Name $< w_0,c_00,c_01,...c_0n; w_1,c_10,c_11,...c_1n;...w_m,c_m0,c_m1,...c_mn;>$". \textbf{such as}
+
+The rationale behind switching the applications at various stages, is to cache the results and create checkpoints for restarting any failed stages, easily.
+Additionally, since python provides better support for easy generation of embedding vectors, it was thus preferred over the Java based implementation, which is otherwise very beneficial for other tools.
+
+These applications were executed on a workstation running Ubuntu 20.04.2 LTS on top of AMD Ryzen 3 2200G, and 32GB ram.

### 2021-03-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
experimental setup 1

@@
 In order to provide an interoperable solution, it is therefore necessary to provide syntactic and semantic mappings, while taking the data instances (or tuples) into account.
-Data instances are used to enrich the semantic context of an attribute ($a_i$) by establishing its probable data type and possible value set.
-In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_5$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
-We extended the same setup to create an additional 100,000 records, for 1000 patients with 3 medical fragments for $s_1$, $s_2$, and $s_4$, and 97 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$.
-These fragments, follow various design elements, supporting a variety of valid relational storage architectures.
-Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
-\textbf{further include}
+Specifically, the creation of Amplified Attributes (AA), as an enriched version of EMR attributes, provides a semantic context, by establishing its existential context(such as schema, table, version, date and other factors), probable data type, possible value set, and its related semantic concepts.
 
@@
 \textbf{metadata}
-In order to process the EMR schema set $S$, we use the methodology shown in \textbf{figAlgorithm}.
-
+In order to process the EMR schema set $S$ and produce AA, we use the methodology shown in \textbf{figAlgorithm}.
 First we use the data representation $s_i$, generated through the process explained above (\ref{schema_acq}) to collect the various medical fragments in memory.

### 2021-03-04 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
experimental setup 2

@@
 Secondly, we compare the semantic concepts of the two amplified attributes, by applying \textbf{cosine} similarity between their embedding vectors.
-Since the embedding vector is based on the amalgamation of the suffix strings and their corresponding suffix concepts, \textbf{cosine similarity can give a good measure of the direction of these vectors}.
+In order to generate the embedding vectors, we utilize {BERT} and apply it on the sentence formed by flattening the AA.
+This operation is applied on each AA in the schema map pair, by concatenating the name of the attribute, its $m$ suffixes, and their associated $0..n$ concepts, to create a sentence as shown in Equation \ref{aaSentenceFormat}:
+
+\begin{equation}\label{aaSentenceFormat}
+\begin{aligned}
+\left \{ Attribute\_Name < w_0,c_{00},c_{01},...c_{0n}; w_1,c_{10},c_{11},...c_{1n};...w_m,c_{m0},c_{m1},...c_{mn};>\right \}\\
+| w_i \epsilon \phi_{suffix}(Attribute\_Name) \wedge c_{ij} \epsilon \phi_{concept}(w_i) 
+\end{aligned}
+\end{equation}
+
+An example of the resultant sentence is shown as follows:\\
+
+\framebox{\parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{\itshape%
+
+		``$DateOfAdmission < mission,C0026219;Dat,C1420213,C3813713,C0114838,\\
+		C0200555,C1439340,C2826247,C0057150,C0002395;Of,C1705644,C0919490,\\
+		C1704913,C1426958,C0332285,C0456628,C0029151,C1879775;ion,C1700702,\\
+		C0022023;Admission,C0809949,C0184666;Da,C3668815,C0678223,C0226032,\\
+		C1602374,C0280573,C4761311,C0332151,C1704643;Date,C1548309,C2740799,\\
+		C0011008,C1547350,C2348077;on,C2985244,C0029446,C1420342,C1720294,\\
+		C1720176 >$"
+}}\\
+
+Since the embedding vector is based on the amalgamation of the suffix strings and their corresponding concepts, \textbf{cosine similarity can give a good measure of the direction of these vectors}.
 ``SemSim", thereby obtained is then used in conjuction with previously obtained ``SynSim" to calculate the similarity of the two amplified attributes.

### 2021-03-11 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
experimental setup 2
experimental setup 3

@@
 The resulting set of AA are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps.
-This process, is used to create 34,642 distinct pairs of attributes, across $s$.
+This process, is used to create 17,321  distinct pairs of attributes, across $s$.
 Each pair also contains the ``relationshipList", which stores either the positive result of a case insensitive match between the attributes, in which case no further processing is performed, or the results of fuzzywuzzy matching between the attribute names.
@@
 In this script we used the pre-trained \textbf{Bert base model with nli mean tokens}.
-For each AA in the schema map pair, we first, concatenate the name of the attribute, its suffix array, and its concept array, to create a sentence of the form:
-``Attribute\_Name $< w_0,c_00,c_01,...c_0n; w_1,c_10,c_11,...c_1n;...w_m,c_m0,c_m1,...c_mn;>$". \textbf{such as}
 
@@
 Additionally, since python provides better support for easy generation of embedding vectors, it was thus preferred over the Java based implementation, which is otherwise very beneficial for other tools.
-
 These applications were executed on a workstation running Ubuntu 20.04.2 LTS on top of AMD Ryzen 3 2200G, and 32GB ram.

### 2021-03-11 Implemenation/results.py
Implementation updated

@@ -1,0 +1,108 @@
+print('test')
+exit()
+import pickle
+import csv
+
+
+class Results:
+
+    BASE_INDEX = 2
+    FUZZY_WUZZY_INDEX = 1
+    SYN_AND_SEM_SIM_INDEX = 0
+
+    def readData(self, url):
+
+        data = []
+
+        with open(url, "rb") as fp:
+            data = pickle.load(fp)
+
+        return data
+
+    def generateCSV(self, attributes):
+
+        data = []
+        data.append(['NodeLeftSchemaName', 'NodeLeftTableName', 'NodeLeftName', 'NodeLeftDataType', 'NodeRightSchemaName', 'NodeRightTableName', 'NodeRightName', 'NodeRightDataType', 'BERT_BASE', 'FUZZY_MATCH', 'SYN_AND_SEM_MATCH'])
+
+        for attrIndex, attr in enumerate(attributes):
+            #print("count:", attrIndex)
+            data.append(
+                [attr['nodeLeft']['schemaName'], attr['nodeLeft']['tableName'], attr['nodeLeft']['name'], attr['nodeLeft']['dataType'], attr['nodeRight']['schemaName'], attr['nodeRight']['tableName'], attr['nodeRight']['name'], attr['nodeRight']['dataType'], attr['relationshipList'][2]['confidence'], attr['relationshipList'][1]['confidence'], attr['relationshipList'][0]['confidence']])
+
+        with open('Results/resultsv0.4.csv', 'w', newline='') as file:
+            writer = csv.writer(file, delimiter=',')
+            writer.writerows(data)
+
+    def printBaseHeatMap(self, attributes, confidenceIndex):
+        print('you are here in print Base Heat Map')
+
+        leftNodes = []
+        rightNodes = []
+        matrix = {}
+
+        for attrIndex, attr in enumerate(attributes):
+
+            leftKey = attr['nodeLeft']['schemaName']+"_"+attr['nodeLeft']['tableName']+"_"+attr['nodeLeft']['name']
+            rightKey = attr['nodeRight']['schemaName'] + "_" + attr['nodeRight']['tableName'] + "_" + attr['nodeRight'][
+                'name']
+            #print("count:", attrIndex)
+            if(leftKey not in matrix.keys()):
+                matrix[leftKey] = {}
+                leftNodes.append(leftKey)
+            if (rightKey not in matrix.keys()):
+                rightNodes.append(rightKey)
[…]

### 2021-03-11 Implemenation/similarity.py

@@ -1,33 +1,195 @@
-import json
-from termSemanticType import *
+import ujson as json
+import copy
+import pickle
+from sentence_transformers import SentenceTransformer, util
+from joblib import Parallel, delayed
+import multiprocessing
+
 
 class Similarity:
 
     def __init__(self):
-    	self.termSemanticTypeObj = TermSemanticType()
+        self.embeddingVectors = {}
 
     def readData(self, url):
-    	data = []
-    	with open(url) as json_file:
-    		data = json.load(json_file)
+        data = []
+        with open(url, "rb") as fp:
+            data = pickle.load(fp)
 
-    	return data
+        return data
 
-    def calculateSimilarity(self, url):
+    def getSimpleAttributes(self, attributes):
 
-    	result = self.termSemanticTypeObj.getTermSemanticType('diabetes')
-    	print(result)
-    	exit()
-    	data = self.readData(url)
-    	print('Total Attribute: ', len(data))
-    	for attr in data:
-    		print('attr')
-    		print(attr)
-    		print(attr['schemaName'])
-    		exit()
+        print('in getSimpleAttributes function')
 
+        data = []
+        for attr in attributes:
+            data.append(attr['schemaName'] + ' ' + attr['tableName'] + ' ' + attr['name'])
+
+        return data
+
+    def calcualteBaseLineSimilarity(self, attributes):
+
+        print('len(attributes)')
+        print(len(attributes))
+
+        attributeSimilarities = []
+
+        model = SentenceTransformer('bert-base-nli-mean-tokens')
+
+        for i, attr in enumerate(attributes):
+
+            print('base line i: ', i)
+
+            formatedAttr = copy.deepcopy(attr)
+
+            embedding1 = model.encode(attr['nodeLeft']['name'], convert_to_tensor=True)
+            embedding2 = model.encode(attr['nodeRight']['name'], convert_to_tensor=True)
+
+            similarity = util.pytorch_cos_sim(embedding1, embedding2)
+            similarity = "{:.4f}".format(similarity[0][0])
+
+            formatedAttr['relationshipList'].append({'type': '', 'method': 'BERT_BASE', 'comments': None, 'confidence': similarity})
+
+            attributeSimilarities.append(formatedAttr)
+
+
+        return attributeSimilarities
+
+    def isDataTypeConvertable(self, type1, type2):
+
[…]

### 2021-03-16 Implemenation/results.py
result updated

@@ -68,6 +68,10 @@ class Results:
 
 
         print("Building the "+str(confidenceIndex)+" table")
+
+        leftNodes.sort()
+        rightNodes.sort()
+
         rowSize = len(leftNodes)
         colSize = len(rightNodes)
         i,j = 0,0
@@ -87,13 +91,16 @@ class Results:
 
                 #print("leftNodes[i]=", leftNodes[i], ", rightNodes[j]=", rightNodes[j])
                 #print("matrix[leftNodes[i]][rightNodes[j]]=", matrix[leftNodes[i]][rightNodes[j]])
-                table += str(matrix[leftNodes[i]][rightNodes[j]]) + ", "
+                if(leftNodes[i] == rightNodes[j]):
+                    table += str(1) + ", "
+                else:
+                    table += str(matrix[leftNodes[i]][rightNodes[j]]) + ", "
                 j += 1
             table += '\r\n'
             i += 1
 
         print("Done. Now saving it:")
-        with open("Data/"+str(confidenceIndex)+"-table-V0.1.csv", "wb") as fp:  # Pickling
+        with open("Data/"+str(confidenceIndex)+"-table-V0.2.csv", "wb") as fp:  # Pickling
             pickle.dump(table, fp)
         #print(table)
 

### 2021-03-16 Implemenation/similarity.py

@@ -181,7 +181,7 @@ num_cores = multiprocessing.cpu_count() - 1
 print("num_cores:", num_cores)
 
 simObj = Similarity()
-data = simObj.readData('Data/schema_processed_1615541107002.json')
+data = simObj.readData('Data/schema_processed_1615861448988.json')
 
 
 print('data')

### 2021-03-24 Implemenation/correlation.py
correlation code

@@ -1,0 +1,61 @@
+import csv
+from scipy.stats import pearsonr
+
+class Correlation:
+
+    def readCSV(self, url):
+        data= []
+
+        with open(url) as csvFile:
+
+            csvReader = csv.reader(csvFile, delimiter=',')
+
+            i = 0
+
+            for row in csvReader:
+                rowData = []
+                if i == 0:
+                    i += 1
+                    continue
+                for attr in row :
+                    if attr == '-' or attr == '0':
+                        rowData.append(0)
+                    elif attr == '<' or attr == '>':
+                        rowData.append(0.5)
+                    elif attr == '1':
+                        rowData.append(1)
+
+                data.append(rowData)
+
+        return data
+
+    def getCorrelation(self, list1, list2):
+
+        print('correlation')
+        corr, _ = pearsonr(list1, list2)
+        corr = round(corr, 2)
+
+        return corr
+
+corrObj = Correlation()
+
+annotator1Data = corrObj.readCSV('Data/Annotated/Annotator1.csv')
+print('annotator1 data loaded: ', len(annotator1Data))
+
+
+annotator2Data = corrObj.readCSV('Data/Annotated/Annotator2.csv')
+print('annotator2 data loaded: ', len(annotator2Data))
+
+
+annotator3Data = corrObj.readCSV('Data/Annotated/Annotator3.csv')
+print('annotator3 data loaded: ', len(annotator3Data))
+
+annotator4Data = corrObj.readCSV('Data/Annotated/Annotator4.csv')
+print('annotator4 data loaded: ', len(annotator4Data))
+
+
+#List1 = [1, 2, 3]
+#List2 = [1, 2, 3]
+
+corr1vs4 = corrObj.getCorrelation(annotator1Data, annotator4Data)
+print('corr between annotator1 and annotator4: ', corr1vs4)

### 2021-03-24 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
Update experimentalsetup.tex
Results 1

@@
 The resulting set of AA are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps.
-This process, is used to create 17,321  distinct pairs of attributes, across $s$.
-Each pair also contains the ``relationshipList", which stores either the positive result of a case insensitive match between the attributes, in which case no further processing is performed, or the results of fuzzywuzzy matching between the attribute names.
+This process, is used to create 21,809  distinct pairs of attributes, across $s$.
+Each pair also contains the ``relationshipList", which stores either the positive result of a case insensitive match between the attributes, in which case no further processing is performed, or the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
 The ``json" file thus produced, is then used by a python script to perform the syntactic and semantic matching on the attributes.
-In this script we used the pre-trained \textbf{Bert base model with nli mean tokens}.
+In this script we used the pre-trained Bert base model with nli mean tokens\cite{reimers-2019-sentence-bert} to create the sentence embeddings, which are then compared using cosine similarity.
 
@@
 These applications were executed on a workstation running Ubuntu 20.04.2 LTS on top of AMD Ryzen 3 2200G, and 32GB ram.
+
+\textbf{Annotators}

### 2021-03-24 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
on ubuntu
Results 1

@@
 \label{results}
-Results goes here ....
+
+The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed syntactic and semantic matching process with fuzzy string matching, only semantic matching of attribute names using sentence embedding, and with multiple human annotated versions of the schema map.
+Using the 21,809 AA pairs, we created a two dimensional matrix, of AA identifiers, whereby each cell refers to a ``SchemaName\_TableName\_AttributeName" element.
+All nodes, for which the SchemaName part of the name is same, are then marked with ``-", and these are omitted from further processing.
+This various versions of this dataset (D) are available at \textbf{url}.
+
+The results of fuzzy string comparison ($D_f$) on the attribute names of each pair, can be visualized using the heatmap shown in \textbf{figFuzzyWuzzy}.
+Similarly, the results of comparison using BERT based word embedding of the attribute names ($D_b$), is shown in \textbf{figBase}.
+Finally, the heatmap of the syntactic and semantic matching of the AA's using our proposed Algorithm \ref{knowledgeEvolAlgo} ($D_p$), is shown in \textbf{figSynAndSemMatching}.
+The values, for each cell range between ``0" and ``1", with higher values indicating a larger match between the elements, in each of these cases.
+The black areas of these heatmaps, indicate missing values, while white indicates a matching value of ``0".
+The few areas with red color, indicate the values above ``0.9", while blue areas indicate values above ``0.8".
+
+Overall, the number of similarities above the threshold values of ``0.8" are greatly increased from $D_f$, to $D_b$, and then to $D_p$ (proposed methodology).
+Changing the threshold value in $D_p$ to ``0.9", brings it relatively closer to $D_b$.
+This is due to our proposed similarity matching methodology, which gives an equal score (0.5) to the values obtained from both syntactic and semantic matches.
+Since the decision made at the syntactic evaluation is binary (0 or 1), thus for a similarity score of ``0.8", in $D_p$, ``0.5" represents the syntactic similarity, and ``0.3" semantic similarity.
+The semantic similarity value, obtained from this rescaling process, would in turn represent an original value of ``0.6" from $D_b$.
+Therefore, for an equal semantic representation, the value of semantic similarity after rescaling (between 0 and 0.5) should be ``0.4", and originally ``0.8".
+\textbf{figSynAndSemMatching0.9} shows the heatmap, of similarity matrix, obtained from $D_p$ with the threshold values as ``0.9".
+
+Generally, a comparison of these heatmaps, indicate an increase in the recall rate of the methodology.
+This is due to the fact, that our proposed methodology is able to match a larger number of AAs, providing 50\% of the score to the syntactic match, thereby increasing the count of cells without a missing value.
+This approach is also able to reduce the impact of semantic matching from names, which might contain repeated words, such as ``patient" but in reality refer to disparate concepts, such as ``PatientName" and "PatientDateOfBirth".
+Another important aspect of our matching process is the inclusion of semantic concepts and suffixes, as a sentence before its conversion to an embedded vector.
+As discussed earlier, this process is used to reduce the impact of syntactic matches alone, which would give a higher score to the attributes ``PatientName" and ``PatientGender", which refer to different concepts.
+The inclusion of concepts behind ``Name" and ``Gender" part of these names, allow for an improved comparison.
+However, the evaluation of accuracy and precision rates necessitates the comparison of these methodologies with the ground truth.
+\textbf{annotation comparison}

### 2021-03-24 Implemenation/correlation.py
annotator compare

@@ -1,5 +1,7 @@
 import csv
 from scipy.stats import pearsonr
+from sklearn.metrics import cohen_kappa_score
+import numpy as np
 
 class Correlation:
 
@@ -7,55 +9,163 @@ class Correlation:
         data= []
 
         with open(url) as csvFile:
-
             csvReader = csv.reader(csvFile, delimiter=',')
-
-            i = 0
-
+            rowIterator = 0
             for row in csvReader:
-                rowData = []
-                if i == 0:
-                    i += 1
+                rowIterator += 1
+                if rowIterator==1:
                     continue
-                for attr in row :
-                    if attr == '-' or attr == '0':
-                        rowData.append(0)
-                    elif attr == '<' or attr == '>':
-                        rowData.append(0.5)
+                colIterator = 0
+                rowData = []
+                for attr in row:
+                    attr = attr.strip()
+                    colIterator += 1
+                    if colIterator == 1:
+                        continue
+
+                    if attr == '-' or attr == '~':
+                        rowData.append("-1.0")
+                    elif attr == '' and len(rowData) < 260:
+                        rowData.append("-1.0")
+                    elif attr == '0':
+                        rowData.append("0.0")
+                    elif attr == '<':
+                        rowData.append("0.5")
                     elif attr == '1':
-                        rowData.append(1)
+                        rowData.append("1.0")
+                    elif  attr == '>':
+                        rowData.append("1.5")
+                    elif attr == '':
+                        print("rowIterator:",rowIterator,",colIterator:",colIterator, ",attr:",attr)
+                        #colIterator = colIterator-1
+                        continue
+                    # else:
+                    #     print("colIterator:",colIterator, ",attr:",attr)
+                if 0 < len(rowData) < 259:
+                    print("Row Iterator:", rowIterator)
+                    print("Column size:", colIterator)
+                    print("Columns in the original data row:", len(row))
+                    print("problematic row:", row)
+                    print("Columns in the rowData:", len(rowData))
+                    print("rowData:", rowData)
 
-                data.append(rowData)
-
+                if len(rowData)>0:
+                    data.append(rowData)
+        print("data:", data)
         return data
 
     def getCorrelation(self, list1, list2):
+        correlationBetweenLists = []
[…]

### 2021-03-24 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
added annotators comparison explain

@@
 
-\textbf{Annotators}
+In order to compare our computed models with ground truth, \textbf{4} data annotators were hired, to anonymously, score the similarity of each pair of attribute names.
+In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-".
+Following this, the annotators, marked each cell corresponding to a pair of attributes, by determining the similarity in terms of dissimilar as ``0", exactly similar as ``1", row attribute as child of column attribute as ``<", row attribute as a parent of the column attribute as ``>", and finally, unknown as ``~".
+The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
+These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
+Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in \textbf{figKappaScore}.
+The 7 permutations, amongst the 4 annotators, generate 257 kappa scores, where each individual score corresponds to the correlation of agreement between two annotators.
+Further, each score identifies the agreement in terms of scoring a set of paired attributes, while keeping the row attribute constant, and moving along the 257 column attributes.
+
+An average dataset was then produced, containing average scores of all annotators, for each attribute pair. This dataset was then used for evaluating the performance of the automated approaches.

### 2021-03-25 Implementation/AnnotatedDataHandler.py
reformatted python script

@@ -1,0 +1,265 @@
+import csv
+from scipy.stats import pearsonr
+from sklearn.metrics import cohen_kappa_score
+import numpy as np
+import re
+
+
+class AnnotatedDataHandler:
+    annotator1Data = []
+    annotator2Data = []
+    annotator3Data = []
+    annotator4Data = []
+    logLevel = ["DEBUG", "INFO"]  # ["TRACE", "DEBUG", "INFO"]       # Leave out only those levels, which should fire
+
+    def __init__(self):
+        pass
+
+    def log(self, msg, log_at="INFO"):
+        if log_at in self.logLevel:
+            if isinstance(msg, list):
+                print(' '.join(str(v) for v in msg))
+            else:
+                print(msg)
+
+    def readCSV(self, url):
+        data = []
+        with open(url) as csvFile:
+            csvReader = csv.reader(csvFile, delimiter=',')
+            for row in csvReader:
+                cellData = []
+                for attr in row:
+                    attr = self.convertAttrValue(attr)
+                    cellData.append(attr)
+                if len(cellData) > 0:
+                    data.append(cellData)
+        return data
+
+    def readCSVWithoutHeaders(self, url):
+        data = []
+        with open(url) as csvFile:
+            csvReader = csv.reader(csvFile, delimiter=',')
+            rowIterator = 0
+            for row in csvReader:
+                rowIterator += 1
+                if rowIterator == 1:
+                    continue
+                colIterator = 0
+                cellData = []
+                for attr in row:
+                    colIterator += 1
+                    if colIterator == 1:
+                        continue
+                    attr = self.convertAttrValue(attr)
+
+                    if attr == '':
+                        self.log(["rowIterator:", rowIterator, ",colIterator:", colIterator, ",attr:", attr], "DEBUG")
+                        # colIterator = colIterator-1
+                        continue
+                    else:
+                        cellData.append(attr)
+                    # else:
+                    #     log(["colIterator:",colIterator, ",attr:",attr], "DEBUG")
+                if 0 < len(cellData) < 259:
+                    self.log(["Row Iterator:", rowIterator], "DEBUG")
+                    self.log(["Column size:", colIterator], "DEBUG")
+                    self.log(["Columns in the original data row:", len(row)], "DEBUG")
+                    self.log(["problematic row:", row], "DEBUG")
+                    self.log(["Columns in the cellData:", len(cellData)], "DEBUG")
[…]

### 2021-03-25 Implementation/AnnotatedDataHandler.py
refactoring

@@ -10,7 +10,13 @@ class AnnotatedDataHandler:
     annotator2Data = []
     annotator3Data = []
     annotator4Data = []
+    method1Data = []
+    method2Data = []
+    method3Data = []
+
     logLevel = ["DEBUG", "INFO"]  # ["TRACE", "DEBUG", "INFO"]       # Leave out only those levels, which should fire
+
+
 
     def __init__(self):
         pass
@@ -73,26 +79,26 @@ class AnnotatedDataHandler:
         return data
 
     @staticmethod
-    def getAnnotatedDataHandler(list1, list2):
-        AnnotatedDataHandlerBetweenLists = []
+    def getPearsonCorrelationScore(list1, list2):
+        correlationBetweenLists = []
         for list1_attr, list2_attr in zip(list1, list2):
             (correlation_value, p_value) = pearsonr(list1_attr, list2_attr)
             formatted_correlation_value = str(round(correlation_value, 2))
-            AnnotatedDataHandlerBetweenLists.append(formatted_correlation_value)
+            correlationBetweenLists.append(formatted_correlation_value)
             # AnnotatedDataHandler = round(AnnotatedDataHandler, 2)
             # print('%7.4f %7.4f' % (AnnotatedDataHandler, p_value))
-        return AnnotatedDataHandlerBetweenLists
+        return correlationBetweenLists
 
     @staticmethod
-    def getKappaAnnotatedDataHandler(list1, list2):
-        kappaAnnotatedDataHandlerBetweenLists = []
+    def getKappaCorrelationScore(list1, list2):
+        kappaCorrelationBetweenLists = []
         for list1_attr, list2_attr in zip(list1, list2):
             d_score = cohen_kappa_score(list1_attr, list2_attr)
             formatted_d_score = str(round(d_score, 2))
-            kappaAnnotatedDataHandlerBetweenLists.append(formatted_d_score)
+            kappaCorrelationBetweenLists.append(formatted_d_score)
             # AnnotatedDataHandler = round(AnnotatedDataHandler, 2)
             # print('%7.4f %7.4f' % (AnnotatedDataHandler, p_value))
-        return kappaAnnotatedDataHandlerBetweenLists
+        return kappaCorrelationBetweenLists
 
     @staticmethod
     def convertAttrValue(attr):
@@ -152,6 +158,31 @@ class AnnotatedDataHandler:
 
         self.log("**********************************************************************************")
 
+    def readAllComputedData(self, readHeaders=False):
+
[…]

### 2021-03-25 Implementation/AnnotatedDataHandler.py
Data parsing updated to handle computed data

@@ -78,21 +78,21 @@ class AnnotatedDataHandler:
                     data.append(cellData)
         return data
 
-    @staticmethod
-    def getPearsonCorrelationScore(list1, list2):
+    def getPearsonCorrelationScore(self, list1, list2):
         correlationBetweenLists = []
         for list1_attr, list2_attr in zip(list1, list2):
-            (correlation_value, p_value) = pearsonr(list1_attr, list2_attr)
+            (correlation_value, p_value) = pearsonr(list(float(v) for v in list1_attr), list(float(v) for v in list2_attr))
             formatted_correlation_value = str(round(correlation_value, 2))
             correlationBetweenLists.append(formatted_correlation_value)
             # AnnotatedDataHandler = round(AnnotatedDataHandler, 2)
             # print('%7.4f %7.4f' % (AnnotatedDataHandler, p_value))
         return correlationBetweenLists
 
-    @staticmethod
-    def getKappaCorrelationScore(list1, list2):
+    def getKappaCorrelationScore(self, list1, list2):
         kappaCorrelationBetweenLists = []
         for list1_attr, list2_attr in zip(list1, list2):
+            # self.log(len(list1_attr))
+            # self.log(len(list2_attr))
             d_score = cohen_kappa_score(list1_attr, list2_attr)
             formatted_d_score = str(round(d_score, 2))
             kappaCorrelationBetweenLists.append(formatted_d_score)
@@ -277,17 +277,17 @@ class AnnotatedDataHandler:
 
         self.log('Cohen kappa score  between method1 and avg(annotators): ')
         resultAsCsvString += "method1 vs avg(annotators)," + ",".join(
-            annotatedDataHandler.getKappaCorrelationScore(self.method1Data, avgAnnotatedData)) + "\r\n"
+            annotatedDataHandler.getPearsonCorrelationScore(self.method1Data, avgAnnotatedData)) + "\r\n"
         self.log("**********************************************************************************")
 
         self.log('Cohen kappa score  between method2 and avg(annotators): ')
         resultAsCsvString += "method2 vs avg(annotators)," + ",".join(
-            annotatedDataHandler.getKappaCorrelationScore(self.method2Data, avgAnnotatedData)) + "\r\n"
+            annotatedDataHandler.getPearsonCorrelationScore(self.method2Data, avgAnnotatedData)) + "\r\n"
         self.log("**********************************************************************************")
         self.log('Cohen kappa score  between method3 and avg(annotators): ')
 
[…]

### 2021-03-26 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
added annotators comparison explain
computed comparison

@@
 The inclusion of concepts behind ``Name" and ``Gender" part of these names, allow for an improved comparison.
-However, the evaluation of accuracy and precision rates necessitates the comparison of these methodologies with the ground truth.
-\textbf{annotation comparison}
+
+In order to evaluate the accuracy and precision rates of these methodologies, we then compared the results of our computed methods $D_f$, $D_b$, and $D_p$, with the average scored datasets by the human annotators.
+A visualization of the resultant Cohen's Kappa score for the 257 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}.
+The bar chart shown in this visualization, indicates, an overall greater positive agreement between our proposed methodolody $D_p$, and the average scores of the annotators.
+The same is shown by the \textbf{orange} colored peaks in this dataset, which in all cases is either equivalent to the other approaches ($D_f$ and $D_b$), or better than them.

### 2021-03-26 Implementation/AnnotatedDataHandler.py

@@ -93,7 +93,7 @@ class AnnotatedDataHandler:
         for list1_attr, list2_attr in zip(list1, list2):
             # self.log(len(list1_attr))
             # self.log(len(list2_attr))
-            d_score = cohen_kappa_score(list1_attr, list2_attr)
+            d_score = cohen_kappa_score(list(str(v) for v in list1_attr), list(str(v) for v in list2_attr))
             formatted_d_score = str(round(d_score, 2))
             kappaCorrelationBetweenLists.append(formatted_d_score)
             # AnnotatedDataHandler = round(AnnotatedDataHandler, 2)
@@ -277,17 +277,17 @@ class AnnotatedDataHandler:
 
         self.log('Cohen kappa score  between method1 and avg(annotators): ')
         resultAsCsvString += "method1 vs avg(annotators)," + ",".join(
-            annotatedDataHandler.getPearsonCorrelationScore(self.method1Data, avgAnnotatedData)) + "\r\n"
+            annotatedDataHandler.getKappaCorrelationScore(self.method1Data, avgAnnotatedData)) + "\r\n"
         self.log("**********************************************************************************")
 
         self.log('Cohen kappa score  between method2 and avg(annotators): ')
         resultAsCsvString += "method2 vs avg(annotators)," + ",".join(
-            annotatedDataHandler.getPearsonCorrelationScore(self.method2Data, avgAnnotatedData)) + "\r\n"
+            annotatedDataHandler.getKappaCorrelationScore(self.method2Data, avgAnnotatedData)) + "\r\n"
         self.log("**********************************************************************************")
         self.log('Cohen kappa score  between method3 and avg(annotators): ')
 
         resultAsCsvString += "method3 vs avg(annotators)," + ",".join(
-            annotatedDataHandler.getPearsonCorrelationScore(self.method3Data, avgAnnotatedData)) + "\r\n"
+            annotatedDataHandler.getKappaCorrelationScore(self.method3Data, avgAnnotatedData)) + "\r\n"
         self.log("**********************************************************************************")
 
         self.log("**********************************************************************************")

### 2021-03-27 Implementation/AnnotatedDataHandler.py
flat datastructures

@@ -21,6 +21,15 @@ class AnnotatedDataHandler:
     def __init__(self):
         pass
 
+    def initDataStructures(self):
+        self.annotator1Data = []
+        self.annotator2Data = []
+        self.annotator3Data = []
+        self.annotator4Data = []
+        self.method1Data = []
+        self.method2Data = []
+        self.method3Data = []
+
     def log(self, msg, log_at="INFO"):
         if log_at in self.logLevel:
             if isinstance(msg, list):
@@ -134,21 +143,21 @@ class AnnotatedDataHandler:
         else:
             self.annotator1Data = annotatedDataHandler.readCSV('Data/Annotated/Annotator1.csv')
         self.log(["annotator1 data loaded: ", len(self.annotator1Data), " with readHeaders=", readHeaders])
-        # log("**********************************************************************************")
+        # log(["*"]*80)
         # log("*****************************************Annotator 2*****************************************")
         if not readHeaders:
             self.annotator2Data = annotatedDataHandler.readCSVWithoutHeaders('Data/Annotated/Annotator2.csv')
         else:
             self.annotator2Data = annotatedDataHandler.readCSV('Data/Annotated/Annotator2.csv')
         self.log(["annotator2 data loaded: ", len(self.annotator2Data), " with readHeaders=", readHeaders])
-        # log("**********************************************************************************")
+        # log(["*"]*80)
         # log("*****************************************Annotator 3*****************************************")
         if not readHeaders:
             self.annotator3Data = annotatedDataHandler.readCSVWithoutHeaders('Data/Annotated/Annotator3.csv')
         else:
             self.annotator3Data = annotatedDataHandler.readCSV('Data/Annotated/Annotator3.csv')
         self.log(["annotator3 data loaded: ", len(self.annotator3Data), " with readHeaders=", readHeaders])
-        # log("**********************************************************************************")
+        # log(["*"]*80)
         # log("*****************************************Annotator 4*****************************************")
         if not readHeaders:
             self.annotator4Data = annotatedDataHandler.readCSVWithoutHeaders('Data/Annotated/Annotator4.csv')
@@ -156,7 +165,7 @@ class AnnotatedDataHandler:
             self.annotator4Data = annotatedDataHandler.readCSV('Data/Annotated/Annotator4.csv')
         self.log(["annotator4 data loaded: ", len(self.annotator4Data), " with readHeaders=", readHeaders])
 
[…]

### 2021-03-27 Implementation/AnnotatedDataHandler.py
Update AnnotatedDataHandler.py

@@ -315,11 +315,13 @@ class AnnotatedDataHandler:
                                                 self.annotator4Data):
             rowIterator += 1
             if hasHeaders and rowIterator == 1:
+                print(a1Row)
                 for attr in a1Row:
                     colHeadNameList.append(attr)
                 # Even java has labeled loops. This sucks!
                 if rowIterator == 1:
                     averagedData.append(colHeadNameList)
+                    print(averagedData)
                     continue
 
             colIterator = 0
@@ -371,6 +373,22 @@ class AnnotatedDataHandler:
 
         return list1d
 
+    def compare1dLists(self, list2dWithHeader1, list2dWithHeader2):
+        self.log(["len(list2dWithHeader1):", len(list2dWithHeader1)])
+        self.log(["len(list2dWithHeader2):", len(list2dWithHeader2)])
+        countProblematicRows=0
+        self.log(["list2dWithHeader1:", list2dWithHeader1[0]])
+        self.log(["list2dWithHeader2:", list2dWithHeader2[0]])
+        for (row1, row2) in zip(list2dWithHeader1, list2dWithHeader2):
+            for (a1Col, a2Col) in zip(row1, row2):
+                 if not self.isFloat(a1Col) and not self.isFloat(a2Col) and not a1Col == a2Col:
+                     countProblematicRows+=1
+                    # self.log(["row1:", row1])
+                    # self.log(["row2:", row2])
+                    # self.log(["a1Col:",a1Col, ",a2Col:", a2Col])
+        self.log(["countProblematicRows:",countProblematicRows])
+
+
 
 annotatedDataHandler = AnnotatedDataHandler()
 annotatedDataHandler.readAllAnnotatorsData(False)
@@ -395,8 +413,15 @@ flatMethod1Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.
 flatMethod2Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.method2Data)
 flatMethod3Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.method3Data)
 
+annotatedDataHandler.compare1dLists(flatAnnotatedData, flatMethod1Data)
 annotatedDataHandler.log(["*"]*80)
-annotatedDataHandler.log(flatAnnotatedData)
[…]

### 2021-03-28 Implementation/AnnotatedDataHandler.py
Update AnnotatedDataHandler.py

@@ -1,7 +1,8 @@
 import csv
 from scipy.stats import pearsonr
-from sklearn.metrics import cohen_kappa_score
+from sklearn.metrics import cohen_kappa_score, confusion_matrix, ConfusionMatrixDisplay
 import numpy as np
+import matplotlib.pyplot as plt
 import re
 
 
@@ -15,8 +16,6 @@ class AnnotatedDataHandler:
     method3Data = []
 
     logLevel = ["DEBUG", "INFO"]  # ["TRACE", "DEBUG", "INFO"]       # Leave out only those levels, which should fire
-
-
 
     def __init__(self):
         pass
@@ -90,7 +89,8 @@ class AnnotatedDataHandler:
     def getPearsonCorrelationScore(self, list1, list2):
         correlationBetweenLists = []
         for list1_attr, list2_attr in zip(list1, list2):
-            (correlation_value, p_value) = pearsonr(list(float(v) for v in list1_attr), list(float(v) for v in list2_attr))
+            (correlation_value, p_value) = pearsonr(list(float(v) for v in list1_attr),
+                                                    list(float(v) for v in list2_attr))
             formatted_correlation_value = str(round(correlation_value, 2))
             correlationBetweenLists.append(formatted_correlation_value)
             # AnnotatedDataHandler = round(AnnotatedDataHandler, 2)
@@ -165,7 +165,7 @@ class AnnotatedDataHandler:
             self.annotator4Data = annotatedDataHandler.readCSV('Data/Annotated/Annotator4.csv')
         self.log(["annotator4 data loaded: ", len(self.annotator4Data), " with readHeaders=", readHeaders])
 
-        self.log(["*"]*80)
+        self.log(["*"] * 80)
 
     def readAllComputedData(self, readHeaders=False):
 
@@ -190,9 +190,10 @@ class AnnotatedDataHandler:
             self.method3Data = annotatedDataHandler.readCSV('Data/2-table-V0.2.csv')
         self.log(["method3 data loaded: ", len(self.method3Data), " with readHeaders=", readHeaders])
 
-        self.log(["*"]*80)
+        self.log(["*"] * 80)
 
     def calculatePearsonScoreBetweenAnnotators(self):
+        allAnnotatedDataHandlers = ""
         if len(self.annotator1Data) < 1 or len(self.annotator2Data) < 1 or len(self.annotator3Data) < 1 or len(
                 self.annotator4Data) < 1:
[…]

### 2021-03-29 Implementation/AnnotatedDataHandler.py
Comparison fix

@@ -4,6 +4,7 @@ from sklearn.metrics import cohen_kappa_score, confusion_matrix, ConfusionMatrix
 import numpy as np
 import matplotlib.pyplot as plt
 import re
+import pandas as pd
 
 
 class AnnotatedDataHandler:
@@ -36,20 +37,23 @@ class AnnotatedDataHandler:
             else:
                 print(msg)
 
-    def readCSV(self, url):
+    def readCSV(self, url, isComputed=False, thresholds={}):
         data = []
         with open(url) as csvFile:
             csvReader = csv.reader(csvFile, delimiter=',')
             for row in csvReader:
                 cellData = []
                 for attr in row:
-                    attr = self.convertAttrValue(attr)
+                    if not isComputed:
+                        attr = self.convertAnnotatedAttrValue(attr)
+                    else:
+                        attr = self.convertComputedAttrValue(attr, thresholds)
                     cellData.append(attr)
                 if len(cellData) > 0:
                     data.append(cellData)
         return data
 
-    def readCSVWithoutHeaders(self, url):
+    def readCSVWithoutHeaders(self, url, isComputed=False, thresholds={}):
         data = []
         with open(url) as csvFile:
             csvReader = csv.reader(csvFile, delimiter=',')
@@ -64,7 +68,12 @@ class AnnotatedDataHandler:
                     colIterator += 1
                     if colIterator == 1:
                         continue
-                    attr = self.convertAttrValue(attr)
+
+                    # Convert the attribute values, according to thresholds
+                    if not isComputed:
+                        attr = self.convertAnnotatedAttrValue(attr)
+                    else:
+                        attr = self.convertComputedAttrValue(attr, thresholds)
 
                     if attr == '':
                         self.log(["rowIterator:", rowIterator, ",colIterator:", colIterator, ",attr:", attr], "DEBUG")
@@ -110,7 +119,42 @@ class AnnotatedDataHandler:
         return kappaCorrelationBetweenLists
 
     @staticmethod
-    def convertAttrValue(attr):
+    def getDefaultThresholdValues(attr, thresholdValues={}):
+        # since the call could hold an undefined, otherwise not needed for routine operations
+        if thresholdValues == "undefined":
+            thresholdValues = {}
+
+        # initializing default threshold values. Perhaps this should be in a separate function?
[…]

### 2021-03-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
Comparison fix

@@
 
+\textbf{Threshold Selection}
 Overall, the number of similarities above the threshold values of ``0.8" are greatly increased from $D_f$, to $D_b$, and then to $D_p$ (proposed methodology).

### 2021-03-30 Implementation/AnnotatedDataHandler.py

@@ -126,7 +126,7 @@ class AnnotatedDataHandler:
 
         # initializing default threshold values. Perhaps this should be in a separate function?
         if "0" not in thresholdValues or thresholdValues["0"] == "undefined":
-            thresholdValues["0"] = 0.5
+            thresholdValues["0"] = 0.6
         if "1" not in thresholdValues or thresholdValues["1"] == "undefined":
             thresholdValues["1"] = 0.8
         if "0.5" not in thresholdValues or thresholdValues["0.5"] == "undefined":
@@ -498,11 +498,13 @@ print(len(annotatedDataHandler.method1Data))
 print(len(annotatedDataHandler.method2Data))
 print(len(annotatedDataHandler.method3Data))
 print("")
-# avgAnnotatedData = annotatedDataHandler.calculateAverageScoreBetweenAllAnnotators(True)
+avgAnnotatedData = annotatedDataHandler.calculateAverageScoreBetweenAllAnnotators(True)
 # print(avgAnnotatedData)
-# flatAnnotatedData = annotatedDataHandler.collapseDataSetTo1d(avgAnnotatedData)
+flatAnnotatedData = annotatedDataHandler.collapseDataSetTo1d(avgAnnotatedData)
 flatAnnotatedData1 = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.annotator1Data)
+flatAnnotatedData2 = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.annotator2Data)
 flatAnnotatedData3 = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.annotator3Data)
+flatAnnotatedData4 = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.annotator4Data)
 flatMethod1Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.method1Data)
 flatMethod2Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.method2Data)
 flatMethod3Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.method3Data)
[…]

### 2021-03-30 Implementation/AnnotatedDataHandler.py
Mode calculation

@@ -5,6 +5,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import re
 import pandas as pd
+from statistics import mode, StatisticsError
 
 
 class AnnotatedDataHandler:
@@ -337,7 +338,7 @@ class AnnotatedDataHandler:
                 self.log("Insufficient data for the annotators, have you read the files yet?")
                 return
             else:
-                avgAnnotatedData = annotatedDataHandler.calculateAverageScoreBetweenAllAnnotators()
+                avgAnnotatedData = annotatedDataHandler.calculateModeScoreBetweenAllAnnotators()
 
         if len(self.method1Data) < 1 or len(self.method1Data) < 1 or len(self.method1Data) < 1:
             self.log("Insufficient data for the computed methods, have you read the files yet?")
@@ -364,7 +365,7 @@ class AnnotatedDataHandler:
         self.log(["*"] * 80)
         self.log(resultAsCsvString)
 
-    def calculateAverageScoreBetweenAllAnnotators(self, hasHeaders=False):
+    def calculateModeScoreBetweenAllAnnotators(self, hasHeaders=False):
         if len(self.annotator1Data) < 1 or len(self.annotator2Data) < 1 or len(self.annotator3Data) < 1 \
                 or len(self.annotator4Data) < 1:
             self.log("Insufficient data for the annotators, have you read the files yet?")
@@ -396,8 +397,13 @@ class AnnotatedDataHandler:
                         self.log([a1Col, a2Col, a3Col, a4Col])
                         exit()
                 else:
-                    avg = (float(a1Col) + float(a2Col) + float(a3Col) + float(a4Col)) / 4
-                    cellData.append(str(avg))
+                    try:
+                        mode_val = mode([a1Col, a2Col, a3Col, a4Col])
+                    except StatisticsError:
+                        self.log([a1Col, a2Col, a3Col, a4Col])
+                        self.log("Major error: No mode found")
+                        exit()
+                    cellData.append(str(mode_val))
             averagedData.append(cellData)
         return averagedData
 
[…]

### 2021-03-30 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
more code

@@
 Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in \textbf{figKappaScore}.
-The 7 permutations, amongst the 4 annotators, generate 257 kappa scores, where each individual score corresponds to the correlation of agreement between two annotators.
-Further, each score identifies the agreement in terms of scoring a set of paired attributes, while keeping the row attribute constant, and moving along the 257 column attributes.
+The 7 permutations, amongst the 4 annotators, generate 261 kappa scores, where each individual score corresponds to the correlation of agreement between two annotators.
+Further, each score identifies the agreement in terms of scoring a set of paired attributes, while keeping the row attribute constant, and moving along the 261 column attributes.
 

### 2021-03-30 Implementation/AnnotatedDataHandler.py

@@ -1,10 +1,10 @@
 import csv
 from scipy.stats import pearsonr
-from sklearn.metrics import cohen_kappa_score, confusion_matrix, ConfusionMatrixDisplay
+from sklearn.metrics import cohen_kappa_score, confusion_matrix
 import numpy as np
 import matplotlib.pyplot as plt
 import re
-import pandas as pd
+# import pandas as pd
 from statistics import mode, StatisticsError
 
 
@@ -119,33 +119,28 @@ class AnnotatedDataHandler:
             # print('%7.4f %7.4f' % (AnnotatedDataHandler, p_value))
         return kappaCorrelationBetweenLists
 
-    @staticmethod
-    def getDefaultThresholdValues(attr, thresholdValues={}):
-        # since the call could hold an undefined, otherwise not needed for routine operations
-        if thresholdValues == "undefined":
-            thresholdValues = {}
+    def getDefaultThresholdValues(self, thresholdValues={}):
 
         # initializing default threshold values. Perhaps this should be in a separate function?
-        if "0" not in thresholdValues or thresholdValues["0"] == "undefined":
+        if "0.0" not in thresholdValues or thresholdValues["0.0"] == "undefined":
+            print("setting default value for 0.0", thresholdValues)
             thresholdValues["0"] = 0.6
-        if "1" not in thresholdValues or thresholdValues["1"] == "undefined":
-            thresholdValues["1"] = 0.8
         if "0.5" not in thresholdValues or thresholdValues["0.5"] == "undefined":
+            print("setting default value for 0.5", thresholdValues)
             thresholdValues["0.5"] = 0.8
         return thresholdValues
 
     def convertComputedAttrValue(self, attr, thresholdValues={}):
         attr = attr.strip()
-
-        thresholdValues = self.getDefaultThresholdValues(thresholdValues)
+        thresholds = self.getDefaultThresholdValues(thresholdValues)
 
         if attr == '-1' or attr == '-' or attr == '~' or attr == '':
             return "-1.0"
-        elif self.isFloat(attr) and 0 <= float(attr) < thresholdValues["0"]:
[…]

### 2021-03-31 Implementation/AnnotatedDataHandler.py
Update AnnotatedDataHandler.py

@@ -1,10 +1,10 @@
 import csv
 from scipy.stats import pearsonr
-from sklearn.metrics import cohen_kappa_score, confusion_matrix
+from sklearn.metrics import cohen_kappa_score, accuracy_score, classification_report
 import numpy as np
-import matplotlib.pyplot as plt
+#import matplotlib.pyplot as plt
 import re
-# import pandas as pd
+import pandas as pd
 from statistics import mode, StatisticsError
 
 
@@ -134,7 +134,9 @@ class AnnotatedDataHandler:
         attr = attr.strip()
         thresholds = self.getDefaultThresholdValues(thresholdValues)
 
-        if attr == '-1' or attr == '-' or attr == '~' or attr == '':
+        if attr == '-1' or attr == '-' or attr == '':
+            return "-2.0"
+        elif attr == '~' or attr == '':
             return "-1.0"
         elif self.isFloat(attr) and 0 <= float(attr) < thresholds["0.0"]:
             return "0.0"
@@ -152,7 +154,9 @@ class AnnotatedDataHandler:
     @staticmethod
     def convertAnnotatedAttrValue(attr):
         attr = attr.strip()
-        if attr == '-' or attr == '~':
+        if attr == '-':
+            attr = "-2.0"
+        elif attr == '~':
             attr = "-1.0"
         elif attr == '0':
             attr = "0.0"
@@ -163,7 +167,7 @@ class AnnotatedDataHandler:
         elif attr == '>':
             attr = "1.5"
         elif attr == '':
-            attr = "-1.0"
+            attr = "-2.0"
 
         return attr
 
@@ -428,8 +432,8 @@ class AnnotatedDataHandler:
                     continue
                 # colHeaderName = colHeadNameList[colIterator - 1]
                 # attr = self.convertAttrValue(attr)
-
-                list1d.append(attr)
+                if not attr == "-2.0":
+                    list1d.append(attr)
 
         return list1d
 
@@ -663,9 +667,10 @@ max_accuracy = 0.0
 annotatedDataHandler.log("Mode(Annotated Data) vs Method 1")
 accuracy = 0.0
 curr_epoch = 0
-minFive = -0.01
-maxFive = 0.0
+minFive = 0.89
+maxFive = 0.9
 best_threshold = thresholdsMethod1 = {"0.0": minFive, "0.5": maxFive}
[…]

### 2021-03-31 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
more code
some fixes

@@
 The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed syntactic and semantic matching process with fuzzy string matching, only semantic matching of attribute names using sentence embedding, and with multiple human annotated versions of the schema map.
-Using the 21,809 AA pairs, we created a two dimensional matrix, of AA identifiers, whereby each cell refers to a ``SchemaName\_TableName\_AttributeName" element.
+Using the 21,873 AA pairs, we created a two dimensional matrix, of AA identifiers, whereby each cell refers to a ``SchemaName\_TableName\_AttributeName" element.
 All nodes, for which the SchemaName part of the name is same, are then marked with ``-", and these are omitted from further processing.
@@
 In order to evaluate the accuracy and precision rates of these methodologies, we then compared the results of our computed methods $D_f$, $D_b$, and $D_p$, with the average scored datasets by the human annotators.
-A visualization of the resultant Cohen's Kappa score for the 257 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}.
+A visualization of the resultant Cohen's Kappa score for the 261 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}.
 The bar chart shown in this visualization, indicates, an overall greater positive agreement between our proposed methodolody $D_p$, and the average scores of the annotators.

### 2021-03-31 Implementation/results.py
result

@@ -100,7 +100,7 @@ class Results:
             i += 1
 
         print("Done. Now saving it:")
-        with open("Data/"+str(confidenceIndex)+"-table-V0.2.csv", "wb") as fp:  # Pickling
+        with open("Data/"+str(confidenceIndex)+"-table-V0.4.csv", "wb") as fp:  # Pickling
             pickle.dump(table, fp)
         #print(table)
 
@@ -115,7 +115,7 @@ class Results:
 
 resultObj = Results()
 # data = simObj.readData('Data/dataV03.json')
-data = resultObj.readData('Data/AmplifiedSimilarity-bert-base-nli-mean-tokensV0.1.txt')
+data = resultObj.readData('Data/AmplifiedSimilarity-bert-base-nli-mean-tokensV0.2.txt')
 
 print('data')
 print(len(data))

### 2021-03-31 Implementation/similarity.py

@@ -181,7 +181,7 @@ num_cores = multiprocessing.cpu_count() - 1
 print("num_cores:", num_cores)
 
 simObj = Similarity()
-data = simObj.readData('Data/schema_processed_1615861448988.json')
+data = simObj.readData('Data/schema_processed_1617174847206.json')
 
 
 print('data')
@@ -200,6 +200,6 @@ synAndSemSimilarity = simObj.calculateAmplifiedSimilarity(data)
 # print('synAndSemSimilarity')
 # print(synAndSemSimilarity)
 
-with open("Data/AmplifiedSimilarity-bert-base-nli-mean-tokensV0.1.txt", "wb") as fp:   #Pickling
+with open("Data/AmplifiedSimilarity-bert-base-nli-mean-tokensV0.2.txt", "wb") as fp:   #Pickling
     pickle.dump(synAndSemSimilarity, fp)
 

### 2021-03-31 Implementation/AnnotatedDataHandler.py
some fixes

@@ -219,30 +219,30 @@ class AnnotatedDataHandler:
     def readMethod1ComputedData(self, readHeaders=False, thresholdValues={}):
         if not readHeaders:
             self.method1Data = annotatedDataHandler.readCSVWithoutHeaders(
-                'Data/0-table-V0.3.csv', True, thresholdValues)
+                'Data/0-table-V0.4.csv', True, thresholdValues)
         else:
             self.method1Data = annotatedDataHandler.readCSV(
-                'Data/0-table-V0.3.csv', True, thresholdValues)
+                'Data/0-table-V0.4.csv', True, thresholdValues)
         self.log(["method1 data loaded: ", len(self.method1Data), " with readHeaders=", readHeaders])
 
     def readMethod2ComputedData(self, readHeaders=False, thresholdValues={}):
         if not readHeaders:
             self.method2Data = annotatedDataHandler.readCSVWithoutHeaders(
-                'Data/1-table-V0.3.csv', True,
+                'Data/1-table-V0.4.csv', True,
                 thresholdValues)
         else:
             self.method2Data = annotatedDataHandler.readCSV(
-                'Data/1-table-V0.3.csv', True,
+                'Data/1-table-V0.4.csv', True,
                 thresholdValues)
         self.log(["method2 data loaded: ", len(self.method2Data), " with readHeaders=", readHeaders])
 
     def readMethod3ComputedData(self, readHeaders=False, thresholdValues={}):
         if not readHeaders:
             self.method3Data = annotatedDataHandler.readCSVWithoutHeaders(
-                'Data/2-table-V0.3.csv', True, thresholdValues)
+                'Data/2-table-V0.4.csv', True, thresholdValues)
         else:
             self.method3Data = annotatedDataHandler.readCSV(
-                'Data/2-table-V0.3.csv', True, thresholdValues)
+                'Data/2-table-V0.4.csv', True, thresholdValues)
         self.log(["method3 data loaded: ", len(self.method3Data), " with readHeaders=", readHeaders])
 
     def readAllComputedData(self, readHeaders=False, thresholdValues={}):

### 2021-03-31 Implementation/results.py
new method for generating results

@@ -3,46 +3,47 @@ import csv
 
 
 class Results:
-
     BASE_INDEX = 2
     FUZZY_WUZZY_INDEX = 1
     SYN_AND_SEM_SIM_INDEX = 0
 
     def readData(self, url):
-
         data = []
-
         with open(url, "rb") as fp:
             data = pickle.load(fp)
-
         return data
 
     def generateCSV(self, attributes):
-
         data = []
-        data.append(['NodeLeftSchemaName', 'NodeLeftTableName', 'NodeLeftName', 'NodeLeftDataType', 'NodeRightSchemaName', 'NodeRightTableName', 'NodeRightName', 'NodeRightDataType', 'BERT_BASE', 'FUZZY_MATCH', 'SYN_AND_SEM_MATCH'])
-
+        data.append(
+            ['NodeLeftSchemaName', 'NodeLeftTableName', 'NodeLeftName', 'NodeLeftDataType', 'NodeRightSchemaName',
+             'NodeRightTableName', 'NodeRightName', 'NodeRightDataType', 'BERT_BASE', 'FUZZY_MATCH',
+             'SYN_AND_SEM_MATCH'])
         for attrIndex, attr in enumerate(attributes):
-            #print("count:", attrIndex)
+            # print("count:", attrIndex)
             data.append(
-                [attr['nodeLeft']['schemaName'], attr['nodeLeft']['tableName'], attr['nodeLeft']['name'], attr['nodeLeft']['dataType'], attr['nodeRight']['schemaName'], attr['nodeRight']['tableName'], attr['nodeRight']['name'], attr['nodeRight']['dataType'], attr['relationshipList'][2]['confidence'], attr['relationshipList'][1]['confidence'], attr['relationshipList'][0]['confidence']])
+                [attr['nodeLeft']['schemaName'], attr['nodeLeft']['tableName'], attr['nodeLeft']['name'],
+                 attr['nodeLeft']['dataType'], attr['nodeRight']['schemaName'], attr['nodeRight']['tableName'],
+                 attr['nodeRight']['name'], attr['nodeRight']['dataType'], attr['relationshipList'][2]['confidence'],
+                 attr['relationshipList'][1]['confidence'], attr['relationshipList'][0]['confidence']])
 
-        with open('Results/resultsv0.4.csv', 'w', newline='') as file:
+        with open(
+                '/content/drive/MyDrive/papers/EMR-Interoperability/Implementation/Data/ComputedResults/resultsv0.4.csv',
[…]

### 2021-03-31 Implementation/AnnotatedDataHandler.py
annotation update

@@ -1,6 +1,6 @@
 import csv
 from scipy.stats import pearsonr
-from sklearn.metrics import cohen_kappa_score, accuracy_score, classification_report
+from sklearn.metrics import cohen_kappa_score, accuracy_score, classification_report, multilabel_confusion_matrix, confusion_matrix
 import numpy as np
 #import matplotlib.pyplot as plt
 import re
@@ -666,8 +666,8 @@ max_accuracy = 0.0
 annotatedDataHandler.log("Mode(Annotated Data) vs Method 1")
 accuracy = 0.0
 curr_epoch = 0
-minFive = 0.89
-maxFive = 0.9
+minFive = 0.5
+maxFive = 0.8
 best_threshold = thresholdsMethod1 = {"0.0": minFive, "0.5": maxFive}
 best_report = {}
 while curr_epoch < max_epoch:
@@ -678,18 +678,17 @@ while curr_epoch < max_epoch:
     curr_epoch += 1
     thresholdsMethod1 = {"0.0": minFive, "0.5": maxFive}
     annotatedDataHandler.readMethod2ComputedData(True, thresholdsMethod1)
-    flatAnnotator1Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.annotator1Data)
-    flatMethod1Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.method2Data)
+    flatMethod2Data = annotatedDataHandler.collapseDataSetTo1d(annotatedDataHandler.method2Data)
     data = {'y_Actual': flatAnnotatedData,  # ["-1","0","0.5","1","1.5"],
-            'y_Predicted': flatMethod1Data  # [1,0.9,0.6,0.7,0.1]
+            'y_Predicted': flatMethod2Data  # [1,0.9,0.6,0.7,0.1]
             }
 
     # df = pd.DataFrame(data, columns=['y_Actual', 'y_Predicted'])
     # flatAnnotatedData, flatMethod1Data
     #accuracy = accuracy_score(flatAnnotatedData, flatMethod1Data) #, rownames=['Actual'], colnames=['Predicted'])
     target_names = ['0.0', '0.5', "1.0", "1.5"]
-    annotatedDataHandler.compare1dLists(flatAnnotator1Data, flatMethod1Data)
-    report = classification_report(flatAnnotatedData, flatMethod1Data, target_names=target_names,output_dict=False,zero_division=0) #, rownames=['Actual'], colnames=['Predicted'])
[…]

### 2021-05-31 Implementation/AnnotatedDataHandler_3.py
Update AnnotatedDataHandler_3.py

@@ -195,8 +195,11 @@ class AnnotatedDataHandler:
 
         # print('list1: ', len(list1), ' list2: ', len(list2))
 
-        d_score = cohen_kappa_score( list1, list2)
+        list1Class = [t[2] for t in list1]
+        list2Class = [t[2] for t in list2]
 
+        # d_score = cohen_kappa_score( list1, list2)
+        d_score = cohen_kappa_score( list1Class, list2Class)
 
         formatted_d_score = str(round(d_score, 2))
         # kappaCorrelationBetweenLists.append(formatted_d_score)

### 2021-05-31 Implementation/AnnotatedDataHandler_3.py
fixed for calculating kappa score

@@ -6,7 +6,7 @@ import re
 import pandas as pd
 from statistics import mode, StatisticsError
 import math
-#from matplotlib import pyplot as plt
+# from matplotlib import pyplot as plt
 from decimal import Decimal
 from sklearn.metrics import cohen_kappa_score, accuracy_score, classification_report, multilabel_confusion_matrix, \
     confusion_matrix, roc_curve, roc_auc_score, precision_recall_curve, auc
@@ -15,11 +15,33 @@ from sklearn.model_selection import train_test_split
 
 np.seterr('raise')
 
+
 # list1 = [1, 2, 3, 4, 5, 6, 8, 1, 2]
 # list2 = [1, 3, 5, 2, 5, 6, 8, 2 ,1 ]
 # score = cohen_kappa_score(list1, list2)
 # print("score: ", score)
 # exit()
+
+def get_kappa_correlation_score(list1, list2):
+    kappaCorrelationBetweenLists = []
+    list1Class = [t[2] for t in list1]
+    list2Class = [t[2] for t in list2]
+    d_score = cohen_kappa_score(list1Class, list2Class)
+    # formatted_d_score = str(round(d_score, 2))
+    return d_score
+
+
+def get_pearson_correlation_score(list1, list2):
+    correlationBetweenLists = []
+    for list1_attr, list2_attr in zip(list1, list2):
+        (correlation_value, p_value) = pearsonr(list(float(v) for v in list1_attr),
+                                                list(float(v) for v in list2_attr))
+        formatted_correlation_value = str(round(correlation_value, 2))
+        correlationBetweenLists.append(formatted_correlation_value)
+        # AnnotatedDataHandler = round(AnnotatedDataHandler, 2)
+        # print('%7.4f %7.4f' % (AnnotatedDataHandler, p_value))
+    return correlationBetweenLists
+
 
 class AnnotatedDataHandler:
 
@@ -29,18 +51,6 @@ class AnnotatedDataHandler:
         self.logTRACE = "TRACE"
         self.logLevel = ["DEBUG",
                          "INFO"]  # ["TRACE", "DEBUG", "INFO"]       # Leave out only those levels, which should fire
-
-        self.models = ['bert-base-nli-stsb-mean-tokens',
-                       'bert-large-nli-stsb-mean-tokens',
-                       'roberta-base-nli-stsb-mean-tokens',
-                       'roberta-large-nli-stsb-mean-tokens',
-                       'distilbert-base-nli-stsb-mean-tokens',
[…]

### 2021-05-31 Implementation/AnnotatedDataHandler_3.py
kappa

@@ -776,7 +776,7 @@ while minFive < 1:
 
 annotatedDataHandler.log("Printing Final Results")
 annotatedDataHandler.log([kappa_score_at_thresholds])
-annotatedDataHandler.writeDetailedDictToCsv(kappa_score_at_thresholds, "kappa_score"+self.computational_iteration, type="kappa")
+annotatedDataHandler.writeDetailedDictToCsv(kappa_score_at_thresholds, "kappa_score"+annotatedDataHandler.computational_iteration, type="kappa")
 #
 #
 

### 2021-05-31 Implementation/AnnotatedDataHandler_3.py
correct kappa file + updated AA creation

@@ -63,7 +63,7 @@ class AnnotatedDataHandler:
                                "0.8-0.2", "0.9-0.1"]
         self.result_file_index = "0.0-1.0"
         self.computational_iteration = "1.6"
-        self.result_iteration = ".1"
+        self.result_iteration = ".2"
         self.notSynAndSem = ["FUZZY_MATCH", "Word2Vec"]
         self.computed_method = ['bert-base-nli-stsb-mean-tokens',
                                 'bert-large-nli-stsb-mean-tokens',
@@ -100,6 +100,14 @@ class AnnotatedDataHandler:
         self.resultDir = "Results/charts/" + str(self.computational_iteration) + str(self.result_iteration) + "/"
         self.roc_result_dir = self.resultDir + "/roc/"
         self.prc_result_dir = self.resultDir + "/prc/"
+        # Make sure the folder for results exists
+        if not os.path.exists(self.roc_result_dir):
+            os.makedirs(self.roc_result_dir)
+        if not os.path.exists(self.prc_result_dir):
+            os.makedirs(self.prc_result_dir)
+        if not os.path.exists(self.raw_dict_result_dir):
+            os.makedirs(self.raw_dict_result_dir)
+
 
     def log(self, msg, log_at="INFO"):
         if log_at in self.logLevel:
@@ -670,6 +678,7 @@ class AnnotatedDataHandler:
     def writeDetailedDictToCsv(self, dict={}, dict_name="result", type="kappa", is_max_score=False):
         file_name = self.raw_dict_result_dir + "" + dict_name
         dict_table = []
+
         with open(file_name, 'w') as csv_file:
             self.log("Saving CSV data file for: " + dict_name)
             csv_writer = csv.writer(csv_file, delimiter=',')
@@ -692,7 +701,7 @@ class AnnotatedDataHandler:
                     # print("k_method_name:",k_method_name)
                     if not isinstance(v_method_name, list):
                         if type == "kappa":
-                            for k_inner_threshold, v_inner_threshold in v_outer_threshold.items():
+                            for k_inner_threshold, v_inner_threshold in v_method_name.items():
                                 csv_writer.writerow(
                                     [k_outer_threshold, k_method_name, k_inner_threshold,v_inner_threshold])
 

### 2021-05-31 Implementation/Extra/similarity 21 05 2021.py

@@ -120,34 +120,34 @@ class Similarity:
 
         return result
 
-    # @staticmethod
-    # def createSentenceForAA(node):
-    #     amplified_sentences = []
-    #     word_concept_map = {}
-    #     # for word in node['suffixArray']:
-    #     #     word_concept_map["word"] = []
-    #     amplified_sentences.append(" ".join(node['suffixArray']))
-    #     for concept in node['conceptArray']:
-    #         if concept['token'] not in word_concept_map:
-    #             word_concept_map[concept['token']] = []
-    #         word_concept_map[concept['token']].append(concept['name'])
-    #     conceptset = word_concept_map.values()
-    #     product_concepts = list(itertools.product(*conceptset))
-    #     for concept_product_tuple in product_concepts:
-    #         amplified_sentences.append(" ".join(concept_product_tuple))
-    #
-    #     return amplified_sentences
     @staticmethod
     def createSentenceForAA(node):
         amplified_sentences = []
-        # word_concept_map = {}
+        word_concept_map = {}
         # for word in node['suffixArray']:
         #     word_concept_map["word"] = []
-        amplified_sentences.extend(node['suffixArray'])
+        amplified_sentences.append(" ".join(node['suffixArray']))
         for concept in node['conceptArray']:
-            amplified_sentences.append(concept['name'])
+            if concept['token'] not in word_concept_map:
+                word_concept_map[concept['token']] = []
+            word_concept_map[concept['token']].append(concept['name'])
+        conceptset = word_concept_map.values()
+        product_concepts = list(itertools.product(*conceptset))
+        for concept_product_tuple in product_concepts:
+            amplified_sentences.append(" ".join(concept_product_tuple))
 
         return amplified_sentences
+    # @staticmethod
+    # def createSentenceForAA(node):
+    #     amplified_sentences = []
+    #     # word_concept_map = {}
+    #     # for word in node['suffixArray']:
+    #     #     word_concept_map["word"] = []
+    #     amplified_sentences.extend(node['suffixArray'])
+    #     for concept in node['conceptArray']:
+    #         amplified_sentences.append(concept['name'])
+    #
+    #     return amplified_sentences
 
 
     def getSyntacticSimilarity(self, attr):
@@ -308,7 +308,7 @@ class Similarity:
 
[…]

### 2021-06-01 Implementation/similarity.py
fixed serntence

@@ -5,6 +5,49 @@ from sentence_transformers import SentenceTransformer, util
 from joblib import Parallel, delayed
 import multiprocessing
 import itertools
+import torch
+from numba import njit, cuda, prange
+from numba import jit
+import numpy as np
+from fastdist import fastdist
+from numpy import dot
+from numpy.linalg import norm
+
+
+# Function to print the settings
+def print_settings():
+    print('Using device:', device)
+    # Additional Info when using cuda
+    if device.type == 'cuda':
+        print(torch.cuda.get_device_name(0))
+        print('Memory Usage:')
+        print('Allocated:', round(torch.cuda.memory_allocated(0) / 1024 ** 3, 1), 'GB')
+        print('Cached:   ', round(torch.cuda.memory_reserved(0) / 1024 ** 3, 1), 'GB')
+
+
+device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+print_settings()
+
+
+@jit(nopython=True, parallel=True)
+def cosine_similarity_numba(u: np.ndarray, v: np.ndarray):
+    assert (u.shape[0] == v.shape[0])
+    uv = 0
+    uu = 0
+    vv = 0
+    for i in prange(u.shape[0]):
+        uv += u[i] * v[i]
+        uu += u[i] * u[i]
+        vv += v[i] * v[i]
+    cos_theta = 1
+    if uu != 0 and vv != 0:
+        cos_theta = uv / np.sqrt(uu * vv)
+    return cos_theta
+
+
+def cosine_similarity_numpy(u: np.ndarray, v: np.ndarray):
+    cos_sim = dot(u, v) / (norm(u) * norm(v))
+    return cos_sim
 
 
 class Similarity:
@@ -12,16 +55,16 @@ class Similarity:
     def __init__(self):
         self.embeddingVectors = {}
         self.models = ['bert-base-nli-stsb-mean-tokens',
-        'bert-large-nli-stsb-mean-tokens',
-        'roberta-base-nli-stsb-mean-tokens',
-        'roberta-large-nli-stsb-mean-tokens',
-        'distilbert-base-nli-stsb-mean-tokens',
-        'bert-base-nli-mean-tokens',
-        'bert-large-nli-mean-tokens',
-        'roberta-base-nli-mean-tokens',
-        'roberta-large-nli-mean-tokens',
-        'distilbert-base-nli-mean-tokens'
-        ]
+                       'bert-large-nli-stsb-mean-tokens',
[…]

### 2021-06-01 Implementation/results.py
table generated

@@ -10,8 +10,8 @@ class Results:
     # BASE_INDEX = 2
     # FUZZY_WUZZY_INDEX = 1
     # SYN_AND_SEM_SIM_INDEX = 0
-    computational_iteration = "1.6"
-    amplified_similarity_execution_index = "0.4"
+    computational_iteration = "1.7"
+    amplified_similarity_execution_index = "0.5"
     models = ['bert-base-nli-stsb-mean-tokens',
               'bert-large-nli-stsb-mean-tokens',
               'roberta-base-nli-stsb-mean-tokens',
@@ -198,8 +198,8 @@ class Results:
 
 resultObj = Results()
 # data = simObj.readData('Data/dataV03.json')
-#data = resultObj.readData('Data/AmplifiedSimilarity-V'+resultObj.amplified_similarity_execution_index+'.txt')
-data = resultObj.readData('Data/AmplifiedSimilarity-Word2Vec-V'+resultObj.amplified_similarity_execution_index+'.txt')
+data = resultObj.readData('Data/AmplifiedSimilarity-V'+resultObj.amplified_similarity_execution_index+'.txt')
+# data = resultObj.readData('Data/AmplifiedSimilarity-Word2Vec-V'+resultObj.amplified_similarity_execution_index+'.txt')
 
 print('data')
 print(len(data))
@@ -211,11 +211,8 @@ print(len(data))
 
 #for syn in frange(0.1, 0.9, 0.1):
 
-#resultObj.printBaseHeatMap(data, 'FUZZY_MATCH')
-resultObj.printBaseHeatMap(data, 'Word2Vec')
-
-
-exit()
+resultObj.printBaseHeatMap(data, 'FUZZY_MATCH')
+# resultObj.printBaseHeatMap(data, 'Word2Vec')
 
 
 for model_baseline in resultObj.models:

### 2021-06-01 Implementation/AnnotatedDataHandler_3.py
Update AnnotatedDataHandler_3.py

@@ -62,8 +62,8 @@ class AnnotatedDataHandler:
         self.result_indexes = ["0.0-1.0", "0.1-0.9", "0.2-0.8", "0.3-0.7", "0.4-0.6", "0.5-0.5", "0.6-0.4", "0.7-0.3",
                                "0.8-0.2", "0.9-0.1"]
         self.result_file_index = "0.0-1.0"
-        self.computational_iteration = "1.6"
-        self.result_iteration = ".2"
+        self.computational_iteration = "1.7"
+        self.result_iteration = ".1"
         self.notSynAndSem = ["FUZZY_MATCH", "Word2Vec"]
         self.computed_method = ['bert-base-nli-stsb-mean-tokens',
                                 'bert-large-nli-stsb-mean-tokens',

### 2021-06-01 Implementation/AnnotatedDataHandler_3.py
score

@@ -4,12 +4,13 @@ from scipy.stats import pearsonr
 import numpy as np
 import re
 import pandas as pd
+import sys
 from statistics import mode, StatisticsError
 import math
 # from matplotlib import pyplot as plt
 from decimal import Decimal
 from sklearn.metrics import cohen_kappa_score, accuracy_score, classification_report, multilabel_confusion_matrix, \
-    confusion_matrix, roc_curve, roc_auc_score, precision_recall_curve, auc
+    confusion_matrix, roc_curve, roc_auc_score, precision_recall_curve, auc, matthews_corrcoef
 from sklearn.datasets import make_classification
 from sklearn.model_selection import train_test_split
 
@@ -29,6 +30,35 @@ def get_kappa_correlation_score(list1, list2):
     d_score = cohen_kappa_score(list1Class, list2Class)
     # formatted_d_score = str(round(d_score, 2))
     return d_score
+
+def get_Mcc_score(y_true_tuple, y_pred_tuple):
+    kappaCorrelationBetweenLists = []
+    y_true = [t[2] for t in y_true_tuple]
+    y_pred = [t[2] for t in y_pred_tuple]
+
+    # C = confusion_matrix(y_true, y_pred, sample_weight=None)
+    # t_sum = C.sum(axis=1, dtype=np.float64)
+    # p_sum = C.sum(axis=0, dtype=np.float64)
+    # n_correct = np.trace(C, dtype=np.float64)
+    # n_samples = p_sum.sum()
+    # print("n_correct * n_samples:", n_correct * n_samples)
+    # print("np.dot(t_sum, p_sum):", np.dot(t_sum, p_sum))
+    # cov_ytyp = n_correct * n_samples - np.dot(t_sum, p_sum)
+    # cov_ypyp = n_samples ** 2 - np.dot(p_sum, p_sum)
+    # cov_ytyt = n_samples ** 2 - np.dot(t_sum, t_sum)
+    # print("cov_ytyp:",cov_ytyp)
+    # print("cov_ytyt:",cov_ytyt)
+    # print("cov_ypyp:",cov_ypyp)
+    # mcc = cov_ytyp / np.sqrt(cov_ytyt * cov_ypyp)
+    try:
+        mcc_score = matthews_corrcoef(y_true, y_pred)
+    except:
+        mcc_score = 0
+
+
+    # formatted_d_score = str(round(d_score, 2))
+    return mcc_score
+
 
 
[…]

### 2021-06-02 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
updated paper without RDR and AA

@@
 This application produces three custom formatted files, containing an index for patients, an index for their medical fragments, and the medical fragment, corresponding to the EMR data.
-Using the medical fragments file, we then generate the AA\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhp\_map\_generation}.
-The resulting set of AA are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps.
-This process, is used to create 21,809  distinct pairs of attributes, across $s$.
-Each pair also contains the ``relationshipList", which stores either the positive result of a case insensitive match between the attributes, in which case no further processing is performed, or the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
-The ``json" file thus produced, is then used by a python script to perform the syntactic and semantic matching on the attributes.
-In this script we used the pre-trained Bert base model with nli mean tokens\cite{reimers-2019-sentence-bert} to create the sentence embeddings, which are then compared using cosine similarity.
-
+Using the medical fragments file, we then generate the semantically enriched attribute \footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhp\_map\_generation}, which contains the suffixes and their concepts corresponding to each EMR data attribute.
+The resulting set of enriched attributes are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps.
+This process, is used to create 21,873  distinct pairs of attributes, across $s$.
+Each pair also contains the ``relationshipList", which stores the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
+The ``json" file thus produced, is then used by a python script to generate the semantically enriched sentences and their embedded vectors using WordNet, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
+The BERT models include 'bert-base-nli-stsb-mean-tokens', 'bert-large-nli-stsb-mean-tokens', 'roberta-base-nli-stsb-mean-tokens', 'roberta-large-nli-stsb-mean-tokens', 'distilbert-base-nli-stsb-mean-tokens', 'bert-base-nli-mean-tokens', 'bert-large-nli-mean-tokens', 'roberta-base-nli-mean-tokens', 'roberta-large-nli-mean-tokens', and 'distilbert-base-nli-mean-tokens'.
+The embedding vectors are then compared using cosine similarity, which produces a score between -1 and 1.
 The rationale behind switching the applications at various stages, is to cache the results and create checkpoints for restarting any failed stages, easily.
@@
 
-In order to compare our computed models with ground truth, \textbf{4} data annotators were hired, to anonymously, score the similarity of each pair of attribute names.
+In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal", ``related", or ``unrelated" 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
 In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-".
@@
 Further, each score identifies the agreement in terms of scoring a set of paired attributes, while keeping the row attribute constant, and moving along the 261 column attributes.
-
-An average dataset was then produced, containing average scores of all annotators, for each attribute pair. This dataset was then used for evaluating the performance of the automated approaches.
+Finally we produced a consolidated dataset, using mode scores of all annotators, for each attribute pair.
+This dataset is then split into development and testing partitions with a ratio of 70:30.
+The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal", followed by best scores for class ``related" and finally best of class "unrelated".
+The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and F-1 score.

### 2021-06-02 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/introduction.tex
on ubuntu
updated paper without RDR and AA

@@
 In the current manuscript, we will present our research work to build and manage the schema map knowledge base.
-Overall, our methodology has two major portions, firstly we apply a novel schema matching technique to create a transformation function $\sigma$ for the participating legacy schema, and secondly, we have used the Ripple Down Rules (RDR)  to manage our knwoledgebase, which will be presented in some detail, focusing primarily on the search and evolution services.
-In particular,
+Overall, our methodology is based on the creation, evaluation, and application of a novel schema matching technique to identify the relationships between attributes of the participating medical data schema.
+These will be presented in detail, with following flow:
 
 \begin{itemize}
-\item[$-$] Section 2 contains the details of our methodology, where we aim to present a reproducible theoretical framework.
-\item[$-$] Section 3 provides the experimental setup
-\item[$-$] Section 4 presents the results
+\item[$-$] Section \ref{methodology} contains the details of our methodology
+\item[$-$] Section \ref{experimentalSetup} provides the experimental setup
+\item[$-$] Section \ref{results} presents the results
 \item[$-$] Section \ref{relatedwork} presents the related work

### 2021-06-02 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
experimental setup 3
more code
updated paper without RDR and AA

--- 2021-03-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
@@
 To this end, the creation of a cohesive workflow is of utmost importance.
-In our earlier work \cite{Satti2020} we used maximum sequence identification and matching using suffix trees for syntactic matching of two distinctly sources data schemas.
+In our earlier work \cite{Satti2020} we used maximum sequence identification and suffix tress based matching for syntactic matching of two distinct data schemas.
 This was followed by semantic concept enrichment and subsequently concept matching, for creating rules in the form of schema maps.
-The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data, into a non-persisted, interpretable, model form.
-\textbf{In our current methodology we have utilized state-of-the-art machine learning techniques for converting medical schemas into semi-structured form, which is then used to create embedding vectors.
-These vectors are then used for} modeling and creating interpretable rules for applying semantic reconciliation in the form of schema matching and/or transformation.
-These rules are managed by the RDR which allows fast inference using the relevant knowledge sub-tree, and can well manage knowledge evolution to scale out (by incorporating new schema) and up (by incorporating changes and additions to existing schema)
-In essence, the aim here is to define a uniqueness property ($\mathbb{P}$), as shown in Equation \eqref{uniquenessProp}, whereby the semantic and syntactic uniqueness of each attribute as a disjoint union, is used.
-
-\begin{equation}\label{uniquenessProp}
-range(\mathbb{P})= \tau_{syntatic} \uplus \tau_{semantic}
-\end{equation}
-
-The syntactic uniqueness as represented in Equation \eqref{synType}, is also a disjoint union of the measured attribute type and its valid values.
-The type of the attribute can correspond to one of Long (signed decimal values), Double (signed floating point values), Date (yyyy-MM-dd), DateTime (yyyy-MM-dd'T'HH:mm:ss.
-SSSXXX) or String.
-On the other hand, ``validValues" are determined based on what is contained in some sampled portion of the database.
-It is represented by the set of all possible categorical values (such as values of the attribute with type Date, DateTime, and String which can be used to represent names, address, and others textual elements of the EMR), the minimum and maximum values enclosed within closed intervals (``[ ]") to represent a range of numerical values ( such as values of attributes with type Double or Long),
-
-The elements of $t$ set have been determined based on some common types available to our java application.
-This set can be further extended to include other types, such as ``Boolean", ``Long", ``UUID" and so on, however each type requires a parser, which can identify the type, based on the values in the instances.
-As an example, if we add the type ``Boolean" to the set $t$, then a parser must exist, which can at the very least validate, values such as ``True", ``T", ``1", as true, and ``False:, ``f", ``0" as false.
-However, the problem here lies in determining, if the string ``1" and ``0" really belongs to the type Boolean or Long?
-Therefore, in our current implementation, we have limited the attribute type set, as mentioned above.
-Additionally, while database schema used by EMR systems, correspond to the SQL datatypes\cite{SQLDataTypes}, the application of semantic reconciliation-on-read strategy, instead necessitates the usage of common programming primitive types.
-This ensures that the querying application is able to correctly transform the textual values into their most relevant, programming type counterparts.
-
-\begin{equation}\label{synType}
-\tau_{syntatic}= \left \{ t \mid t \epsilon \left \{ \left \{ Long, Double, Date, DateTime, String \right \} \uplus validValues \right \} \right \}
-\end{equation}
-
-The semantic type is represented by the Equation \eqref{semType}, which is the set of all concepts corresponding to the leaf nodes of the suffix tree, generated from the name of the attribute.
-Suffix trees are used to divide a string into components, which is a very useful base for quickly identifying the longest common subsequence between a pair of strings and data compression.
-In our case, these trees provide a manageable list of words, contained with the name of attribute.
-For each substring, represented by a path of the tree, we then identify the corresponding concept, if it exists, thereby producing a set of concepts which may represent the attribute.
-
-\begin{equation}\label{semType}
-\tau_{semantic}= \left \{s \mid s \epsilon \left \{ concept_{i,j} \mid i \leq width(suffixTree(s)) \wedge j \epsilon \left \{ substring_i \right \} \right \} \right \}
-\end{equation}
-
-Finally, the set $AA$ of Amplified Attribute (AA), holds all unique attributes of participating schema, as shown in Equation \eqref{uniqueA}.
-For each element of this set, the attribute is unique if its properties from Equation \eqref{uniquenessProp}, are not similar to any other element of this set.
-The similarity function ``$\sim$" is a threshold based loose bound, on the disjoint elements of ``$\mathbb{P}$".
-
-\begin{equation}\label{uniqueA}
-\exists a \epsilon AA \mid ( \mathbb{P}(a) \wedge \forall b \epsilon AA \mid \mathbb{P}(b) \rightarrow a \sim b)
-\end{equation}
-
-As a possible realization of this theoretical set notation form, and from a practical point of view, our methodology is presented in the following subsections.
+The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data, into an interpretable, model form.
+In our current methodology we have utilized state-of-the-art natural language processing (NLP) techniques to extract the schema mapping rules from semi-structured data schemas.
+This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas.
+\textbf{Traditional NLP techniques such as WordNet are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence.} However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
+In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names.
+The bidirectional nature of BERT, allows the creation of contextual embedded vectors, where each target word is affected by its neighboring words.
+Hence to convert the set of suffixes into a sentence, we collected the set of concepts corresponding to each suffix, from Unified Medical Language System (UMLS).
+This operation has two effects, firstly it is used to remove any suffix, which does not have a corresponding concept and secondly the extracted concepts are used to add context to each suffix and produce a contextual sentence.
+The following subsections provide the practical details for our methodology, from schema acquisition, to attribute name expansion, and finally schema map generation.
 
@@
 In fact, the change in context of the EMR storage system from the initial time of development to a later stage of collaborative processing systems, is the main cause of heterogeneity.
-In order to provide an interoperable solution, it is therefore necessary to provide syntactic and semantic mappings, while taking the data instances (or tuples) into account.
-Specifically, the creation of Amplified Attributes (AA), as an enriched version of EMR attributes, provides a semantic context, by establishing its existential context(such as schema, table, version, date and other factors), probable data type, possible value set, and its related semantic concepts.
+In order to provide an interoperable solution, it is therefore necessary to enhance the semantics of each EMR attribute by its contextually equivalent sentence.
 
-\subsection*{From Attribute to Amplified Attribute}
+\subsection*{From Attribute to Sentence}
 \label{schema_prepro}
-\textbf{metadata}
-In order to process the EMR schema set $S$ and produce AA, we use the methodology shown in \textbf{figAlgorithm}.
+In order to process the EMR schema set $S$ and produce a set of corresponding semantically enriched sentences, we use the methodology shown in \textbf{figAlgorithm}.
 First we use the data representation $s_i$, generated through the process explained above (\ref{schema_acq}) to collect the various medical fragments in memory.
-We then iterate over these fragments, building a set of attributes (not AA), distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.
+We then iterate over these fragments, building a set of attributes, distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.
 This entails that ``PatientID" from each of the four tables in $s_2$, and ``patientID" from five tables in $s_4$, would result into nine attributes (assuming, as in the current case, of no differences in versions of these systems).
@@
 In case, no semantic concept is found for a particular suffix, it is removed from the final Suffix Array.
-On the other hand, if atleast one semantic concepts is found against the queried suffix, it is retained.
-The list of concepts thus found, are also added to Concept Array of the AA.
-We continue this process, until all substrings have been processed.
-This is followed by syntactic type check of the attribute, which is based on its data.
-Here we determine, if the attribute values correspond to one of the types from $t$ (Equation \eqref{synType}).
-Additionally, we collect the values of each corresponding data cell, and determine the list of possible values in each case.
+On the other hand, if atleast one semantic concept is found against the queried suffix, it is retained.
+Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
+The set of suffixes and their corresponding concepts are then used to build the sentence, where by each concept, corresponding to a suffix is appended next to the suffix.
+An example of the resultant sentence for the attribute ``DateOfAdmission" is shown as follows:\\
 
-Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
-The flat enriched schema, following the design shown in \textbf{figEnrichedSchema} provides the input to our knowledge base.
-The logically amplified structure of the attribute, AA, is represented in \textbf{figAttributeRepresentation}.
-Here, the elements of AA are categorized into three parts.
-``AttributeContext" contains the metadata conforming to an instance of the attribute's existence,  with its name, container table name and schema name, acting as a pointer, and schema version, source, and recorded date providing the version control features.
-In this manner, the attribute's fully qualified reference, along with its existential context is identified.
-``AttributeType" then encapsulates the data type features of this attribute's instances, with its primitive data type, and values providing a representation of the attribute's instance.
-Finally, ``Attribute Semantics" holds, the semantic information of this attribute, in the form of its suffix array, CA and Embedding Vector.
-A pair of AA's with distinct references, are then used as an input to the schema map generation process, which is explained in the next step.
+\framebox{\parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{\itshape%
+
+		``Date Value type - Date date allergenic extract Date in time Data types - Date Date Fruit;Of SPI1 wt Allele SPI1 gene TAF1 wt Allele BRIP1 gene Within Degrees fahrenheit Oral contraception BRIP1 wt Allele;Da Displacement of abomasum dalton Anterior descending branch of left coronary artery deca units cytarabine/daunorubicin protocol Dai Chinese Asymptomatic diagnosis of Drug Accountability Domain;ion Iontophoresis Route of Drug Administration Ions;on SPARC wt Allele Osteonectin SPARC gene On (qualifier value) Upon - dosing instruction fragment;Admission Admission activity Hospital admission;Dat SLC6A3 gene SLC6A3 wt Allele dopamine transporter Direct Coombs test SLC6A3 protein, human Test Date cytarabine/daunorubicin/thioguanine Alzheimer's Disease;mission Religious Missions;"
+}}\\
+
+Here the various suffixes and their concepts are seperated by the symbol ``;", however together they form one sentence, for which an embedded vector is generated.
 
@@
 \label{schema_map_gen}
-Schema Maps, provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the links between their participating attributes.
-This identification is based on the schema matching process, shown in Algorithm \ref{knowledgeEvolAlgo}, which operates on a pair of AA, $\left ( aa_i,aa_j \right ) \mid aa_i \epsilon s_i \wedge aa_j \epsilon s_j$, and calculates the similarity score $S$.
 
-\begin{algorithm}
-	\textbf{Input}: AmplifiedAttributes $ aa_i, aa_j$ \\
-	\textbf{Output}: Similarity $S$ 
-	\begin{algorithmic}[1]
-		\State Similarity $S = 0$;
-		\If{$aa_i.AttributeContext == aa_j.AttributeContext$}:
-		\State $S = 1$;
-		\Else
-		% Checking Attribute Type
-		\State Syntactic Similarity $SynSim = 0 $
-		\State $at_i = aa_i.AttributeType$
-		\State $at_j = aa_j.AttributeType$
-
-		\If{$(at_i.DataType == at_j.DataType) || (at_i.DataType \Leftrightarrow at_j.DataType)$}: 
-		\State	$SynSim = 1$
-		\EndIf
-		\State Semantic Similarity $SemSim = 0 $
-		\State $\vec{ae_i} =  aa_i.Attribute Semantics
-		.TreeEmbedding$
-		\State $\vec{ae_j} =  aa_j.Attribute Semantics
-		.TreeEmbedding$
-
-		\State $SemSim = \frac{\vec{ae_i} \cdot \vec{ae_j}}{\|\vec{ae_i}\|\|\vec{ae_j}\|}$
-
-		\State $S = (0.5 * SynSim) + (0.5 * SemSim) $
-		\EndIf
-
-		\State return $S$
-		\caption{Attributes similarity identifier}
-		\label{knowledgeEvolAlgo}
-	\end{algorithmic}
-\end{algorithm}
-
-This algorithmic process starts by comparing the metadata context of the two amplified attributes.
-The schema name, table name, attribute name, and version are used to establish the context of each attribute, which are then evaluated based on naive string matching of corresponding elements.
-If the pair refer to the same instance of the amplified attribute the process simply returns 1 as the similarity score.
-If however, the amplified attribute refer to separate instances, we then apply syntactic and semantic similarity on the pair.
-Firstly we compare the datatypes of the pair, to determine if they either have the same datatype or the datatypes are convertible.
-In our current approach \textit{Double} is convertible into \textit{Long} and vice versa, and \textit{Date} is convertible into \textit{DateTime} datatypes and vice versa.
-However, this step is very much implementation specific and can be extended if $t$ is enhanced with newer data types.
-This test is used to set the ``SynSim" score to ``1", if the datatypes are equal or convertible, and ``0" otherwise.
-Secondly, we compare the semantic concepts of the two amplified attributes, by applying \textbf{cosine} similarity between their embedding vectors.
-Since the embedding vector is based on the amalgamation of the suffix strings and their corresponding suffix concepts, \textbf{cosine similarity can give a good measure of the direction of these vectors}.
-``SemSim", thereby obtained is then used in conjuction with previously obtained ``SynSim" to calculate the similarity of the two amplified attributes.
-Using equal weights for syntactic and semantic similarity, we then re-scale their individual values to finally provide a similarity score between ``0" and ``1".
-
-The schema matching approach represented above, can be further improved by enwrapping the individual calls with memoization, which can avoid redundant checks.
-However, in practical terms, the creation of the schema map between two amplified attributes is rarer than its application to transform or link two distinct schemas.
-Additionally, just like its other schema/ontology matching counterparts, the presented Algorithm \ref{knowledgeEvolAlgo}, applies a one-way compression on the various matched factors to produce a similarity measure/ indicator.
-This operation is very useful for building unsupervised and semi-supervised automated systems, which base their decisions on a measured confidence score.
-However, in the healthcare domain, knowledge acquisition and application process, requires the use of supervised automated systems, which can provide strong traceability for the decision making process.
-Summarily, it is not enough for our schema matching process to simply return $S$.
-
-This is where, Ripple Down Rules (RDR) knowledge base, steps in.
-RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules \cite{compton1992ripple, richards2009two, kim2018rdr}.
-As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm.
-Beyond the root node of the RDR, which represents the default condition, at lower depths, syntactic matching characteristics are represented, while semantic matching characteristics, such as the concepts associated with semantic types, follow thereafter.
-``AttributeType" elements representing the data types of the attributes (from set $t$) are placed in the first case, followed by convertible types, such as the case where the attribute values, in the form of Long are placed in a string (``\textit{1}",``\textit{2}", and so on).
-The ``Except" clauses then point towards various ``SemanticType", collected from UMLS.
-Here, the conditional part of the node refers to types such as (``\textit{Sign or Symptom}", ``\textit{Organism Function}", ``\textit{organism Attribute}", and so on), while the conclusion part refers to concepts, such as (``\textit{Fever}", ``\textit{blood pressure}", ``\textit{age}", and so on).
-In this way, the RDR based knowledge base, provides us with a concrete, memoized, tree data structure, that can be used for schema matching, on the fly.
-In moving from root to the leaf nodes of this tree, we gain additional matching characteristics, which are all accumulated in the returned results to provide traceability for the decision makers.
-Additionally, the RDR creation and subsequently evolution process, is dependent on approval by the expert, in determining which cases can be added to the knowledge base.
-This combination of automated process for building the schema maps, followed by expert intervention to approve the results, enables a safe and consistent knowledge base.
-
-\subsection*{Schema Map application}
-\label{schema_map_evol}
+Schema Maps, provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the semantic relationship between their participating attributes.
+This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each EMR attribute.
+While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as \textbf{stsb-roberta-large} provides the best results.
+The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them.
+For our classification, we used the raw results (unnormalized) of cosine similarity, which produces a score between -1, and 1.
+Cosine similarity score of 0 indicates orthogonal relationship between the two vectors, which in our scenario indicates that the two sentences, and by extension their attributes are not related to each other.
+-1 indicates, inverse relationship between the attributes, while 1 indicates the two attributes are very much the same.
+For producing our schema maps, we are interested in three types of relationships, ``equal" (the two attributes are same), ``related" (the two attributes are related to each other), and ``unrelated" (no relationship between the attributes).
+In order to classify the similarity results, into one of these three classes, we then calculated the best thresholds, using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal", ``related", and ``unrelated".
+Finally on a test dataset we evaluated our multi-class classification approach, to identify the relationships between each pair of attributes.

### 2021-06-02 Implementation/AnnotatedDataHandler_3.py

@@ -93,7 +93,7 @@ class AnnotatedDataHandler:
         #                        "0.8-0.2", "0.9-0.1"]
         self.result_indexes = ["0.0-1.0"]
         self.computational_iteration = "1.7"
-        self.result_iteration = ".3"
+        self.result_iteration = ".5"
         self.notSynAndSem = ["FUZZY_MATCH", "Word2Vec"]
         self.computed_method = ['bert-base-nli-stsb-mean-tokens',
                                 'bert-large-nli-stsb-mean-tokens',
@@ -520,6 +520,49 @@ class AnnotatedDataHandler:
         return result_as_dict
         # self.log(["*"] * 80)
 
+    def calculateOvrBetweenComputedAndAnnotatedData(self, dataset):
+        performance_dict = {}
+        development_y = dataset['dev_y']
+        # result_as_csv_str = "\r\n"
+        # print("result_as_dict:", result_as_dict)
+
+        # Base methods
+        for m in self.notSynAndSem:
+            if m not in performance_dict:
+                performance_dict[m] = {}
+            if len(self.computed_data[m]) < 1:
+                self.log("Insufficient data for measuring performance of the computed methods, have you read the files yet?")
+                return
+            # self.log('Cohen kappa score  between ' + m + ' and avg(annotators): ')
+            data_in_1d = self.collapseDataSetTo1dArrayWithHeaders(self.computed_data[m]["0-0"])
+            development_x = [data_in_1d[i] for i in dataset['dev_x_index']]
+            if "0-0" not in performance_dict[m]:
+                performance_dict[m]["0-0"] = {}
+            performance_dict[m]["0-0"] = self.calculate_ovr_conditions(development_x, development_y)
+        # print(self.computed_data)
+        for m in self.computed_method:
+            if m not in performance_dict:
+                performance_dict[m] = {}
+            for _syn_sem_threshold in self.result_indexes:
+                if len(self.computed_data[m]) < 1:
+                    self.log("Insufficient data for the computed methods, have you read the files yet?")
+                    return
+                # self.log('Cohen kappa score  between ' + m + ' and avg(annotators): ')
+                data_in_1d = self.collapseDataSetTo1dArrayWithHeaders(self.computed_data[m][_syn_sem_threshold])
+                development_x = [data_in_1d[i] for i in dataset['dev_x_index']]
+
+                if _syn_sem_threshold not in performance_dict[m]:
[…]

### 2021-06-02 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
test results

@@
 al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$).
-Each of these medical systems follow the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
+Each of these medical systems as shown in \textbf{figSchema}, follows the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
 While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.
@@
 \label{schema_prepro}
-In order to process the EMR schema set $S$ and produce a set of corresponding semantically enriched sentences, we use the methodology shown in \textbf{figAlgorithm}.
-First we use the data representation $s_i$, generated through the process explained above (\ref{schema_acq}) to collect the various medical fragments in memory.
+In order to process the EMR schema set $S$ and produce a set of corresponding semantically enriched sentences, we use the data representation $s_i$, generated through the process explained in sequence acquisition to collect the various medical fragments in memory.
 We then iterate over these fragments, building a set of attributes, distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.

### 2021-06-02 Implementation/AnnotatedDataHandler_3.py

@@ -106,16 +106,33 @@ class AnnotatedDataHandler:
                                 'roberta-large-nli-mean-tokens',
                                 'distilbert-base-nli-mean-tokens'
                                 ]
+        self.class_equal = "1.0"
+        self.class_related = "0.5"
+        self.class_unrelated = "0.0"
+
+        self.max_thresholds = { 'Word2Vec': {self.class_unrelated:0.05, self.class_related:0.1},
+                                'FUZZY_MATCH': {self.class_unrelated:0.7, self.class_related:0.75},
+                                'bert-base-nli-stsb-mean-tokens': {self.class_unrelated:0.85, self.class_related:0.9} ,
+                                'bert-large-nli-stsb-mean-tokens': {self.class_unrelated:0.85, self.class_related:0.9},
+                                'roberta-base-nli-stsb-mean-tokens': {self.class_unrelated:0.85, self.class_related:0.9},
+                                'roberta-large-nli-stsb-mean-tokens': {self.class_unrelated:0.85, self.class_related:0.9},
+                                'distilbert-base-nli-stsb-mean-tokens': {self.class_unrelated:0.85, self.class_related:0.9},
+                                'bert-base-nli-mean-tokens': {self.class_unrelated:0.9, self.class_related:0.95},
+                                'bert-large-nli-mean-tokens': {self.class_unrelated:0.75, self.class_related:0.9},
+                                'roberta-base-nli-mean-tokens': {self.class_unrelated:0.9, self.class_related:0.95},
+                                'roberta-large-nli-mean-tokens': {self.class_unrelated:0.9, self.class_related:0.95},
+                                'distilbert-base-nli-mean-tokens': {self.class_unrelated:0.9, self.class_related:0.95}
+                               }
+
         # Computed Data Structures
         self.computed_data = {}
+        self.test_data = {}
         for m in self.notSynAndSem:
             self.computed_data[m] = {}
         for m in self.computed_method:
             self.computed_data[m] = {}
 
-        self.class_equal = "1.0"
-        self.class_related = "0.5"
-        self.class_unrelated = "0.0"
+
         # self.roc_dict = {}
         # self.max_roc_dict = {}
         # self.prc_dict = {}
@@ -520,6 +537,82 @@ class AnnotatedDataHandler:
         return result_as_dict
         # self.log(["*"] * 80)
 
[…]

### 2021-06-02 Implementation/AnnotatedDataHandler_4.py
Results calculation

@@ -1,0 +1,1030 @@
+import csv
+import os
+from scipy.stats import pearsonr
+import numpy as np
+import re
+import pandas as pd
+import sys
+from statistics import mode, StatisticsError
+import math
+# from matplotlib import pyplot as plt
+from decimal import Decimal
+from sklearn.metrics import cohen_kappa_score, accuracy_score, classification_report, multilabel_confusion_matrix, \
+    confusion_matrix, roc_curve, roc_auc_score, precision_recall_curve, auc, matthews_corrcoef
+from sklearn.datasets import make_classification
+from sklearn.model_selection import train_test_split
+
+np.seterr('raise')
+
+
+# list1 = [1, 2, 3, 4, 5, 6, 8, 1, 2]
+# list2 = [1, 3, 5, 2, 5, 6, 8, 2 ,1 ]
+# score = cohen_kappa_score(list1, list2)
+# print("score: ", score)
+# exit()
+
+def get_kappa_correlation_score(list1, list2):
+    kappaCorrelationBetweenLists = []
+    list1Class = [t[2] for t in list1]
+    list2Class = [t[2] for t in list2]
+    d_score = cohen_kappa_score(list1Class, list2Class)
+    # formatted_d_score = str(round(d_score, 2))
+    return d_score
+
+def get_Mcc_score(y_true_tuple, y_pred_tuple):
+    kappaCorrelationBetweenLists = []
+    y_true = [t[2] for t in y_true_tuple]
+    y_pred = [t[2] for t in y_pred_tuple]
+
+    # C = confusion_matrix(y_true, y_pred, sample_weight=None)
+    # t_sum = C.sum(axis=1, dtype=np.float64)
+    # p_sum = C.sum(axis=0, dtype=np.float64)
+    # n_correct = np.trace(C, dtype=np.float64)
+    # n_samples = p_sum.sum()
+    # print("n_correct * n_samples:", n_correct * n_samples)
+    # print("np.dot(t_sum, p_sum):", np.dot(t_sum, p_sum))
+    # cov_ytyp = n_correct * n_samples - np.dot(t_sum, p_sum)
+    # cov_ypyp = n_samples ** 2 - np.dot(p_sum, p_sum)
+    # cov_ytyt = n_samples ** 2 - np.dot(t_sum, t_sum)
+    # print("cov_ytyp:",cov_ytyp)
+    # print("cov_ytyt:",cov_ytyt)
+    # print("cov_ypyp:",cov_ypyp)
[…]

### 2021-06-02 Implementation/similarity.py

@@ -9,7 +9,7 @@ import torch
 from numba import njit, cuda, prange
 from numba import jit
 import numpy as np
-from fastdist import fastdist
+#from fastdist import fastdist
 from numpy import dot
 from numpy.linalg import norm
 
@@ -723,6 +723,8 @@ data = simObj.readData('Data/AmplifiedSimilarity-V0.3.txt')
 
 print('data')
 print(len(data))
+
+exit()
 
 # data = simObj.calcualteBaseLineSimilarity(data)
 

### 2021-06-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
fixes
Annotator table and graph

@@
 The same is shown by the \textbf{orange} colored peaks in this dataset, which in all cases is either equivalent to the other approaches ($D_f$ and $D_b$), or better than them.
+
+\begin{table}[]
+	\begin{tabular}{|l|l|l|l|l|l|}
+		\hline
+		Method     & Total Matches & Marked as Equal & Marked as Related & Marked as Unrelated & Not Marked \\ \hline
+		Annotator1 & 40698         & 238             & 109               & 40351               & 0          \\ \hline
+		Annotator2 & 40698         & 241             & 116               & 40341               & 0          \\ \hline
+		Annotator3 & 40698         & 260             & 2103              & 38182               & 153        \\ \hline
+		Annotator4 & 40698         & 225             & 62                & 40400               & 11         \\ \hline
+	\end{tabular}
+\end{table}

### 2021-06-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/experimentalsetup.tex
fixes
update

@@
 The resulting set of enriched attributes are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps.
-This process, is used to create 21,873  distinct pairs of attributes, across $s$.
+This process, is used to create 20,349 distinct pairs of attributes, across $s$.
 Each pair also contains the ``relationshipList", which stores the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
-The ``json" file thus produced, is then used by a python script to generate the semantically enriched sentences and their embedded vectors using WordNet, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
+The ``json" file thus produced, is then used by a python script to generate the semantically enriched sentences and their embedded vectors using Word2Vec, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
 The BERT models include 'bert-base-nli-stsb-mean-tokens', 'bert-large-nli-stsb-mean-tokens', 'roberta-base-nli-stsb-mean-tokens', 'roberta-large-nli-stsb-mean-tokens', 'distilbert-base-nli-stsb-mean-tokens', 'bert-base-nli-mean-tokens', 'bert-large-nli-mean-tokens', 'roberta-base-nli-mean-tokens', 'roberta-large-nli-mean-tokens', and 'distilbert-base-nli-mean-tokens'.
@@
 These applications were executed on a workstation running Ubuntu 20.04.2 LTS on top of AMD Ryzen 3 2200G, and 32GB ram.
-
-In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal", ``related", or ``unrelated" 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
-In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-".
-Following this, the annotators, marked each cell corresponding to a pair of attributes, by determining the similarity in terms of dissimilar as ``0", exactly similar as ``1", row attribute as child of column attribute as ``<", row attribute as a parent of the column attribute as ``>", and finally, unknown as ``~".
-The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
-These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
-Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in \textbf{figKappaScore}.
-The 7 permutations, amongst the 4 annotators, generate 261 kappa scores, where each individual score corresponds to the correlation of agreement between two annotators.
-Further, each score identifies the agreement in terms of scoring a set of paired attributes, while keeping the row attribute constant, and moving along the 261 column attributes.
-Finally we produced a consolidated dataset, using mode scores of all annotators, for each attribute pair.
-This dataset is then split into development and testing partitions with a ratio of 70:30.
-The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal", followed by best scores for class ``related" and finally best of class "unrelated".
-The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and F-1 score.

### 2021-06-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
update

@@
 This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas.
-\textbf{Traditional NLP techniques such as WordNet are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence.} However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
+\textbf{Traditional NLP techniques such as Word2Vec are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence.} However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
 In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names.
@@
 al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$).
-Each of these medical systems as shown in \textbf{figSchema}, follows the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
+Each of these medical systems as shown in \ref{fig:schemas}, follows the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
 While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.
@@
 This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each EMR attribute.
-While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as \textbf{stsb-roberta-large} provides the best results.
+While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with Word2Vec and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as \textbf{stsb-roberta-large} provides the best results.
 The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them.

### 2021-06-03 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
update

--- 2021-03-31 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
@@
 
-The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed syntactic and semantic matching process with fuzzy string matching, only semantic matching of attribute names using sentence embedding, and with multiple human annotated versions of the schema map.
-Using the 21,873 AA pairs, we created a two dimensional matrix, of AA identifiers, whereby each cell refers to a ``SchemaName\_TableName\_AttributeName" element.
-All nodes, for which the SchemaName part of the name is same, are then marked with ``-", and these are omitted from further processing.
-This various versions of this dataset (D) are available at \textbf{url}.
+The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed semantic matching process with fuzzy string matching, embedded vector generation and comparison using Word2Vec, and 10 BERT nli models.
+
+\subsection*{Dataset Annotation}
+In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal", ``related", or ``unrelated" 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
+In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-".
+Following this, the annotators, marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells, with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0", exactly similar as ``1", row attribute as child of column attribute as ``<", row attribute as a parent of the column attribute as ``>", and finally, unknown as ``~".
+The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
+These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
+Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in \ref{fig:kappaInterAnnotatorAgrement}.
+It can be seen in this plot, that ``Annotator3" has very small correlation with the other 3 annotators.
+This difference can be traced back to the number and type of annotations performed by each annotator, which is shown in Table \ref{tab:annotator_marking}.
+The ``Annotator3" has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty.
+However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness.
+This annotated data was then processed, to replace all related entries with ``0.5" and all``-" with ``0", while the values for similar at ``1" and ``0" for dissimilar were kept the same.
+This conversion was then used to produce a consolidated dataset of 40,698 attribute pairs, using mode scores of all annotators, for each cell.
+We also tested average scores between the annotators, but that would produce scores between ``0", ``0.5", and ``1", greatly increasing the number of classes for classification.
+Hence the maximum agreement between the annotators, maintains the final label values within these three classes, which become easier to evaluate.
+Additionally, the original dataset and its mode consolidated form is biased in favour of class "0", since most attribute pairs are not related to each other.
+This dataset is then split into development and testing partitions with a ratio of 70:30.
+The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal", followed by best scores for class ``related" and finally best of class "unrelated".
+The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and F-1 score.
+\subsection*{Threshold Selection}
 
@@
 
-\textbf{Threshold Selection}
 Overall, the number of similarities above the threshold values of ``0.8" are greatly increased from $D_f$, to $D_b$, and then to $D_p$ (proposed methodology).

### 2021-06-03 ManuScript/IEEEAccess/ManuScript.tex
IEEE Access tempalte

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Preparation of Papers for IEEE ACCESS}
\author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
\uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
Jr}.\authorrefmark{3},
\IEEEmembership{Member, IEEE}}
\address[1]{National Institute of Standards and 
Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
\address[2]{Department of Physics, Colorado State University, Fort Collins, 
CO 80523 USA (e-mail: author@lamar.colostate.edu)}
\address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
80309 USA}
\tfootnote{This paragraph of the first footnote will contain support 
information, including sponsor and financial support acknowledgment. For 
example, ``This work was supported in part by the U.S. Department of 
Commerce under Grant BS123456.''}

\markboth
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}

\corresp{Corresponding author: First A. Author (e-mail: author@ boulder.nist.gov).}

\begin{abstract}
Abstract goes here.
\end{abstract}

\begin{keywords}
Enter key words or phrases in alphabetical 
order, separated by commas. For a list of suggested keywords, send a blank 
e-mail to keywords@ieee.org or visit \underline
{http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
\end{keywords}

\titlepgskip=-15pt

\maketitle

\section{Introduction}
\label{intro}
\PARstart{D}{ata} and Information modeling in the healthcare domain have witnessed significant improvements in the last decade owing to advances in the development of state-of-the-art information and communication technologies (ICT) and formalization of storage and messaging standards. Subsequently, the scope of Healthcare Management Information Systems (HMIS), medical ontologies, and Clinical Decision Support Systems (CDSS) has broadened, beyond the operational capabilities of traditional rule based systems. One of the major reasons behind this limitation is due to the numerous heterogeneities in healthcare at data, knowledge, and process level. Thus, healthcare interoperability which aims to provide a solution to this problem, can be compartmentalized into data interoperability, process interoperability, and knowledge interoperability.
Data interoperability resolves the heterogeneity between data artificats, to enable, seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International HL7, and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
On the other hand, process interoperability regulates the communication among organizational processes to provide compatability between process artifacts within and seamless transformations across different organizations\cite{khan2013process}. Lastly, knowledge interoperability provides a sharing mechanism for reusing interpretable medical knowledge, acquired through expert intervention and other mechanisms, across decision support systems \cite{ali2017multi}.
In more tangible terms, healthcare interoperability at data, process, and knowledge level can be exemplified within the healthcare constraints experienced due to the emergence of Covid 19. The operational capabilities of the current healthcare service delivery infrastructure has gone under tremendous stress due to Covid 19. World over, large primary healthcare units have managed to create separate units for managing patients, suffering from extreme cases of the novel coronavirus. For secondary and tertiary care units, government involvement has become necessary to filter coronavirus patients and adhering to a national pandemic response policy. 
These complex circumstances have enhanced the need for sharing patient data and state-of-the-art medical knowledge in real-time, to provide the medical experts with a tool to make accurate and timely decisions.
Data interoperability can enable the front line medical workers to fetch, understand, and use patient data, especially comorbidities, across organizational and physical boundaries, without suffering from societal taboos that may prevent the patient from sharing their complete and accurate medical histories. Knowledge interoperability can improve the knowledge acquisition and sharing protocols to provide the medical experts such as epidieomologists and vaccinologist, with latest information on affected population trends, disease diagnosis, treatment, and followup procedures, and interpretable decisions leading to positive or negative outcomes. Process interoperability can help reduce and in some cases remove the operational redundancies between health centers. In this way, successive healthcare treatments can take benefit from earlier diagnosis, treatment, and followup procedures, thereby reducing the stress on healthcare experts and systems.
Standards such as Health Level Seven (HL7) Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols. While systematized nomenclature of medicine—clinical terms (Snomed-CT) \cite{snomedct_url} and logical observation identifiers names and codes (LOINC) \cite{loinc} provide a standard definition for clinical terminologies and laboratory tests, respectively. Similarly Medical Logic Module (MLM) provides a standardized way for expressing medical knowledge. However, the plethora of standards, necessitates the creation of bridging standards, that can resolve the heterogeniety between the medical standards. Substantial effort has gone into this endeavor with the Clinical Information Modeling Initiative (CIMI) \cite{CIMI2015} taking the lead in bridging the gap between HL7v3 and openEHR. Similarly, SNOMED CT and LOINC are working to resolve the redundancies between the two terminological standards since 2013. This healthcare interoperability solution follows a formal, albiet long process, which is greatly dependent on the human factor. However, the current healthcare scenario, requires a quick solution to create a scaffolding of an interoperable bridge between various healthcare providers. It is also important to ensure that this scaffolding should be able to support the formal standardization processes of the future. In \cite{Satti2020}we have presented the Ubiquitous Health Platform (UHP), which provides semantic reconciliation-on-read based data curation for resolving data interoperability between various schema. This methodology is based on the creation and management of schema maps, that can provide the framework for transforming a source schema into a target schema. 
In the current manuscript, we will present our research work to build and manage the schema map knowledge base. Overall, our methodology is based on the creation, evaluation, and application of a novel schema matching technique to identify the relationships between attributes of the participating medical data schema. These will be presented in detail, with following flow:

\begin{itemize}
	\item[$-$] Section \ref{methodology} contains the details of our methodology
	\item[$-$] Section \ref{experimentalSetup} provides the experimental setup
	\item[$-$] Section \ref{results} presents the results
	\item[$-$] Section \ref{relatedwork} presents the related work
	\item[$-$] Section 6 concludes the paper.
\end{itemize}

\section{Related Work}
\label{relatedwork}
Althubait et al. \cite{althubaiti2020combining} proposed an ontology expansion methodology that identifies and extracts new class from text articles using word embedding and machine learning techniques. The authors identified the similarity of tokens and phrases of the text articles with the exiting classes of the ontology. The target ontology is expanded with classes from text articles having greater similarity with that of already added classes. A similar word embedding technique was also used by Nozaki et al. \cite{nozaki2019semantic}, where the authors used instance based schema matching technique to identify the semantic similarity between two instances. The results of the study showed the possibility of detecting similar string attributes of different schemas. Yousfi et al. \cite{yousfi2020xmatcher} also utilized semantic base techniques and proposed xMatcher XML schemas matching approach. xMatcher transforms schemas into a set of words, followed by measuring words context, and relatedness score using WordNet. The terms from different schemas having similarities greater or equal to 0.8 are considered similar. 
Bylygin et al. \cite{bulygin2018combining} devised an ontology and schema matching approach by combining lexical and semantic similarity with machine learning approaches.  The authors used lexical and semantic measures as features and trained various machine learning algorithms including Naive Bayes, logistic regression, and gradient boosted tree. The result achieved showed that the combination of algorithms outperformed the single modal.

Martono et al. \cite{martono2017review} provided overview of previous studies related to linguistic approaches used for schema matching. Linguistic methods focused on finding strings and evaluate there similarity in different schemas. The string are normally normalized before to align both the strings before similarity comparison. The normalized strings are categories based on the information relatedness and element with similar category are compared using various similarity measure including  Jaro-distance, Lavenstein (edit-distance), and many more. Alwan et al. \cite{alwan2017survey} have summarized the techniques used in the literature for schemas and instances based schema matching. The information used for schema matching is categories into  schema information, instance and auxiliary information. Most of the searchers have used syntactic techniques (including n-gram, and regular expression), semantic techniques (including Latent Semantic Analysis, WordNet/Thesaurus and Google Similarity) for schema level and instance level matching to achieve the final goal of data/information interoperability.  Kersloot et al. \cite{kersloot2020natural} performed a comprehensive systematic review to evaluate natural language processing (NLP) algorithms used for clinical text mapping onto ontological concepts. The findings of the studies were evaluated with respect to five categories; use of NLP algorithms, data used, validation and evaluation performed, result presentation, and generalization of results. The authors revealed that over one-fourth of the NLP algorithms used were not evaluated and have no validation. The systems that claimed generalization, were self evaluated and having no external validation.

Xu et al. \cite{xu2003discovering} presented a framework for discovering indirect links besides direct links among schema elements. The indirect matches were detected for relations such as union, composition, decomposition, selection, and boolean. The indirect links are useful to handle concepts merge, split, generalization, and specialization. The matching techniques utilized in the study considered terminological relationships (word synonym and hypernym), structural characteristics, data-value characteristics, and expected data values. The experimental results revealed framework effectiveness by achieving more than 90\% precision and recall for direct and indirect link matching.

A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al. \cite{moll2020oncology} to check their perspectives regarding patient accessible electronic health record (PAEHR). The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations. The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions. However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.

\section{Methodology}
\label{methodology}
Healthcare interoperability, with a focus on non-standard compliant medical schema, is dependent on the generation and validation of schema maps, as discussed above. To this end, the creation of a cohesive workflow is of utmost importance. In our earlier work \cite{Satti2020} we used maximum sequence identification and suffix tress based matching for syntactic matching of two distinct data schemas. This was followed by semantic concept enrichment and subsequently concept matching, for creating rules in the form of schema maps. The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data, into an interpretable, model form.
In our current methodology we have utilized state-of-the-art natural language processing (NLP) techniques to extract the schema mapping rules from semi-structured data schemas. This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas. 
\textbf{Traditional NLP techniques such as WordNet are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence.} However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence. In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names. The bidirectional nature of BERT, allows the creation of contextual embedded vectors, where each target word is affected by its neighboring words. Hence to convert the set of suffixes into a sentence, we collected the set of concepts corresponding to each suffix, from Unified Medical Language System (UMLS). This operation has two effects, firstly it is used to remove any suffix, which does not have a corresponding concept and secondly the extracted concepts are used to add context to each suffix and produce a contextual sentence. 
The following subsections provide the practical details for our methodology, from schema acquisition, to attribute name expansion, and finally schema map generation.

\subsection{Schema acquisition}
\label{schema_acq}
In the first step of our semantic reconciliation methodology, we simulate medical data acquisition from five distinct EMR storage systems ($S$). These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et. al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$). Each of these medical systems as shown in \ref{figSchema}, follows the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables. While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.

%[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){schemas}
{Schemas used for knowledge interoperability.\label{figSchema}}

A similar notion of data heterogeneity, in terms of medical data schema, is evident across the healthcare domain. This is caused by various factors, including the lack of one all-encompassing, and universally applicable terminological standard and different normalization level for representing attributes.\\
In the former case, while SNOMED-CT provides a mechanism for identifying the standard codes for clinical terms and LOINC can be used for laboratory related terms, most attribute names are created based on the gut feeling of the database designer. Additionally, while these codes can be used to represent data instances, the data schema, achieves no benefit from the same.  Consider the terms ``name" and ``patientName", which refer to the same attribute of the patient entity.  However, since there is no standard way to represent this attribute, both are considered correct ($s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter).\\
In the later case, differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others. Similarly, ``EncounterDate" from $s_5$ is semantically similar to ``BeginDate" of ``openemr\_MedicalProblems" table in $s_1$, ``AdmissionStartDate" of ``LabsCorePopulatedTable" in $s_2$, 
``time" in ``Diagnosis" table of $s_3$, and  ``dateOfAdmission" in ``Diagnosis" and ``CareHistory" tables of $s_4$.
Finally, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, $s_5$. Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for these EMR storage systems.
In fact, the change in context of the EMR storage system from the initial time of development to a later stage of collaborative processing systems, is the main cause of heterogeneity. In order to provide an interoperable solution, it is therefore necessary to enhance the semantics of each EMR attribute by its contextually equivalent sentence.

\subsection{From Attribute to Sentence}
\label{schema_prepro}
In order to process the EMR schema set $S$ and produce a set of corresponding semantically enriched sentences, we use the data representation $s_i$, generated through the process explained in sequence acquisition to collect the various medical fragments in memory. We then iterate over these fragments, building a set of attributes, distinguished by their name, schema's name, table's name, schema's version, source, and recorded data. This entails that ``PatientID" from each of the four tables in $s_2$, and ``patientID" from five tables in $s_4$, would result into nine attributes (assuming, as in the current case, of no differences in versions of these systems).
For each attribute, we then generate the suffix array, which provides all possible substring representations contained within the attribute name. In order to generate the set of suffixes, we employ three strategies, forward suffix generation, whereby for a word $w$ of length $n$, $n-1$ suffixes of size 2 to $n-1$ are produced, backward suffix generation, to produce $n-1$ suffixes in reverse order with size $n-1$ to 2, and regular expression based suffix generation, which splits each word on, change of case, special characters(such as -, \_, !, and others), and numbers. An example of this suffix generation process is shown in \ref{figSuffixAttribute}. 
Here, the attribute ``DOB" in $s_1$, ``PatientDateOfBirth" appears in $s_2$, ``birthday" appears in $s_3$, ``DateOfBirth" in $s_5$, and ``birthDate" in $s_4$. These attributes refer to the same attribute of the patient entity, however, with the suffix generation process, our aim is to identify all words within these strings. While the forward and backward generation process, generates all possible sequences of characters as suffix, the regex based method, only identifies the changes in the string. In this way a large list of suffixes is generated, which is combined using a ``TreeSet" data structure of Java, which internally sorts this list as well.

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){suffixAttribute}
{Suffix attributes.\label{figSuffixAttribute}}

Similarly the attribute, ``dateOfAdmission" appears in $s_4$, while ``AdmissionStartDate". ``diseaseNameOnAdmission", and ``AdmissionEndDate" appear in $s_2$. As evident within these strings, while they refer to semantically different entity attributes, syntactically they contain similar elements. The suffixes generated from these strings are shown in \ref{figSuffixAttribute}. The suffix generation process, identified thus far, is only able to generate syntactic suffixes, producing many incoherent and unrelated suffixes. In order to counter this problem, and to limit the list of suffixes within the domain, we then query UMLS, with exact search strategy, looking for the existence of any concepts, against each suffix. In case, no semantic concept is found for a particular suffix, it is removed from the final Suffix Array. On the other hand, if atleast one semantic concept is found against the queried suffix, it is retained. Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible. 
The set of suffixes and their corresponding concepts are then used to build the sentence, where by each concept, corresponding to a suffix is appended next to the suffix. An example of the resultant sentence for the attribute ``DateOfAdmission" is shown as follows:\\

\framebox{\parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{\itshape%

		``Date Value type - Date date allergenic extract Date in time Data types - Date Date Fruit;Of SPI1 wt Allele SPI1 gene TAF1 wt Allele BRIP1 gene Within Degrees fahrenheit Oral contraception BRIP1 wt Allele;Da Displacement of abomasum dalton Anterior descending branch of left coronary artery deca units cytarabine/daunorubicin protocol Dai Chinese Asymptomatic diagnosis of Drug Accountability Domain;ion Iontophoresis Route of Drug Administration Ions;on SPARC wt Allele Osteonectin SPARC gene On (qualifier value) Upon - dosing instruction fragment;Admission Admission activity Hospital admission;Dat SLC6A3 gene SLC6A3 wt Allele dopamine transporter Direct Coombs test SLC6A3 protein, human Test Date cytarabine/daunorubicin/thioguanine Alzheimer's Disease;mission Religious Missions;"
}}\\

Here the various suffixes and their concepts are seperated by the symbol ``;", however together they form one sentence, for which an embedded vector is generated.

\subsection{Schema Map generation}
\label{schema_map_gen}

Schema Maps, provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the semantic relationship between their participating attributes. This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each EMR attribute. While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as \textbf{stsb-roberta-large} provides the best results. The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them. For our classification, we used the raw results (unnormalized) of cosine similarity, which produces a score between -1, and 1. Cosine similarity score of 0 indicates orthogonal relationship between the two vectors, which in our scenario indicates that the two sentences, and by extension their attributes are not related to each other. -1 indicates, inverse relationship between the attributes, while 1 indicates the two attributes are very much the same.
For producing our schema maps, we are interested in three types of relationships, ``equal" (the two attributes are same), ``related" (the two attributes are related to each other), and ``unrelated" (no relationship between the attributes). In order to classify the similarity results, into one of these three classes, we then calculated the best thresholds, using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal", ``related", and ``unrelated". Finally on a test dataset we evaluated our multi-class classification approach, to identify the relationships between each pair of attributes.

\section{Experimental Setup}
\label{experimentalSetup}
In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_5$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS). We extended the same setup to create an additional 100,000 records, for 1000 patients with 3 medical fragments for $s_1$, $s_2$, and $s_4$, and 97 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$. These fragments, follow various design elements, supporting a variety of valid relational storage architectures. Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure. The code to generate this data set is available at ``uhp\_map\_generation"\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhpr\_storage}. This application produces three custom formatted files, containing an index for patients, an index for their medical fragments, and the medical fragment, corresponding to the EMR data. Using the medical fragments file, we then generate the semantically enriched attribute \footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhp\_map\_generation}, which contains the suffixes and their concepts corresponding to each EMR data attribute. The resulting set of enriched attributes are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps. This process, is used to create 20,349 distinct pairs of attributes, across $s$. Each pair also contains the ``relationshipList", which stores the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names. 
The ``json" file thus produced, is then used by a python script to generate the semantically enriched sentences and their embedded vectors using Word2Vec, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}. The BERT models include 'bert-base-nli-stsb-mean-tokens', 'bert-large-nli-stsb-mean-tokens', 'roberta-base-nli-stsb-mean-tokens', 'roberta-large-nli-stsb-mean-tokens', 'distilbert-base-nli-stsb-mean-tokens', 'bert-base-nli-mean-tokens', 'bert-large-nli-mean-tokens', 'roberta-base-nli-mean-tokens', 'roberta-large-nli-mean-tokens', and 'distilbert-base-nli-mean-tokens'. 
The embedding vectors are then compared using cosine similarity, which produces a score between -1 and 1.
The rationale behind switching the applications at various stages, is to cache the results and create checkpoints for restarting any failed stages, easily. Additionally, since python provides better support for easy generation of embedding vectors, it was thus preferred over the Java based implementation, which is otherwise very beneficial for other tools. These applications were executed on a workstation running Ubuntu 20.04.2 LTS on top of AMD Ryzen 3 2200G, and 32GB ram.

\section{Results}
\label{results}

The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed semantic matching process with fuzzy string matching, embedded vector generation and comparison using Word2Vec, and 10 BERT nli models.

\subsection{Dataset Annotation}
In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal", ``related", or ``unrelated" 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names. In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-". Following this, the annotators, marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells, with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0", exactly similar as ``1", row attribute as child of column attribute as ``<", row attribute as a parent of the column attribute as ``>", and finally, unknown as ``~". The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0". Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in \ref{fig:kappaInterAnnotatorAgrement}. It can be seen in this plot, that ``Annotator3" has very small correlation with the other 3 annotators. This difference can be traced back to the number and type of annotations performed by each annotator, which is shown in Table \ref{tab:annotator_marking}. The ``Annotator3" has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty. However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness. 
This annotated data was then processed, to replace all related entries with ``0.5" and all``-" with ``0", while the values for similar at ``1" and ``0" for dissimilar were kept the same. This conversion was then used to produce a consolidated dataset of 40,698 attribute pairs, using mode scores of all annotators, for each cell. We also tested average scores between the annotators, but that would produce scores between ``0", ``0.5", and ``1", greatly increasing the number of classes for classification. Hence the maximum agreement between the annotators, maintains the final label values within these three classes, which become easier to evaluate. Additionally, the original dataset and its mode consolidated form is biased in favour of class "0", since most attribute pairs are not related to each other.
This dataset is then split into development and testing partitions with a ratio of 70:30. The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal", followed by best scores for class ``related" and finally best of class "unrelated". The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and F-1 score.

\subsection{Threshold Selection}

The results of fuzzy string comparison ($D_f$) on the attribute names of each pair, can be visualized using the heatmap shown in \textbf{figFuzzyWuzzy}. Similarly, the results of comparison using BERT based word embedding of the attribute names ($D_b$), is shown in \textbf{figBase}. Finally, the heatmap of the syntactic and semantic matching of the AA's using our proposed Algorithm \ref{knowledgeEvolAlgo} ($D_p$), is shown in \textbf{figSynAndSemMatching}. The values, for each cell range between ``0" and ``1", with higher values indicating a larger match between the elements, in each of these cases. The black areas of these heatmaps, indicate missing values, while white indicates a matching value of ``0". The few areas with red color, indicate the values above ``0.9", while blue areas indicate values above ``0.8".

Overall, the number of similarities above the threshold values of ``0.8" are greatly increased from $D_f$, to $D_b$, and then to $D_p$ (proposed methodology). Changing the threshold value in $D_p$ to ``0.9", brings it relatively closer to $D_b$. This is due to our proposed similarity matching methodology, which gives an equal score (0.5) to the values obtained from both syntactic and semantic matches. Since the decision made at the syntactic evaluation is binary (0 or 1), thus for a similarity score of ``0.8", in $D_p$, ``0.5" represents the syntactic similarity, and ``0.3" semantic similarity. The semantic similarity value, obtained from this rescaling process, would in turn represent an original value of ``0.6" from $D_b$. Therefore, for an equal semantic representation, the value of semantic similarity after rescaling (between 0 and 0.5) should be ``0.4", and originally ``0.8". \textbf{figSynAndSemMatching0.9} shows the heatmap, of similarity matrix, obtained from $D_p$ with the threshold values as ``0.9".

Generally, a comparison of these heatmaps, indicate an increase in the recall rate of the methodology. This is due to the fact, that our proposed methodology is able to match a larger number of AAs, providing 50\% of the score to the syntactic match, thereby increasing the count of cells without a missing value. This approach is also able to reduce the impact of semantic matching from names, which might contain repeated words, such as ``patient" but in reality refer to disparate concepts, such as ``PatientName" and "PatientDateOfBirth". Another important aspect of our matching process is the inclusion of semantic concepts and suffixes, as a sentence before its conversion to an embedded vector. As discussed earlier, this process is used to reduce the impact of syntactic matches alone, which would give a higher score to the attributes ``PatientName" and ``PatientGender", which refer to different concepts. The inclusion of concepts behind ``Name" and ``Gender" part of these names, allow for an improved comparison.

In order to evaluate the accuracy and precision rates of these methodologies, we then compared the results of our computed methods $D_f$, $D_b$, and $D_p$, with the average scored datasets by the human annotators. A visualization of the resultant Cohen's Kappa score for the 261 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}. The bar chart shown in this visualization, indicates, an overall greater positive agreement between our proposed methodolody $D_p$, and the average scores of the annotators. The same is shown by the \textbf{orange} colored peaks in this dataset, which in all cases is either equivalent to the other approaches ($D_f$ and $D_b$), or better than them.

\section{Conclusion}
Conclusion goes here.

\section*{Acknowledgment}

Acknowledgment goes here.

\bibliographystyle{unsrt}
\bibliography{references}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.png}}]{First A. Author} (M'76--SM'81--F'87) and all authors may include 
biographies. Biographies are often not included in conference-related
papers. This author became a Member (M) of IEEE in 1976, a Senior
Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may
contain a place and/or date of birth (list place, then date). Next,
the author's educational background is listed. The degrees should be
listed with type of degree in what field, which institution, city,
state, and country, and year the degree was earned. The author's major
field of study should be lower-cased.

The second paragraph uses the pronoun of the person (he or she) and not the 
author's last name. It lists military and work experience, including summer 
and fellowship jobs. Job titles are capitalized. The current job must have a 
location; previous positions may be listed 
without one. Information concerning previous publications may be included. 
Try not to list more than three books or published articles. The format for 
listing publishers of a book within the biography is: title of book 
(publisher name, year) similar to a reference. Current and previous research 
interests end the paragraph. The third paragraph begins with the author's 
title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). 
List any memberships in professional societies other than the IEEE. Finally, 
list any awards and work for IEEE committees and publications. If a 
photograph is provided, it should be of good quality, and 
professional-looking. Following are two examples of an author's biography.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]{Second B. Author} was born in Greenwich Village, New York, NY, USA in 
1977. He received the B.S. and M.S. degrees in aerospace engineering from 
the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in 
mechanical engineering from Drexel University, Philadelphia, PA, in 2008.

From 2001 to 2004, he was a Research Assistant with the Princeton Plasma 
Physics Laboratory. Since 2009, he has been an Assistant Professor with the 
Mechanical Engineering Department, Texas A{\&}M University, College Station. 
He is the author of three books, more than 150 articles, and more than 70 
inventions. His research interests include high-pressure and high-density 
nonthermal plasma discharge processes and applications, microscale plasma 
discharges, discharges in liquids, spectroscopic diagnostics, plasma 
propulsion, and innovation plasma applications. He is an Associate Editor of 
the journal \emph{Earth, Moon, Planets}, and holds two patents.

Dr. Author was a recipient of the International Association of Geomagnetism 
and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE 
Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.png}}]{Third C. Author, Jr.} (M'87) received the B.S. degree in mechanical 
engineering from National Chung Cheng University, Chiayi, Taiwan, in 2004 
and the M.S. degree in mechanical engineering from National Tsing Hua 
University, Hsinchu, Taiwan, in 2006. He is currently pursuing the Ph.D. 
degree in mechanical engineering at Texas A{\&}M University, College 
Station, TX, USA.

From 2008 to 2009, he was a Research Assistant with the Institute of 
Physics, Academia Sinica, Tapei, Taiwan. His research interest includes the 
development of surface processing and biological/medical treatment 
techniques using nonthermal atmospheric pressure plasmas, fundamental study 
of plasma sources, and fabrication of micro- or nanostructured surfaces.

Mr. Author's awards and honors include the Frew Fellowship (Australian 
Academy of Science), the I. I. Rabi Prize (APS), the European Frequency and 
Time Forum Award, the Carl Zeiss Research Award, the William F. Meggers 
Award and the Adolph Lomb Medal (OSA).
\end{IEEEbiography}

\EOD

\end{document}

### 2021-06-03 Implementation/AnnotatedDataHandler_4.py

@@ -424,9 +424,14 @@ class AnnotatedDataHandler:
 
         allKappaAnnotatedDataHandlers = "\r\n"
 
-        # self.log('Cohen kappa score  between annotator1 and annotator2: ')
-        # allKappaAnnotatedDataHandlers += "annotator1 vs annotator2," + str(annotatedDataHandler.get_kappa_correlation_score(annotator1DataFlat, annotator2DataFlat) )+ "\r\n"
-        # self.log(["*"] * 80)
+        self.log('Cohen kappa score  between annotator1 and annotator2: ')
+        allKappaAnnotatedDataHandlers += "annotator1 vs annotator2," + str(annotatedDataHandler.get_kappa_correlation_score(annotator1DataFlat, annotator2DataFlat) )+ "\r\n"
+        self.log(["*"] * 80)
+
+        self.log('Cohen kappa score  between annotator2 and annotator1: ')
+        allKappaAnnotatedDataHandlers += "annotator2 vs annotator1," + str(
+            annotatedDataHandler.get_kappa_correlation_score(annotator2DataFlat, annotator1DataFlat)) + "\r\n"
+        self.log(["*"] * 80)
 
         self.log('Cohen kappa score  between annotator1 and annotator3: ')
         allKappaAnnotatedDataHandlers += "annotator1 vs annotator3," + str(annotatedDataHandler.get_kappa_correlation_score(annotator1DataFlat,annotator3DataFlat)) + "\r\n"
@@ -910,6 +915,7 @@ annotatedDataHandler = AnnotatedDataHandler()
 # Now to convert the datasets into 1d
 annotatedDataHandler.readAllAnnotatorsData(True)
 annotatedDataHandler.calculateKappaScoreBetweenAnnotators()
+exit()
 
 
 

### 2021-06-03 ManuScript/IEEEAccess/ManuScript.tex
figure set
updated on ieee access format

@@
 
-%[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]
-
-\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){schemas}
-{Schemas used for knowledge interoperability.\label{figSchema}}
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[scale=0.53]{schemas}
+	\caption{Schemas used for knowledge interoperability.}
+	\label{figSchema}
+\end{figure*}
 
@@
 In order to generate the set of suffixes, we employ three strategies, forward suffix generation, whereby for a word $w$ of length $n$, $n-1$ suffixes of size 2 to $n-1$ are produced, backward suffix generation, to produce $n-1$ suffixes in reverse order with size $n-1$ to 2, and regular expression based suffix generation, which splits each word on, change of case, special characters(such as -, \_, !, and others), and numbers.
-An example of this suffix generation process is shown in \ref{figSuffixAttribute}.
-Here, the attribute ``DOB" in $s_1$, ``PatientDateOfBirth" appears in $s_2$, ``birthday" appears in $s_3$, ``DateOfBirth" in $s_5$, and ``birthDate" in $s_4$.
-These attributes refer to the same attribute of the patient entity, however, with the suffix generation process, our aim is to identify all words within these strings.
-While the forward and backward generation process, generates all possible sequences of characters as suffix, the regex based method, only identifies the changes in the string.
 In this way a large list of suffixes is generated, which is combined using a ``TreeSet" data structure of Java, which internally sorts this list as well.
+An example of this suffix generation process, using the attribute name ``dateOfAdmission" as it appears in $s_4$ is shown in \ref{figSuffixAttribute}.
 
-\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){suffixAttribute}
-{Suffix attributes.\label{figSuffixAttribute}}
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[scale=0.53]{suffixAttribute}
+	\caption{Suffix attributes.}
+	\label{figSuffixAttribute}
+\end{figure*}
 
-Similarly the attribute, ``dateOfAdmission" appears in $s_4$, while ``AdmissionStartDate".
-``diseaseNameOnAdmission", and ``AdmissionEndDate" appear in $s_2$.
-As evident within these strings, while they refer to semantically different entity attributes, syntactically they contain similar elements.
-The suffixes generated from these strings are shown in \ref{figSuffixAttribute}.
-The suffix generation process, identified thus far, is only able to generate syntactic suffixes, producing many incoherent and unrelated suffixes.
+Suffix strings for similar attributes such as ``AdmissionStartDate".
+``diseaseNameOnAdmission", and ``AdmissionEndDate" appear in $s_2$, produce many, synctactically similar suffixes, to the presented example.
+This process, is only able to generate syntactic suffixes, producing many incoherent and unrelated suffixes.
 In order to counter this problem, and to limit the list of suffixes within the domain, we then query UMLS, with exact search strategy, looking for the existence of any concepts, against each suffix.
@@
 This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each EMR attribute.
-While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as \textbf{stsb-roberta-large} provides the best results.
+While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as ``stsb-roberta-large" provides the best results.
 The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them.
@@
 The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics{kappaInterAnnotatorAgrement}
+	\caption{Cohen's Kappa (d) score between the four annotators}
+	\label{kappaInterAnnotatorAgrement}
+\end{figure*}
+
 These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
@@
 However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness.
+
+\begin{table}[h!]
+	\caption{Annotations performed by the four annotators on five medical schema}
+	\begin{tabular}{c|ccccc}
+		\hline
+		Method     & Total Matches & Marked as Equal & Marked as Related & Marked as Unrelated & Not Marked \\ \hline
+		Annotator1 & 40698         & 238             & 109               & 40351               & 0          \\
+		Annotator2 & 40698         & 241             & 116               & 40341               & 0          \\
+		Annotator3 & 40698         & 260             & 2103              & 38182               & 153        \\
+		Annotator4 & 40698         & 225             & 62                & 40400               & 11         \\ \hline
+	\end{tabular}
+	\label{tab:annotator_marking}
+\end{table}
+
 This annotated data was then processed, to replace all related entries with ``0.5" and all``-" with ``0", while the values for similar at ``1" and ``0" for dissimilar were kept the same.

### 2021-06-03 ManuScript/IEEEAccess/ManuScript.tex
update
updated abbreviations

@@
 \label{intro}
-\PARstart{D}{ata} and Information modeling in the healthcare domain have witnessed significant improvements in the last decade owing to advances in the development of state-of-the-art information and communication technologies (ICT) and formalization of storage and messaging standards.
+\PARstart{D}{ata} and Information modeling in the healthcare domain have witnessed significant improvements in the last decade owing to advances in the development of state-of-the-art Information and Communication Technologies (ICT) and formalization of storage and messaging standards.
 Subsequently, the scope of Healthcare Management Information Systems (HMIS), medical ontologies, and Clinical Decision Support Systems (CDSS) has broadened, beyond the operational capabilities of traditional rule based systems.
@@
 Thus, healthcare interoperability which aims to provide a solution to this problem, can be compartmentalized into data interoperability, process interoperability, and knowledge interoperability.
-Data interoperability resolves the heterogeneity between data artificats, to enable, seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International HL7, and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
+Various abbreviations, used in this manuscript are listed in Table \ref{tab:abbreviations}.
+
+\begin{table}[]
+	\centering
+	\caption{Abbreviations}
+	\label{tab:abbreviations}
+	\begin{tabular}{ll}
+		\hline
+		Abbreviations              & Full Form                                               \\ \hline
+		ICT                        & Information and Communication Technologies              \\
+		HMIS                       & Healthcare Management Information Systems               \\
+		CDSS                       & Clinical Decision Support Systems                       \\
+		HL7                        & Health Level Seven International                        \\
+		HIMSS                      & Healthcare Information and Management Systems Society   \\
+		FHIR                       & Fast Healthcare Interoperability Resources              \\
+		Snomed-CT                  & Systematized Nomenclature of Medicine—Clinical Terms    \\
+		LOINC                      & Logical Observation Identifiers Names and Codes         \\
+		MLM                        & Medical Logic Module                                    \\
+		CIMI                       & Clinical Information Modeling Initiative                \\
+		UHP                        & Ubiquitous Health Platform                              \\
+		NLP                        & Natural Language Processing                             \\
+		BERT                       & Bidirectional Encoder Representations from Transformers \\
+		UMLS                       & Unified Medical Language System                         \\
+		EMR 					   & Electronic Medical Records                              \\
+		EHR						   & Electronic Health Records                               \\
+		MCC                        & Matthews Correlation coefficient                        \\
+		NLI                        & Natural Language Inference                              \\ \hline
+	\end{tabular}
+\end{table}
+
+Data interoperability resolves the heterogeneity between data artificats, to enable, seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International (HL7), and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
 On the other hand, process interoperability regulates the communication among organizational processes to provide compatability between process artifacts within and seamless transformations across different organizations\cite{khan2013process}.
@@
 In this way, successive healthcare treatments can take benefit from earlier diagnosis, treatment, and followup procedures, thereby reducing the stress on healthcare experts and systems.
-Standards such as Health Level Seven (HL7) Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
-While systematized nomenclature of medicine—clinical terms (Snomed-CT) \cite{snomedct_url} and logical observation identifiers names and codes (LOINC) \cite{loinc} provide a standard definition for clinical terminologies and laboratory tests, respectively.
+Standards such as HL7 - Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
+While Systematized Nomenclature of Medicine—Clinical Terms (Snomed-CT) \cite{snomedct_url} and Logical Observation Identifiers Names and Codes (LOINC) \cite{loinc} provide a standard definition for clinical terminologies and laboratory tests, respectively.
 Similarly Medical Logic Module (MLM) provides a standardized way for expressing medical knowledge.
@@
 Kersloot et al.
-\cite{kersloot2020natural} performed a comprehensive systematic review to evaluate natural language processing (NLP) algorithms used for clinical text mapping onto ontological concepts.
+\cite{kersloot2020natural} performed a comprehensive systematic review to evaluate Natural Language Processing (NLP) algorithms used for clinical text mapping onto ontological concepts.
 The findings of the studies were evaluated with respect to five categories; use of NLP algorithms, data used, validation and evaluation performed, result presentation, and generalization of results.
@@
 A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al.
-\cite{moll2020oncology} to check their perspectives regarding patient accessible electronic health record (PAEHR).
+\cite{moll2020oncology} to check their perspectives regarding Patient Accessible Electronic Health Record (PAEHR).
 The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations.
@@
 \label{schema_acq}
-In the first step of our semantic reconciliation methodology, we simulate medical data acquisition from five distinct EMR storage systems ($S$).
+In the first step of our semantic reconciliation methodology, we simulate medical data acquisition from five distinct Electronic Medical Records (EMR) storage systems ($S$).
 These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
 al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$).
-Each of these medical systems as shown in \ref{figSchema}, follows the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
+Each of these medical systems as shown in \ref{fig:schema}, follows the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
 While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.
@@
 	\includegraphics[scale=0.53]{schemas}
-	\caption{Schemas used for knowledge interoperability.}
-	\label{figSchema}
+	\caption{The five medical schemas used for achieving data interoperability.}
+	\label{fig:schema}
 \end{figure*}
@@
 Finally, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, $s_5$.
-Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for these EMR storage systems.
-In fact, the change in context of the EMR storage system from the initial time of development to a later stage of collaborative processing systems, is the main cause of heterogeneity.
-In order to provide an interoperable solution, it is therefore necessary to enhance the semantics of each EMR attribute by its contextually equivalent sentence.
+Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for the EMR/EHR storage systems.
+In fact, the change in context of the medical data storage system from the initial time of development to a later stage of collaborative processing systems, is the main cause of heterogeneity.
+In order to provide an interoperable solution, it is therefore necessary to enhance the semantics of each data attribute by its contextually equivalent sentence.
 
@@
 \label{schema_prepro}
-In order to process the EMR schema set $S$ and produce a set of corresponding semantically enriched sentences, we use the data representation $s_i$, generated through the process explained in sequence acquisition to collect the various medical fragments in memory.
+In order to process the EMR/EHR schema set $S$ and produce a set of corresponding semantically enriched sentences, we use the data representation $s_i$, generated through the process explained in sequence acquisition to collect the various medical fragments in memory.
 We then iterate over these fragments, building a set of attributes, distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.
@@
 In this way a large list of suffixes is generated, which is combined using a ``TreeSet" data structure of Java, which internally sorts this list as well.
-An example of this suffix generation process, using the attribute name ``dateOfAdmission" as it appears in $s_4$ is shown in \ref{figSuffixAttribute}.
+An example of this suffix generation process, using the attribute name ``dateOfAdmission" as it appears in $s_4$ is shown in \ref{fig:suffix_attribute}.
 
@@
 	\caption{Suffix attributes.}
-	\label{figSuffixAttribute}
+	\label{fig:suffix_attribute}
 \end{figure*}
@@
 Schema Maps, provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the semantic relationship between their participating attributes.
-This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each EMR attribute.
+This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each data attribute.
 While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as ``stsb-roberta-large" provides the best results.
@@
 Additionally, since python provides better support for easy generation of embedding vectors, it was thus preferred over the Java based implementation, which is otherwise very beneficial for other tools.
-These applications were executed on a workstation running Ubuntu 20.04.2 LTS on top of AMD Ryzen 3 2200G, and 32GB ram.
+These applications were executed on a workstation running Ubuntu 20.04.2 on top of AMD Ryzen 3 2200G, and 32GB ram.
 
@@
 	\caption{Cohen's Kappa (d) score between the four annotators}
-	\label{kappaInterAnnotatorAgrement}
+	\label{fig:kappaInterAnnotatorAgrement}
 \end{figure*}
@@
 These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
-Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in \ref{fig:kappaInterAnnotatorAgrement}.
+Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
 It can be seen in this plot, that ``Annotator3" has very small correlation with the other 3 annotators.
@@
 
-\begin{table}[h!]
+\begin{table*}
+	\centering
 	\caption{Annotations performed by the four annotators on five medical schema}
-	\begin{tabular}{c|ccccc}
+	\label{tab:annotator_marking}
+	\begin{tabular}{|l|l|l|l|l|l|}
 		\hline
@@
 	\end{tabular}
-	\label{tab:annotator_marking}
-\end{table}
+\end{table*}
 
@@
 \subsection{Threshold Selection}
+A good text classification methodology is dependent on the correct choice of a threshold, which can maximize the target class participation.
+In case of independent labels, area under the precision recall curve can provide this optimal measure, however as in our case, for dependent classes on a biased dataset the Matthews Correlation Coefficient (MCC), is better\cite{chicco2020advantages}.
+Since our aim is to apply an optimal text similarity classifier to resolve this multi-class problem (class 0, class 0.5, and class 1), we have to test various threshold scores for separating the instances between 0 and 0.5 ($t_1$), and then 0.5 and 1($t_2$).
+Additionally, since our aim is to correctly identify the similar attribute instances, it is pertinent to maximize the classification performance of class 1 (similar), followed by class 0.5 (related), and finally class 0 (unrelated).
+With a step size of 0.05 ($step_size$), and starting from $t_1$ as 0.0 and $t_2$ as $t_1$ + $step_size$, we move the thresholds until $t_2$ reaches 1, followed by increase in $t_1$ by step size.
+Eventually, $t_1$, reaches 0.95 and $t_2$ reaches 1, at which point, the process stops.
+This is to ensure that $t_1$ remains behind $t_2$, for all iterations, measuring MCC score, for the 12 models.
+These models include, ``Fuzzy\_Wuzzy", ``Word2Vec", and 10 BERT models.
 

### 2021-06-03 ManuScript/IEEEAccess/ManuScript.tex
threshold selection graphs
results

@@
 This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each data attribute.
-While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models of BERT further detailed in section \ref{experimentalSetup}), the large/STSb version of the Siamese BERT-Networks \cite{reimers-2019-sentence-bert}, commonly known as ``stsb-roberta-large" provides the best results.
+While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models based on BERT (including BERT base, BERT large, distilBert, and RoBERTa) further detailed in section \ref{experimentalSetup}), the large/STSb version of RoBERTa\cite{reimers-2019-sentence-bert},provides the best results.
 The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them.
@@
 This is to ensure that $t_1$ remains behind $t_2$, for all iterations, measuring MCC score, for the 12 models.
-These models include, ``Fuzzy\_Wuzzy", ``Word2Vec", and 10 BERT models.
+These models include, ``Fuzzy\_Wuzzy", ``Word2Vec", and 10 BERT based models.
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[scale=0.83]{thresholdSelection}
+	\caption{Thresholds selection.}
+	\label{fig:thresholdSelection}
+\end{figure*}
+Threshold values for Word2Vec are placed at the lower end of the spectrum, indicating a very large number of instances are classified as similar (above similarity score of 0.1), while a small number of instances (with similarity score 0.05) are classified as dissimilar.
+Similarly, the class related lies within the similarity threshold of 0.05 similarity points.
+It can be observed that the threshold for selecting the related class, is within 0.05 points, in all except one case (bert-large-nli-mean-tokens where the difference is 0.15 points).
+Five BERT based models, trained on the STSb dataset, all have minimum threshold values of 0.85 and maximum of 0.9, while the 4 remaining BERT models, lie between 0.9 and 0.95.
+These results show a general trend, of how the cosine similarity varies/maintains itself, against embedded vectors generated from various pre-trained models.
+In absolute terms, however these threshold values provide the mechanism for classifying the test dataset, which is evaluated for performance, in the next subsection.
+
+\subsection{Model Evaluation}
+On unseen test dataset,
 

### 2021-06-03 Implementation/AnnotatedDataHandler_3.py

@@ -575,6 +575,44 @@ class AnnotatedDataHandler:
         return result_as_dict
         # self.log(["*"] * 80)
 
+    def calculatePerformanceOnTest(self, dataset):
+        result_as_dict = {}
+        test_y = dataset['test_y']
+        # result_as_csv_str = "\r\n"
+        # print("result_as_dict:", result_as_dict)
+
+        # Base methods
+        for m in self.notSynAndSem:
+            if m not in result_as_dict:
+                result_as_dict[m] = {}
+            if len(self.test_data[m]) < 1:
+                self.log("Insufficient data for the computed methods, have you read the files yet?")
+                return
+            # self.log('Cohen kappa score  between ' + m + ' and avg(annotators): ')
+            data_in_1d = self.collapseDataSetTo1dArrayWithHeaders(self.test_data[m])
+            test_x = [data_in_1d[i] for i in dataset['test_x_index']]
+            result_as_dict[m] = self.calculate_ovr_conditions(test_x, test_y)
+        # print(self.computed_data)
+        for m in self.computed_method:
+            if m not in result_as_dict:
+                result_as_dict[m] = {}
+            for _syn_sem_threshold in self.result_indexes:
+                if len(self.test_data[m]) < 1:
+                    self.log("Insufficient data for the computed methods, have you read the files yet?")
+                    return
+                # self.log('Cohen kappa score  between ' + m + ' and avg(annotators): ')
+                data_in_1d = self.collapseDataSetTo1dArrayWithHeaders(self.test_data[m])
+                test_x = [data_in_1d[i] for i in dataset['test_x_index']]
+
+                result_as_dict[m] = self.calculate_ovr_conditions(test_x, test_y)
+
+                # result_as_csv_str += m + "-" + str(syn_sem_threshold) + " vs mode(annotators)," + \
+                #                      get_kappa_correlation_score(data_in_1d, annotated_data) + "\r\n"
+
+        # print("result_as_csv_str2:", result_as_dict)
+        return result_as_dict
+        # self.log(["*"] * 80)
+
     def calculateKapaaOnTest(self, dataset):
         result_as_dict = {}
         test_y = dataset['test_y']
@@ -790,10 +828,10 @@ class AnnotatedDataHandler:
         y_pred = [t[2] for t in y_pred_tuple]
 
         cm = confusion_matrix(y_true, y_pred, sample_weight=None)
-
+        performance_table = {}
         performance_dict = {}
         for pc_index, positiveClass in enumerate(self.classes):
-
[…]

### 2021-06-03 ManuScript/IEEEAccess/ManuScript.tex
Update ManuScript.tex

@@
 \subsection{Model Evaluation}
-On unseen test dataset,
+On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-class classification and overall as well.
+In the first case, we evaluated
+
+Finally, we evaluated the
 

### 2021-06-03 ManuScript/IEEEAccess/ManuScript.tex
evaluation graph

@@
 \end{figure*}
+
 Threshold values for Word2Vec are placed at the lower end of the spectrum, indicating a very large number of instances are classified as similar (above similarity score of 0.1), while a small number of instances (with similarity score 0.05) are classified as dissimilar.
@@
 The few areas with red color, indicate the values above ``0.9", while blue areas indicate values above ``0.8".
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[scale=0.83]{evaluation}
+	\caption{Models evaluation.}
+	\label{fig:evaluation}
+\end{figure*}
 

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
updates

@@
 \title{Preparation of Papers for IEEE ACCESS}
-\author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
-\uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
-Jr}.\authorrefmark{3},
+
+\author{ \uppercase{Fahad Ahmed Satti}\authorrefmark{1,2},
+	\uppercase{Musarrat Hussain}\authorrefmark{1},
+	\uppercase{Jamil Hussain}\authorrefmark{3},
+	\uppercase{Syed Imran Ali}\authorrefmark{1}, % \IEEEmembership{} 
+	\uppercase{Taqdir Ali}\authorrefmark{1},
+	\uppercase{Hafiz Syed Muhammad Bilal}\authorrefmark{1,2},
+	\uppercase{TaeChoog Chung}\authorrefmark{1},and  \uppercase {Sungyoung Lee}\authorrefmark{1}
 	\IEEEmembership{Member, IEEE}}
-\address[1]{National Institute of Standards and 
-Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
-\address[2]{Department of Physics, Colorado State University, Fort Collins, 
-CO 80523 USA (e-mail: author@lamar.colostate.edu)}
-\address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
-80309 USA}
-\tfootnote{This paragraph of the first footnote will contain support 
-information, including sponsor and financial support acknowledgment. For 
-example, ``This work was supported in part by the U.S. Department of 
-Commerce under Grant BS123456.''}
+\address[1]{Department of Computer Science and Engineering, Kyung Hee University, Seocheon-dong, Giheung-gu South Korea (e-mail: \{fahad.satti, musarrat.hussain, imran.ali, bilalrizvi, sylee\}@oslab.khu.ac.kr,  \{tcchung, ghpark\}@khu.ac.kr)}
+\address[2]{National Univeristy of Sciences and Technology, School of Electrical Engineering and Computer Science NUST-SEECS, Islamabad, Pakistan (e-mail: \{fahad.satti, bilal.ali\}@seecs.edu.pk)}
+\address[3]{Department of Data Science, Sejong University, Seoul, South Korea (e-mail: jamil@sejong.ac.kr)}
+\tfootnote{}
 
 \markboth
-{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
+{Fahad \headeretal:Ensemble feature ranking for cost-based non-overlapping groups}
+{Fahad \headeretal:Ensemble feature ranking for cost-based non-overlapping groups}
 
-\corresp{Corresponding author: First A. Author (e-mail: author@ boulder.nist.gov).}
+\corresp{Corresponding authors: Sungyoung Lee (e-mail: sylee@oslab.khu.ac.kr) and TaeChoog Chung (e-mail: tcchung@@khu.ac.kr)}
 
 \begin{abstract}
-Abstract goes here.
+Data, information, and knowledge processing systems, in the domain of healthcare are currently plagued by the heterogeneity at various levels.
+Current solutions, have focused on developing a standard based, manual intervention mechanism, which requires a large amount of human resource and necessitate realignment of existing systems.
+State-of-the-art methodologies in the field of natural language processing and machine learning, can help to partially automate this process, reducing the resource requirements and providing a relatively good multi-class based classification algorithm.
+We present a novel methodology for bridging the gap between various healthcare data management solutions by leveraging the strength of transformer based machine learning models, to create mappings between the data elements.
+Additionally, the annotated data, collected against five medical schemas and labeled by 4 annotators is made available for helping future researchers.
+Our results indicate, that for biased, dependent multi-class text classification, RoBERTa shows the best performance, achieving a cohen's kappa score of 0.47 and MCC score of 0.48, with human annotated data.
 \end{abstract}
@@
 \begin{keywords}
-Enter key words or phrases in alphabetical 
-order, separated by commas. For a list of suggested keywords, send a blank 
-e-mail to keywords@ieee.org or visit \underline
-{http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
+Electronic medical records, Health information management, Medical information systems,  Text processing, Unsupervised learning
 \end{keywords}
@@
 
-\begin{figure*}[t!]
+\begin{figure}[]
 	\centering
-	\includegraphics{kappaInterAnnotatorAgrement}
-	\caption{Cohen's Kappa (d) score between the four annotators}
+	\includegraphics[width=\columnwidth]{kappaInterAnnotatorAgrement}
+	\caption{Cohen's Kappa ($\kappa$) score between the four annotators}
 	\label{fig:kappaInterAnnotatorAgrement}
-\end{figure*}
+\end{figure}
 
 These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
-Using \textbf{Cohen's Kappa score (d)}, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
+Using Cohen's Kappa score ($\kappa$) \cite{gwet2014handbook}, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
 It can be seen in this plot, that ``Annotator3" has very small correlation with the other 3 annotators.
@@
 \subsection{Model Evaluation}
-On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-class classification and overall as well.
-In the first case, we evaluated
+On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-classes.
 
-Finally, we evaluated the
-
-The results of fuzzy string comparison ($D_f$) on the attribute names of each pair, can be visualized using the heatmap shown in \textbf{figFuzzyWuzzy}.
-Similarly, the results of comparison using BERT based word embedding of the attribute names ($D_b$), is shown in \textbf{figBase}.
-Finally, the heatmap of the syntactic and semantic matching of the AA's using our proposed Algorithm \ref{knowledgeEvolAlgo} ($D_p$), is shown in \textbf{figSynAndSemMatching}.
-The values, for each cell range between ``0" and ``1", with higher values indicating a larger match between the elements, in each of these cases.
-The black areas of these heatmaps, indicate missing values, while white indicates a matching value of ``0".
-The few areas with red color, indicate the values above ``0.9", while blue areas indicate values above ``0.8".
+Finally, we evaluated the overall $\kappa$ coefficient and MCC score to evaluate the performance of each model on the test dataset.
+These measures range between [0,1], and provide a measure quantifying the accuracy of the classifier to correctly predict correct and incorrect instances.
+The models Word2Vec, bert-large-nli-mean-tokens, and roberta-base-nli-mean-tokens, with values between [0,0.20] indicate random classification, while $\kappa$ score between [0.21,0.39], achieved by fuzzy wuzzy, bert-base-nli-mean-tokens, roberta-base-nli-sts-mean-tokens, distilbert-base-nli-stsb-mean-tokens, bert-base-nli-mean-tokens, roberta-large-nli-mean-tokens, and distilbert-base-nli-mean-tokens, show only minimal agreement with the annotated data \cite{mchugh2012interrater}.
+Relative best rates, in this case, are achieved by roberta-large-nli-stsb-mean-tokens, which substantially surpasses the other models, however in absolute terms, it shows only weak agreement.
+Similarly, MCC scores show a similar result, with roberta-large-nli-stsb-mean-tokens, achieving the relative best performance amongst all classifiers.
 
@@
 
-Overall, the number of similarities above the threshold values of ``0.8" are greatly increased from $D_f$, to $D_b$, and then to $D_p$ (proposed methodology).
-Changing the threshold value in $D_p$ to ``0.9", brings it relatively closer to $D_b$.
-This is due to our proposed similarity matching methodology, which gives an equal score (0.5) to the values obtained from both syntactic and semantic matches.
-Since the decision made at the syntactic evaluation is binary (0 or 1), thus for a similarity score of ``0.8", in $D_p$, ``0.5" represents the syntactic similarity, and ``0.3" semantic similarity.
-The semantic similarity value, obtained from this rescaling process, would in turn represent an original value of ``0.6" from $D_b$.
-Therefore, for an equal semantic representation, the value of semantic similarity after rescaling (between 0 and 0.5) should be ``0.4", and originally ``0.8".
-\textbf{figSynAndSemMatching0.9} shows the heatmap, of similarity matrix, obtained from $D_p$ with the threshold values as ``0.9".
+\section{Discussion}
 
-Generally, a comparison of these heatmaps, indicate an increase in the recall rate of the methodology.
-This is due to the fact, that our proposed methodology is able to match a larger number of AAs, providing 50\% of the score to the syntactic match, thereby increasing the count of cells without a missing value.
-This approach is also able to reduce the impact of semantic matching from names, which might contain repeated words, such as ``patient" but in reality refer to disparate concepts, such as ``PatientName" and "PatientDateOfBirth".
-Another important aspect of our matching process is the inclusion of semantic concepts and suffixes, as a sentence before its conversion to an embedded vector.
-As discussed earlier, this process is used to reduce the impact of syntactic matches alone, which would give a higher score to the attributes ``PatientName" and ``PatientGender", which refer to different concepts.
-The inclusion of concepts behind ``Name" and ``Gender" part of these names, allow for an improved comparison.
+$F_1$ score, which provides the harmonic mean of precision and recall, ranges between 0 and 1, while MCC provides a fair measure of the ability with which a classifier can correctly predict both positive and negative instances \cite{chicco2020advantages}.
 
-In order to evaluate the accuracy and precision rates of these methodologies, we then compared the results of our computed methods $D_f$, $D_b$, and $D_p$, with the average scored datasets by the human annotators.
-A visualization of the resultant Cohen's Kappa score for the 261 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}.
-The bar chart shown in this visualization, indicates, an overall greater positive agreement between our proposed methodolody $D_p$, and the average scores of the annotators.
-The same is shown by the \textbf{orange} colored peaks in this dataset, which in all cases is either equivalent to the other approaches ($D_f$ and $D_b$), or better than them.
+Normalized MCC -> linear interpolation
+x := (c - a) / (b - a)
 
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.png}}]{First A. Author} (M'76--SM'81--F'87) and all authors may include 
-biographies. Biographies are often not included in conference-related
-papers. This author became a Member (M) of IEEE in 1976, a Senior
-Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may
-contain a place and/or date of birth (list place, then date). Next,
-the author's educational background is listed. The degrees should be
-listed with type of degree in what field, which institution, city,
-state, and country, and year the degree was earned. The author's major
-field of study should be lower-cased.
+% orcid: 0000-0002-9883-3355
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{FA.jpg}}]{Fahad Ahmed Satti}  is currently pursuing Ph.D.
+in Computer Engineering from Kyung Hee University, South Korea.
+He completed his MS in Computer Science from University of Trento, Italy in 2014.
+His primary research interest is directed towards providing a technical solution to resolve the lack of interoperability in information systems.
+In general, he is interested in domains of semantic matching, stream reasoning, knowledge extraction, and machine learning.
 
-The second paragraph uses the pronoun of the person (he or she) and not the 
-author's last name. It lists military and work experience, including summer 
-and fellowship jobs. Job titles are capitalized. The current job must have a 
-location; previous positions may be listed 
-without one. Information concerning previous publications may be included. 
-Try not to list more than three books or published articles. The format for 
-listing publishers of a book within the biography is: title of book 
-(publisher name, year) similar to a reference. Current and previous research 
-interests end the paragraph. The third paragraph begins with the author's 
-title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). 
-List any memberships in professional societies other than the IEEE. Finally, 
-list any awards and work for IEEE committees and publications. If a 
-photograph is provided, it should be of good quality, and 
-professional-looking. Following are two examples of an author's biography.
 \end{IEEEbiography}
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]{Second B. Author} was born in Greenwich Village, New York, NY, USA in 
-1977. He received the B.S. and M.S. degrees in aerospace engineering from 
-the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in 
-mechanical engineering from Drexel University, Philadelphia, PA, in 2008.
-
-From 2001 to 2004, he was a Research Assistant with the Princeton Plasma 
-Physics Laboratory. Since 2009, he has been an Assistant Professor with the 
-Mechanical Engineering Department, Texas A{\&}M University, College Station. 
-He is the author of three books, more than 150 articles, and more than 70 
-inventions. His research interests include high-pressure and high-density 
-nonthermal plasma discharge processes and applications, microscale plasma 
-discharges, discharges in liquids, spectroscopic diagnostics, plasma 
-propulsion, and innovation plasma applications. He is an Associate Editor of 
-the journal \emph{Earth, Moon, Planets}, and holds two patents.
-
-Dr. Author was a recipient of the International Association of Geomagnetism 
-and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE 
-Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
+% orcid: 0000-0001-8450-6946
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{S2.jpg}}]{Syed Imran Ali} received the BS degree in Computer Science from IQRA University, Islamabad in 2008 and MS degree in Computer Science From National University of Computer and Emerging Sciences (NUCES) in 2012.
+He has taught in NUCES as an adjunct faculty.
+He is currently pursuing Ph.D.
+degree from Department of Computer Science and Engineering, Kyung Hee University, South Korea.
+His area of interests include machine learning, health analytics and data-driven systems.
 \end{IEEEbiography}
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.png}}]{Third C. Author, Jr.} (M'87) received the B.S. degree in mechanical 
-engineering from National Chung Cheng University, Chiayi, Taiwan, in 2004 
-and the M.S. degree in mechanical engineering from National Tsing Hua 
-University, Hsinchu, Taiwan, in 2006. He is currently pursuing the Ph.D. 
-degree in mechanical engineering at Texas A{\&}M University, College 
-Station, TX, USA.
+% orcid: 0000-0002-8920-4231
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{b2.jpg}}]{Hafiz Syed Muhammad Bilal}  received the M.S.
+degree in computer science from National University of Sciences and Technology, Pakistan,in 2008.
+He is currently pursuing the Ph.D.
+degree in computer science and engineering at Kyung Hee University, South Korea.
+He has working experience of more than three years in data science and open source development and is actively involved in developing big data ecosystem for academic and health care.
+His research interests include behavior quantification \& assessment, machine learning, and behavior modeling \& adaptation.
+\end{IEEEbiography}
 
-From 2008 to 2009, he was a Research Assistant with the Institute of 
-Physics, Academia Sinica, Tapei, Taiwan. His research interest includes the 
-development of surface processing and biological/medical treatment 
-techniques using nonthermal atmospheric pressure plasmas, fundamental study 
-of plasma sources, and fabrication of micro- or nanostructured surfaces.
+% orcid: 0000-0003-4494-1593
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M3.jpg}}]{Musarrat Hussain} is a Ph.D.
+candidate in the Ubiquitous Computing Laboratory, Kyung Hee University, 	South Korea.
+He has completed his MS software Engineering in 2015 from National University of Science 	and Technology (NUST) Pakistan.
+His research interests include clinical text mining, knowledge 	extraction and representation, and machine learning.
 
-Mr. Author's awards and honors include the Frew Fellowship (Australian 
-Academy of Science), the I. I. Rabi Prize (APS), the European Frequency and 
-Time Forum Award, the Carl Zeiss Research Award, the William F. Meggers 
-Award and the Adolph Lomb Medal (OSA).
+\end{IEEEbiography}
+
+% orcid: 0000-0003-3862-8787
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J2.jpg}}]{Jamil Hussain} received the Ph.D.
+degree from the Department of Computer Engineering, Kyung Hee University, South Korea.
+in 2019.
+He is currently working as a postdoctoral researcher in the Ubiquitous Computing Laboratory, Kyung Hee University, South Korea.
+He has a professional experience of over 7 years in software industry working on user experience design and development on various projects.
+His research interest includes user experience design, artificial intelligence, and information extraction from textual data.
+
+\end{IEEEbiography}
+
+%orcid: 0000-0002-1663-1718
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Maq3.jpg}}]{Maqbool Hussain}  received the B.S.
+degree 	in computer science from the Kohat University of Science and Technology, Kohat, Pakistan, the M.S.
+degree from the School of Electrical Engineering and Computer Science, National University of Sciences and Technology, Pakistan, in 2009, and the Ph.D.
+degree from Kyung Hee University, South Korea, in 2016.
+He is currently an Assistant Professor with Sejong University, South Korea.
+He is also working as a Visiting Scholar with Oakland	University, Michigan, USA.
+He has more than eight years software development experience and involve in consultation and development of hospital system with collaboration of medical experts.
+His research interests include	artificial intelligence, and healthcare interoperability standards and clinical decision support systems.
+
+\end{IEEEbiography}
+
+% orcid: 0000-0001-7133-8285
+%(M'95SM'14)
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{G1.jpg}}]{Gwang Hoon Park}  received the B.S.
+and M.S.
+degrees in electronic engineering from Yonsei University, Seoul, South Korea, in 1985 and 1987, respectively, and the M.S.
+and Ph.D.
+degrees in electrical engineering and applied physics from Case Western Reserve University, OH, USA, in 1991 and 1995, respectively.
+He was a Principal Research Engineer with the Information and Telecommunication Research and Development Center, Hyundai Electronics Industries, Icheon, South Korea, from 1995 to 1997, and an Associate Professor with the Department of Computer Science, Yonsei University, Wonju, South Korea, from 1997 to 2001.
+Since 2001, he has been a Professor with the Department of Computer Engineering, Kyung Hee University, South Korea.
+His research interests include video signal processing, multimedia systems, pattern recognition, and computational intelligence.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{TC.jpg}}]{Tae Choong Chung}  received his B.S.
+degree in Electronic Engineering from Seoul National University, Republic of Korea, in 1980, and his M.S.
+and Ph.D.
+degrees in Computer Science from KAIST, Republic of Korea, in 1982 and 1987, respectively.
+Since 1988, he has been with the Department of Computer Science and Engineering, Kyung Hee University, Republic of Korea, where he is now a Professor.
+His research interests include machine learning, meta search, and robotics.
+\end{IEEEbiography}
+
+% orcid: 0000-0002-5962-1587
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.png}}]{Sungyoung Lee} received the B.S.degree from Korea University, Seoul, South Korea,and the M.S.
+and Ph.D.
+degrees in computer science from the Illinois Institute of Technology,Chicago, IL, USA, in 1987 and 1991, respectively.He was an Assistant Professor with the Department of Computer Science, Governors State University, University Park, IL, USA, from 1992 to 1993.
+He has been a Professor with the Department of Computer Engineering, Kyung Hee University,South Korea, since 1993, where he has been the Director of the Neo Medical ubiquitous-Life Care Information Technology Research Center since 2006.He is currently the Founding Director of the Ubiquitous Computing Laboratory.
+His current research interests include ubiquitous computing and applications, wireless ad hoc and sensor networks, context-aware middle-ware, sensor operating systems, real-time systems and embedded systems,and activity and emotion recognition.
+He is a member of ACM.
 \end{IEEEbiography}

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
table upated

@@
 \usepackage{textcomp}
+\usepackage{multirow}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table*}
+	\centering
+	\caption{One vs all binary classifications results}
+	\label{tab:evaluations}
+	\begin{tabular}{|c|c|c|l|l|l|l|l|}
+		\hline
+		\textbf{Model}                                        & \textbf{Class Positive} & \textbf{Class Negative} & \multicolumn{1}{c|}{\textbf{accuracy}} & \multicolumn{1}{c|}{\textbf{precision}} & \multicolumn{1}{c|}{\textbf{recall}} & \multicolumn{1}{c|}{\textbf{f-1}} & \multicolumn{1}{c|}{\textbf{mcc}} \\ \hline
+		\multirow{3}{*}{FUZZY\_MATCH}                         & 0.0                     & 0.5,1                   & 0.98                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.98                                   & 0.20                                    & 0.59                                 & 0.29                              & 0.33                              \\ \hline
+		\multirow{3}{*}{Word2Vec}                             & 0.0                     & 0.5,1                   & 0.24                                   & 0.99                                    & 0.24                                 & 0.38                              & 0.01                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.15                                    & 0.10                                 & 0.12                              & 0.12                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.35                                   & 0.01                                    & \textbf{0.84}                        & 0.01                              & 0.03                              \\ \hline
+		\multirow{3}{*}{bert-base-nli-stsb-mean-tokens}       & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.99                                   & 0.22                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
+		\multirow{3}{*}{bert-large-nli-stsb-mean-tokens}      & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.51                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.99                                   & 0.41                                    & 0.50                                 & 0.45                              & 0.45                              \\ \hline
+		\multirow{3}{*}{roberta-base-nli-stsb-mean-tokens}    & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 1.00                              & 0.40                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.99                                   & 0.26                                    & 0.50                                 & 0.34                              & 0.36                              \\ \hline
+		\multirow{3}{*}{roberta-large-nli-stsb-mean-tokens}   & 0.0                     & 0.5,1                   & 1.00                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.61                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & \textbf{1.00}                          & \textbf{0.59}                           & 0.50                                 & \textbf{0.54}                     & \textbf{0.54}                     \\ \hline
+		\multirow{3}{*}{distilbert-base-nli-stsb-mean-tokens} & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.38                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.99                                   & 0.23                                    & 0.50                                 & 0.32                              & 0.33                              \\ \hline
+		\multirow{3}{*}{bert-base-nli-mean-tokens}            & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.35                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.99                                   & 0.20                                    & 0.50                                 & 0.29                              & 0.31                              \\ \hline
+		\multirow{3}{*}{bert-large-nli-mean-tokens}           & 0.0                     & 0.5,1                   & 0.28                                   & 1.00                                    & 0.27                                 & 0.43                              & 0.05                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 0.99                                   & 0.34                                    & 0.90                                 & 0.49                              & 0.55                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.57                                   & 0.00                                    & 0.50                                 & 0.01                              & 0.01                              \\ \hline
+		\multirow{3}{*}{roberta-base-nli-mean-tokens}         & 0.0                     & 0.5,1                   & 0.96                                   & 1.00                                    & 0.97                                 & 0.98                              & 0.23                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.96                                   & 0.08                                    & 0.50                                 & 0.13                              & 0.19                              \\ \hline
+		\multirow{3}{*}{roberta-large-nli-mean-tokens}        & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.39                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.99                                   & 0.20                                    & 0.50                                 & 0.28                              & 0.31                              \\ \hline
+		\multirow{3}{*}{distilbert-base-nli-mean-tokens}      & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.36                              \\ \cline{2-8}
+		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& 1                       & 0.0,0.5                 & 0.99                                   & 0.21                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
+	\end{tabular}
+\end{table*}
+
 Finally, we evaluated the overall $\kappa$ coefficient and MCC score to evaluate the performance of each model on the test dataset.
@@
 % orcid: 0000-0002-9883-3355
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{FA.jpg}}]{Fahad Ahmed Satti}  is currently pursuing Ph.D.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Fahad Ahmed Satti}  is currently pursuing Ph.D.
 in Computer Engineering from Kyung Hee University, South Korea.
@@
 % orcid: 0000-0001-8450-6946
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{S2.jpg}}]{Syed Imran Ali} received the BS degree in Computer Science from IQRA University, Islamabad in 2008 and MS degree in Computer Science From National University of Computer and Emerging Sciences (NUCES) in 2012.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Syed Imran Ali} received the BS degree in Computer Science from IQRA University, Islamabad in 2008 and MS degree in Computer Science From National University of Computer and Emerging Sciences (NUCES) in 2012.
 He has taught in NUCES as an adjunct faculty.
@@
 % orcid: 0000-0002-8920-4231
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{b2.jpg}}]{Hafiz Syed Muhammad Bilal}  received the M.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Hafiz Syed Muhammad Bilal}  received the M.S.
 degree in computer science from National University of Sciences and Technology, Pakistan,in 2008.
@@
 % orcid: 0000-0003-4494-1593
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M3.jpg}}]{Musarrat Hussain} is a Ph.D.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Musarrat Hussain} is a Ph.D.
 candidate in the Ubiquitous Computing Laboratory, Kyung Hee University, 	South Korea.
@@
 % orcid: 0000-0003-3862-8787
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J2.jpg}}]{Jamil Hussain} received the Ph.D.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Jamil Hussain} received the Ph.D.
 degree from the Department of Computer Engineering, Kyung Hee University, South Korea.
@@
 %orcid: 0000-0002-1663-1718
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Maq3.jpg}}]{Maqbool Hussain}  received the B.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Maqbool Hussain}  received the B.S.
 degree 	in computer science from the Kohat University of Science and Technology, Kohat, Pakistan, the M.S.
@@
 %(M'95SM'14)
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{G1.jpg}}]{Gwang Hoon Park}  received the B.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Gwang Hoon Park}  received the B.S.
 and M.S.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{TC.jpg}}]{Tae Choong Chung}  received his B.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Tae Choong Chung}  received his B.S.
 degree in Electronic Engineering from Seoul National University, Republic of Korea, in 1980, and his M.S.
@@
 % orcid: 0000-0002-5962-1587
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.png}}]{Sungyoung Lee} received the B.S.degree from Korea University, Seoul, South Korea,and the M.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Sungyoung Lee} received the B.S.degree from Korea University, Seoul, South Korea,and the M.S.
 and Ph.D.

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
updated with bio and acknowledgements

@@
 
-\title{Preparation of Papers for IEEE ACCESS}
+\title{}
 
@@
 	\uppercase{Hafiz Syed Muhammad Bilal}\authorrefmark{1,2},
-	\uppercase{TaeChoog Chung}\authorrefmark{1},and  \uppercase {Sungyoung Lee}\authorrefmark{1}
+	\uppercase{TaeChoong Chung}\authorrefmark{1},and  \uppercase {Sungyoung Lee}\authorrefmark{1}
 	\IEEEmembership{Member, IEEE}}
-\address[1]{Department of Computer Science and Engineering, Kyung Hee University, Seocheon-dong, Giheung-gu South Korea (e-mail: \{fahad.satti, musarrat.hussain, imran.ali, bilalrizvi, sylee\}@oslab.khu.ac.kr,  \{tcchung, ghpark\}@khu.ac.kr)}
+\address[1]{Department of Computer Science and Engineering, Kyung Hee University, Seocheon-dong, Giheung-gu South Korea (e-mail: \{fahad.satti, musarrat.hussain, imran.ali, bilalrizvi, sylee\}@oslab.khu.ac.kr,  tcchung@khu.ac.kr)}
 \address[2]{National Univeristy of Sciences and Technology, School of Electrical Engineering and Computer Science NUST-SEECS, Islamabad, Pakistan (e-mail: \{fahad.satti, bilal.ali\}@seecs.edu.pk)}
@@
 % \usepackage{multirow}
-\begin{table*}
+\begin{table*}[h!]
 	\centering
@@
 \section*{Acknowledgment}
-
-Acknowledgment goes here.
+This research was supported by the MSIT(Ministry of Science and ICT), Korea, under the ITRC(Information Technology Research Center) support program(IITP-2017-0-01629) supervised by the IITP(Institute for Information \& communications Technology Promotion), IITP-2017-0-00655, NRF-2016K1A3A7A03951968, and NRF-2019R1A2C2090504.
 
@@
 % orcid: 0000-0002-9883-3355
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Fahad Ahmed Satti}  is currently pursuing Ph.D.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fahad.jpg}}]{Fahad Ahmed Satti} is currently pursuing Ph.D.
 in Computer Engineering from Kyung Hee University, South Korea.
@@
 In general, he is interested in domains of semantic matching, stream reasoning, knowledge extraction, and machine learning.
-
 \end{IEEEbiography}
-
+% orcid: 0000-0003-4494-1593
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{musarrat.jpg}}]{Musarrat Hussain} is a Ph.D.
+candidate in the Ubiquitous Computing Laboratory, Kyung Hee University, 	South Korea.
+He has completed his MS software Engineering in 2015 from National University of Science 	and Technology (NUST) Pakistan.
+His research interests include clinical text mining, knowledge 	extraction and representation, and machine learning.
+\end{IEEEbiography}
+% orcid: 0000-0003-3862-8787
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jamil.jpg}}]{Jamil Hussain} received the Ph.D.
+degree from the Department of Computer Engineering, Kyung Hee University, South Korea in 2019.
+He worked as a postdoctoral researcher in the Ubiquitous Computing Laboratory, Kyung Hee University, South Korea, from Sep 2019 to Feb 2021.
+He is currently an Assistant Professor at Sejong University, South Korea.
+He has professional experience of over 7 years in the software industry, working on user experience design and development on various projects.
+His research interest includes user experience design, artificial intelligence, and information extraction from textual data.
+\end{IEEEbiography}
 % orcid: 0000-0001-8450-6946
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Syed Imran Ali} received the BS degree in Computer Science from IQRA University, Islamabad in 2008 and MS degree in Computer Science From National University of Computer and Emerging Sciences (NUCES) in 2012.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{imran.jpg}}]{Syed Imran Ali} received the BS degree in Computer Science from IQRA University, Islamabad in 2008 and MS degree in Computer Science From National University of Computer and Emerging Sciences (NUCES) in 2012.
 He has taught in NUCES as an adjunct faculty.
@@
 \end{IEEEbiography}
-
+% orcid: 0000-0001-8450-6946
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{taqdir.jpg}}]{Taqdir Ali} received the Ph.D.
+degree from the Department of Computer Engineering, Kyung Hee University, South Korea in 2019.
+He is currently working as a postdoctoral researcher in the Ubiquitous Computing Laboratory, Kyung Hee University, South Korea.
+From 2006 to 2011, he was a Senior Software Engineer, a System Analyst, and a Researcher in a reputable software house.
+His current research includes knowledge acquisition for clinical decision support systems, applications of machine learning, text processing, and e-health standardization.
+\end{IEEEbiography}
 % orcid: 0000-0002-8920-4231
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Hafiz Syed Muhammad Bilal}  received the M.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bilal.jpg}}]{Hafiz Syed Muhammad Bilal}  received the M.S.
 degree in computer science from National University of Sciences and Technology, Pakistan,in 2008.
@@
 \end{IEEEbiography}
-
-% orcid: 0000-0003-4494-1593
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Musarrat Hussain} is a Ph.D.
-candidate in the Ubiquitous Computing Laboratory, Kyung Hee University, 	South Korea.
-He has completed his MS software Engineering in 2015 from National University of Science 	and Technology (NUST) Pakistan.
-His research interests include clinical text mining, knowledge 	extraction and representation, and machine learning.
-
-\end{IEEEbiography}
-
-% orcid: 0000-0003-3862-8787
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Jamil Hussain} received the Ph.D.
-degree from the Department of Computer Engineering, Kyung Hee University, South Korea.
-in 2019.
-He is currently working as a postdoctoral researcher in the Ubiquitous Computing Laboratory, Kyung Hee University, South Korea.
-He has a professional experience of over 7 years in software industry working on user experience design and development on various projects.
-His research interest includes user experience design, artificial intelligence, and information extraction from textual data.
-
-\end{IEEEbiography}
-
-%orcid: 0000-0002-1663-1718
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Maqbool Hussain}  received the B.S.
-degree 	in computer science from the Kohat University of Science and Technology, Kohat, Pakistan, the M.S.
-degree from the School of Electrical Engineering and Computer Science, National University of Sciences and Technology, Pakistan, in 2009, and the Ph.D.
-degree from Kyung Hee University, South Korea, in 2016.
-He is currently an Assistant Professor with Sejong University, South Korea.
-He is also working as a Visiting Scholar with Oakland	University, Michigan, USA.
-He has more than eight years software development experience and involve in consultation and development of hospital system with collaboration of medical experts.
-His research interests include	artificial intelligence, and healthcare interoperability standards and clinical decision support systems.
-
-\end{IEEEbiography}
-
-% orcid: 0000-0001-7133-8285
-%(M'95SM'14)
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Gwang Hoon Park}  received the B.S.
-and M.S.
-degrees in electronic engineering from Yonsei University, Seoul, South Korea, in 1985 and 1987, respectively, and the M.S.
-and Ph.D.
-degrees in electrical engineering and applied physics from Case Western Reserve University, OH, USA, in 1991 and 1995, respectively.
-He was a Principal Research Engineer with the Information and Telecommunication Research and Development Center, Hyundai Electronics Industries, Icheon, South Korea, from 1995 to 1997, and an Associate Professor with the Department of Computer Science, Yonsei University, Wonju, South Korea, from 1997 to 2001.
-Since 2001, he has been a Professor with the Department of Computer Engineering, Kyung Hee University, South Korea.
-His research interests include video signal processing, multimedia systems, pattern recognition, and computational intelligence.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Tae Choong Chung}  received his B.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{prof_tcc.jpg}}]{Tae-Choong Chung}  received his B.S.
 degree in Electronic Engineering from Seoul National University, Republic of Korea, in 1980, and his M.S.
@@
 \end{IEEEbiography}
-
 % orcid: 0000-0002-5962-1587
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authors\/fahad.jpg}}]{Sungyoung Lee} received the B.S.degree from Korea University, Seoul, South Korea,and the M.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{prof_sylee.png}}]{Sungyoung Lee} received the B.S.degree from Korea University, Seoul, South Korea,and the M.S.
 and Ph.D.

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
Update ManuScript.tex

@@
 Overall, our methodology is based on the creation, evaluation, and application of a novel schema matching technique to identify the relationships between attributes of the participating medical data schema.
-These will be presented in detail, with following flow:
+Since the terms used to identify attributes in the data schemas are not defined in any standard way, it is important to first identify the component words of the attribute term and then to append semantic concepts with these to create a meaningful sentence.
+This process is based on \textbf{word expansion} using concept lookup from Unified Medical Language System (UMLS).
+Once the sentence has been created, it is then trivial to create its embedded vectors representation using transformer based pre-trained models.
+The cosine similarity of any two embedded vectors can then indicate the degree of similarity between the original attributes.
+The motivation behind this methodology along with its development and evaluation details will be presented in the following flow:
 
 \begin{itemize}
+	\item[$-$] Section \ref{relatedwork} presents the related work
 	\item[$-$] Section \ref{methodology} contains the details of our methodology
@@
 	\item[$-$] Section \ref{results} presents the results
-	\item[$-$] Section \ref{relatedwork} presents the related work
 	\item[$-$] Section 6 concludes the paper.
@@
 This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas.
-\textbf{Traditional NLP techniques such as WordNet are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence.} However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
+Traditional NLP techniques such as WordNet are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence \cite{zhu2018exploring}.
+However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
 In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names.
 The bidirectional nature of BERT, allows the creation of contextual embedded vectors, where each target word is affected by its neighboring words.
-Hence to convert the set of suffixes into a sentence, we collected the set of concepts corresponding to each suffix, from Unified Medical Language System (UMLS).
+Hence to convert the set of suffixes into a sentence, we collected the set of concepts corresponding to each suffix, from UMLS.
 This operation has two effects, firstly it is used to remove any suffix, which does not have a corresponding concept and secondly the extracted concepts are used to add context to each suffix and produce a contextual sentence.

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
reference adjusted
more updates

@@
 
-\title{}
+\title{Unsupervised Semantic Mapping for Healthcare Data Storage Schema}
 
@@
 Since the terms used to identify attributes in the data schemas are not defined in any standard way, it is important to first identify the component words of the attribute term and then to append semantic concepts with these to create a meaningful sentence.
-This process is based on \textbf{word expansion} using concept lookup from Unified Medical Language System (UMLS).
+This process is based on word expansion using concept lookup from Unified Medical Language System (UMLS).
 Once the sentence has been created, it is then trivial to create its embedded vectors representation using transformer based pre-trained models.
@@
 
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[scale=0.53]{schemas}
+	\caption{The five medical schemas used for achieving data interoperability.}
+	\label{fig:schema}
+\end{figure*}
+
 \section{Methodology}
@@
 
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[scale=0.53]{schemas}
-	\caption{The five medical schemas used for achieving data interoperability.}
-	\label{fig:schema}
-\end{figure*}
-
 A similar notion of data heterogeneity, in terms of medical data schema, is evident across the healthcare domain.
@@
 
+\begin{figure*}[tb!]
+	\centering
+	\includegraphics[scale=0.53]{suffixAttribute}
+	\caption{Suffix attributes.}
+	\label{fig:suffix_attribute}
+\end{figure*}
+
 \subsection{From Attribute to Sentence}
@@
 An example of this suffix generation process, using the attribute name ``dateOfAdmission" as it appears in $s_4$ is shown in \ref{fig:suffix_attribute}.
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[scale=0.53]{suffixAttribute}
-	\caption{Suffix attributes.}
-	\label{fig:suffix_attribute}
-\end{figure*}
 
@@
 In order to classify the similarity results, into one of these three classes, we then calculated the best thresholds, using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal", ``related", and ``unrelated".
-Finally on a test dataset we evaluated our multi-class classification approach, to identify the relationships between each pair of attributes.
+
+\begin{equation}
+MCC = \frac{(TP.FN) - (FP.FN)}{\sqrt{(TP+FP)(TP+FN)(TN+FP)(TN+FN)}}\longrightarrow [-1,1]
+\end{equation}
+MCC provides a fair measure of the ability with which a classifier can correctly predict both positive and negative instances \cite{chicco2020advantages}.
+MCC score of 0 represents random classification, however, with an increase in the number of true positives and true negatives, MCC moves closer to 1.
+It also takes into account the false positives and false negatives, which shift the mcc score towards -1.
+This measurement is markedly different from accuracy, that fails to account for imbalanced datasets and $F_1$ measure which is not affected by the true negative scores.
+As a result, MCC provides an acceptable alternate, in our current scenario comprising of imbalanced dataset (largely in favour of class ``unrelated") to measuring the true performance of the models, used for threshold selection and model evaluation.
+Finally on a test dataset we evaluated our multi-class classification approach, using MCC and Cohen's Kappa coefficient ($\kappa$) \cite{gwet2014handbook} to identify the relationships between each pair of attributes.
 
@@
 
-\subsection{Dataset Annotation}
-In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal", ``related", or ``unrelated" 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
-In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-".
-Following this, the annotators, marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells, with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0", exactly similar as ``1", row attribute as child of column attribute as ``<", row attribute as a parent of the column attribute as ``>", and finally, unknown as ``~".
-The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
-
-\begin{figure}[]
+\begin{figure}[htb!]
 	\centering
@@
 
-These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
-Using Cohen's Kappa score ($\kappa$) \cite{gwet2014handbook}, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
-It can be seen in this plot, that ``Annotator3" has very small correlation with the other 3 annotators.
-This difference can be traced back to the number and type of annotations performed by each annotator, which is shown in Table \ref{tab:annotator_marking}.
-The ``Annotator3" has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty.
-However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness.
+\subsection{Dataset Annotation}
+In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal", ``related", or ``unrelated" 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
+In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-".
+Following this, the annotators, marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells, with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0", exactly similar as ``1", row attribute as child of column attribute as ``<", row attribute as a parent of the column attribute as ``>", and finally, unknown as ``~".
+The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
 
@@
 
+These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
+Using $\kappa$, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
+It can be seen in this plot, that ``Annotator3" has very small correlation with the other 3 annotators.
+This difference can be traced back to the number and type of annotations performed by each annotator, which is shown in Table \ref{tab:annotator_marking}.
+The ``Annotator3" has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty.
+However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness.
+
 This annotated data was then processed, to replace all related entries with ``0.5" and all``-" with ``0", while the values for similar at ``1" and ``0" for dissimilar were kept the same.
@@
 The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and F-1 score.
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[scale=0.83]{thresholdSelection}
+	\caption{Thresholds selection.}
+	\label{fig:thresholdSelection}
+\end{figure*}
 
@@
 These models include, ``Fuzzy\_Wuzzy", ``Word2Vec", and 10 BERT based models.
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[scale=0.83]{thresholdSelection}
-	\caption{Thresholds selection.}
-	\label{fig:thresholdSelection}
-\end{figure*}
 
@@
 Finally, we evaluated the overall $\kappa$ coefficient and MCC score to evaluate the performance of each model on the test dataset.
-These measures range between [0,1], and provide a measure quantifying the accuracy of the classifier to correctly predict correct and incorrect instances.
+These scores range between [-1,1], providing a measure quantifying the accuracy of the classifier to correctly predict correct and incorrect instances.
 The models Word2Vec, bert-large-nli-mean-tokens, and roberta-base-nli-mean-tokens, with values between [0,0.20] indicate random classification, while $\kappa$ score between [0.21,0.39], achieved by fuzzy wuzzy, bert-base-nli-mean-tokens, roberta-base-nli-sts-mean-tokens, distilbert-base-nli-stsb-mean-tokens, bert-base-nli-mean-tokens, roberta-large-nli-mean-tokens, and distilbert-base-nli-mean-tokens, show only minimal agreement with the annotated data \cite{mchugh2012interrater}.

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
updated conclusion

@@
 \subsection{Model Evaluation}
-On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-classes.
+On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-classes. For class 1 (``similar")
 
@@
 \section{Conclusion}
-Conclusion goes here.
+Healthcare information systems are slowly moving towards a standardized approach, whereby the storage, exchange, and usage of health data, information, and knowledge is becoming interoperable.
+However, research and development of ubiquitous health management systems, still require manual interventions by human experts.
+Such approaches require costly resource allocations, which is not possible for small and medium scaled healthcare service providers.
+In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques.
+Using transformer based pre-trained BERT models, we show the applicability of these techniques on creating the, as yet non-validated, schema maps.
+Resultantly, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
+In future, we shall look towards developing a mechanism for schema map storage and evolution, along with expert validation to finally close this loop.
+We shall also work on re-training some of the existing pre-trained models, to improve the performance of schema map creation.
 

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
fixed class labels

@@
 
-This annotated data was then processed, to replace all related entries with ``0.5" and all``-" with ``0", while the values for similar at ``1" and ``0" for dissimilar were kept the same.
+This annotated data was then processed, to replace all related entries with ``0.5" ($class_{0.5}$) and all``-" with ``0" ($class_{0}$), while the values for similar at ``1" ($class_{1}$) and ``0" ($class_{0}$) for dissimilar were kept the same.
 This conversion was then used to produce a consolidated dataset of 40,698 attribute pairs, using mode scores of all annotators, for each cell.
@@
 The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal", followed by best scores for class ``related" and finally best of class "unrelated".
-The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and F-1 score.
+The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and $F_1$ measure.
 
@@
 In case of independent labels, area under the precision recall curve can provide this optimal measure, however as in our case, for dependent classes on a biased dataset the Matthews Correlation Coefficient (MCC), is better\cite{chicco2020advantages}.
-Since our aim is to apply an optimal text similarity classifier to resolve this multi-class problem (class 0, class 0.5, and class 1), we have to test various threshold scores for separating the instances between 0 and 0.5 ($t_1$), and then 0.5 and 1($t_2$).
-Additionally, since our aim is to correctly identify the similar attribute instances, it is pertinent to maximize the classification performance of class 1 (similar), followed by class 0.5 (related), and finally class 0 (unrelated).
-With a step size of 0.05 ($step_size$), and starting from $t_1$ as 0.0 and $t_2$ as $t_1$ + $step_size$, we move the thresholds until $t_2$ reaches 1, followed by increase in $t_1$ by step size.
-Eventually, $t_1$, reaches 0.95 and $t_2$ reaches 1, at which point, the process stops.
+Since our aim is to apply an optimal text similarity classifier to resolve this multi-class problem ($class_0$, $class_{0.5}$, and $class_1$), we have to test various threshold scores for separating the instances between $class_0$ and $class_{0.5}$ ($t_1$), and then $class_{0.5}$ and $class_1$ ($t_2$).
+Additionally, since our aim is to correctly identify the similar attribute instances, it is pertinent to maximize the classification performance of $class_1$ (similar), followed by $class_{0.5}$ (related), and finally $class_0$ (unrelated).
+With a step size of \textit{0.05} ($step$), and starting from $t_1$ as 0.0 and $t_2$ as $t_1$ + $step$, we move the thresholds until $t_2$ reaches \textit{1.0}, followed by increase in $t_1$ by step size.
+Eventually, $t_1$, reaches \textit{0.95} and $t_2$ reaches \textit{1.0}, at which point, the process stops.
 This is to ensure that $t_1$ remains behind $t_2$, for all iterations, measuring MCC score, for the 12 models.
@@
 
-Threshold values for Word2Vec are placed at the lower end of the spectrum, indicating a very large number of instances are classified as similar (above similarity score of 0.1), while a small number of instances (with similarity score 0.05) are classified as dissimilar.
-Similarly, the class related lies within the similarity threshold of 0.05 similarity points.
-It can be observed that the threshold for selecting the related class, is within 0.05 points, in all except one case (bert-large-nli-mean-tokens where the difference is 0.15 points).
-Five BERT based models, trained on the STSb dataset, all have minimum threshold values of 0.85 and maximum of 0.9, while the 4 remaining BERT models, lie between 0.9 and 0.95.
+Threshold values for Word2Vec are placed at the lower end of the spectrum, indicating a very large number of instances are classified as similar (above similarity score of \textit{0.1}), while a small number of instances (with similarity score \textit{0.05}) are classified as dissimilar.
+Similarly, the $class_{0.5}$ lies within the similarity threshold of \textit{0.05} similarity points.
+It can be observed that the threshold for selecting the related class, is within \textit{0.05} points, in all except one case (bert-large-nli-mean-tokens where the difference is \textit{0.15} points).
+Five BERT based models, trained on the STSb dataset, all have minimum threshold values of \textit{0.85} and maximum of \textit{0.9}, while the 4 remaining BERT models, lie between \textit{0.9} and \textit{0.95}.
 These results show a general trend, of how the cosine similarity varies/maintains itself, against embedded vectors generated from various pre-trained models.
@@
 \subsection{Model Evaluation}
-On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-classes. For class 1 (``similar")
+On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-classes.
+As evident in Table \ref{tab:evaluations}, very high values of accuracy are visible across all models, with all three positive classes.
+In all, except the case of Word2Vec, Precision and recall, also show values close to \textit{1.0}.
+However, these measures are very misleading, since the dataset is greatly biased in favour of $class_0$.
+In terms of $F_1$ measure $class_{0.5}$ shows the worst possible results, independently, with all except Word2Vec and bert-large-nli-mean-tokens, having a score of \textit{0.0}.
+Bert-large-nli-mean-tokens, provides the best $F_1$ measure at \textit{0.49}.
+These metrics are thus not useful to gauge the performance of the evaluated models.
+Instead, focusing on the MCC score, provides a good picture of the model performance, for individual classes, when all other instances are negative.
 
@@
 		\textbf{Model}                                        & \textbf{Class Positive} & \textbf{Class Negative} & \multicolumn{1}{c|}{\textbf{accuracy}} & \multicolumn{1}{c|}{\textbf{precision}} & \multicolumn{1}{c|}{\textbf{recall}} & \multicolumn{1}{c|}{\textbf{f-1}} & \multicolumn{1}{c|}{\textbf{mcc}} \\ \hline
-		\multirow{3}{*}{FUZZY\_MATCH}                         & 0.0                     & 0.5,1                   & 0.98                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.98                                   & 0.20                                    & 0.59                                 & 0.29                              & 0.33                              \\ \hline
-		\multirow{3}{*}{Word2Vec}                             & 0.0                     & 0.5,1                   & 0.24                                   & 0.99                                    & 0.24                                 & 0.38                              & 0.01                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.15                                    & 0.10                                 & 0.12                              & 0.12                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.35                                   & 0.01                                    & \textbf{0.84}                        & 0.01                              & 0.03                              \\ \hline
-		\multirow{3}{*}{bert-base-nli-stsb-mean-tokens}       & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.99                                   & 0.22                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
-		\multirow{3}{*}{bert-large-nli-stsb-mean-tokens}      & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.51                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.99                                   & 0.41                                    & 0.50                                 & 0.45                              & 0.45                              \\ \hline
-		\multirow{3}{*}{roberta-base-nli-stsb-mean-tokens}    & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 1.00                              & 0.40                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.99                                   & 0.26                                    & 0.50                                 & 0.34                              & 0.36                              \\ \hline
-		\multirow{3}{*}{roberta-large-nli-stsb-mean-tokens}   & 0.0                     & 0.5,1                   & 1.00                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.61                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & \textbf{1.00}                          & \textbf{0.59}                           & 0.50                                 & \textbf{0.54}                     & \textbf{0.54}                     \\ \hline
-		\multirow{3}{*}{distilbert-base-nli-stsb-mean-tokens} & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.38                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.99                                   & 0.23                                    & 0.50                                 & 0.32                              & 0.33                              \\ \hline
-		\multirow{3}{*}{bert-base-nli-mean-tokens}            & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.35                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.99                                   & 0.20                                    & 0.50                                 & 0.29                              & 0.31                              \\ \hline
-		\multirow{3}{*}{bert-large-nli-mean-tokens}           & 0.0                     & 0.5,1                   & 0.28                                   & 1.00                                    & 0.27                                 & 0.43                              & 0.05                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 0.99                                   & 0.34                                    & 0.90                                 & 0.49                              & 0.55                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.57                                   & 0.00                                    & 0.50                                 & 0.01                              & 0.01                              \\ \hline
-		\multirow{3}{*}{roberta-base-nli-mean-tokens}         & 0.0                     & 0.5,1                   & 0.96                                   & 1.00                                    & 0.97                                 & 0.98                              & 0.23                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.96                                   & 0.08                                    & 0.50                                 & 0.13                              & 0.19                              \\ \hline
-		\multirow{3}{*}{roberta-large-nli-mean-tokens}        & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.39                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.99                                   & 0.20                                    & 0.50                                 & 0.28                              & 0.31                              \\ \hline
-		\multirow{3}{*}{distilbert-base-nli-mean-tokens}      & 0.0                     & 0.5,1                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.36                              \\ \cline{2-8}
-		& 0.5                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& 1                       & 0.0,0.5                 & 0.99                                   & 0.21                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
+		\multirow{3}{*}{FUZZY\_MATCH}                         & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.98                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.98                                   & 0.20                                    & 0.59                                 & 0.29                              & 0.33                              \\ \hline
+		\multirow{3}{*}{Word2Vec}                             & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.24                                   & 0.99                                    & 0.24                                 & 0.38                              & 0.01                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.15                                    & 0.10                                 & 0.12                              & 0.12                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.35                                   & 0.01                                    & \textbf{0.84}                        & 0.01                              & 0.03                              \\ \hline
+		\multirow{3}{*}{bert-base-nli-stsb-mean-tokens}       & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.22                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
+		\multirow{3}{*}{bert-large-nli-stsb-mean-tokens}      & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.51                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.41                                    & 0.50                                 & 0.45                              & 0.45                              \\ \hline
+		\multirow{3}{*}{roberta-base-nli-stsb-mean-tokens}    & $class_0$                    & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 1.00                              & 0.40                              \\ \cline{2-8}
+		& $class_{0.5}$                     & 0.0,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                & 0.99                                   & 0.26                                    & 0.50                                 & 0.34                              & 0.36                              \\ \hline
+		\multirow{3}{*}{roberta-large-nli-stsb-mean-tokens}   & $class_0$                     & $class_{0.5}$,$class_1$                   & 1.00                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.61                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & 0.0,$class_{0.5}$                & \textbf{1.00}                          & \textbf{0.59}                           & 0.50                                 & \textbf{0.54}                     & \textbf{0.54}                     \\ \hline
+		\multirow{3}{*}{distilbert-base-nli-stsb-mean-tokens} & 0.0                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.38                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.23                                    & 0.50                                 & 0.32                              & 0.33                              \\ \hline
+		\multirow{3}{*}{bert-base-nli-mean-tokens}            & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.35                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.20                                    & 0.50                                 & 0.29                              & 0.31                              \\ \hline
+		\multirow{3}{*}{bert-large-nli-mean-tokens}           & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.28                                   & 1.00                                    & 0.27                                 & 0.43                              & 0.05                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 0.99                                   & 0.34                                    & 0.90                                 & 0.49                              & 0.55                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.57                                   & 0.00                                    & 0.50                                 & 0.01                              & 0.01                              \\ \hline
+		\multirow{3}{*}{roberta-base-nli-mean-tokens}         & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.96                                   & 1.00                                    & 0.97                                 & 0.98                              & 0.23                              \\ \cline{2-8}
+		& $class_{0.5}$                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.96                                   & 0.08                                    & 0.50                                 & 0.13                              & 0.19                              \\ \hline
+		\multirow{3}{*}{roberta-large-nli-mean-tokens}        & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.39                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                & 0.99                                   & 0.20                                    & 0.50                                 & 0.28                              & 0.31                              \\ \hline
+		\multirow{3}{*}{distilbert-base-nli-mean-tokens}      & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.36                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$           & 0.99                                   & 0.21                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
 	\end{tabular}

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
update discussion 1

@@
 \usepackage{multirow}
+\usepackage{ulem}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 Additionally, the annotated data, collected against five medical schemas and labeled by 4 annotators is made available for helping future researchers.
-Our results indicate, that for biased, dependent multi-class text classification, RoBERTa shows the best performance, achieving a cohen's kappa score of 0.47 and MCC score of 0.48, with human annotated data.
+Our results indicate, that for biased, dependent multi-class text classification, RoBERTa shows the best performance, achieving a cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
 \end{abstract}
@@
 \begin{keywords}
-Electronic medical records, Health information management, Medical information systems,  Text processing, Unsupervised learning
+\sout{Electronic medical records, Health information management, Medical information systems,  Text processing, Unsupervised learning}
 \end{keywords}
@@
 
-Data interoperability resolves the heterogeneity between data artificats, to enable, seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International (HL7), and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
+Data interoperability resolves the heterogeneity between data artificats to enable seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International (HL7), and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
 On the other hand, process interoperability regulates the communication among organizational processes to provide compatability between process artifacts within and seamless transformations across different organizations\cite{khan2013process}.
@@
 In this way, successive healthcare treatments can take benefit from earlier diagnosis, treatment, and followup procedures, thereby reducing the stress on healthcare experts and systems.
-Standards such as HL7 - Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
+Healthcare Standards such as HL7 - Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
 While Systematized Nomenclature of Medicine—Clinical Terms (Snomed-CT) \cite{snomedct_url} and Logical Observation Identifiers Names and Codes (LOINC) \cite{loinc} provide a standard definition for clinical terminologies and laboratory tests, respectively.
@@
 Additionally, while these codes can be used to represent data instances, the data schema, achieves no benefit from the same.
-Consider the terms ``name" and ``patientName", which refer to the same attribute of the patient entity.
+Consider the terms ``name'' and ``patientName'', which refer to the same attribute of the patient entity.
 However, since there is no standard way to represent this attribute, both are considered correct ($s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter).\\
-In the later case, differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address", ``City", ``State", ``Postal Code", ``Country", and others.
-Similarly, ``EncounterDate" from $s_5$ is semantically similar to ``BeginDate" of ``openemr\_MedicalProblems" table in $s_1$, ``AdmissionStartDate" of ``LabsCorePopulatedTable" in $s_2$,
-``time" in ``Diagnosis" table of $s_3$, and  ``dateOfAdmission" in ``Diagnosis" and ``CareHistory" tables of $s_4$.
+In the later case, differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address'', ``City'', ``State'', ``Postal Code'', ``Country'', and others.
+Similarly, ``EncounterDate'' from $s_5$ is semantically similar to ``BeginDate'' of ``openemr\_MedicalProblems'' table in $s_1$, ``AdmissionStartDate'' of ``LabsCorePopulatedTable'' in $s_2$,
+``time'' in ``Diagnosis'' table of $s_3$, and  ``dateOfAdmission'' in ``Diagnosis'' and ``CareHistory'' tables of $s_4$.
 Finally, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, $s_5$.
@@
 We then iterate over these fragments, building a set of attributes, distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.
-This entails that ``PatientID" from each of the four tables in $s_2$, and ``patientID" from five tables in $s_4$, would result into nine attributes (assuming, as in the current case, of no differences in versions of these systems).
+This entails that ``PatientID'' from each of the four tables in $s_2$, and ``patientID'' from five tables in $s_4$, would result into nine attributes (assuming, as in the current case, of no differences in versions of these systems).
 For each attribute, we then generate the suffix array, which provides all possible substring representations contained within the attribute name.
 In order to generate the set of suffixes, we employ three strategies, forward suffix generation, whereby for a word $w$ of length $n$, $n-1$ suffixes of size 2 to $n-1$ are produced, backward suffix generation, to produce $n-1$ suffixes in reverse order with size $n-1$ to 2, and regular expression based suffix generation, which splits each word on, change of case, special characters(such as -, \_, !, and others), and numbers.
-In this way a large list of suffixes is generated, which is combined using a ``TreeSet" data structure of Java, which internally sorts this list as well.
-An example of this suffix generation process, using the attribute name ``dateOfAdmission" as it appears in $s_4$ is shown in \ref{fig:suffix_attribute}.
+In this way a large list of suffixes is generated, which is combined using a ``TreeSet'' data structure of Java, which internally sorts this list as well.
+An example of this suffix generation process, using the attribute name ``dateOfAdmission'' as it appears in $s_4$ is shown in \ref{fig:suffix_attribute}.
 
-Suffix strings for similar attributes such as ``AdmissionStartDate".
-``diseaseNameOnAdmission", and ``AdmissionEndDate" appear in $s_2$, produce many, synctactically similar suffixes, to the presented example.
+Suffix strings for similar attributes such as ``AdmissionStartDate''.
+``diseaseNameOnAdmission'', and ``AdmissionEndDate'' appear in $s_2$, produce many, synctactically similar suffixes, to the presented example.
 This process, is only able to generate syntactic suffixes, producing many incoherent and unrelated suffixes.
@@
 The set of suffixes and their corresponding concepts are then used to build the sentence, where by each concept, corresponding to a suffix is appended next to the suffix.
-An example of the resultant sentence for the attribute ``DateOfAdmission" is shown as follows:\\
+An example of the resultant sentence for the attribute ``DateOfAdmission'' is shown in Table \ref{tab:sentence_example}.
 
-\framebox{\parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{\itshape%
+\begin{table}[]
+	\centering
+	\caption{Sentence created from the attribute name ``DateOfAdmission''}
+	\label{tab:sentence_example}
+	\begin{tabular}{p{\linewidth}}
+		Date Value type - Date date allergenic extract Date in time Data types - Date Date Fruit;Of SPI1 wt Allele SPI1 gene TAF1 wt Allele BRIP1 gene Within Degrees fahrenheit Oral contraception BRIP1 wt Allele;Da Displacement of abomasum dalton Anterior descending branch of left coronary artery deca units cytarabine/daunorubicin protocol Dai Chinese Asymptomatic diagnosis of Drug Accountability Domain;ion Iontophoresis Route of Drug Administration Ions;on SPARC wt Allele Osteonectin SPARC gene On (qualifier value) Upon - dosing instruction fragment;Admission Admission activity Hospital admission;Dat SLC6A3 gene SLC6A3 wt Allele dopamine transporter Direct Coombs test SLC6A3 protein, human Test Date cytarabine/daunorubicin/thioguanine Alzheimer's Disease;mission Religious Missions;
+	\end{tabular}
+\end{table}
 
-		``Date Value type - Date date allergenic extract Date in time Data types - Date Date Fruit;Of SPI1 wt Allele SPI1 gene TAF1 wt Allele BRIP1 gene Within Degrees fahrenheit Oral contraception BRIP1 wt Allele;Da Displacement of abomasum dalton Anterior descending branch of left coronary artery deca units cytarabine/daunorubicin protocol Dai Chinese Asymptomatic diagnosis of Drug Accountability Domain;ion Iontophoresis Route of Drug Administration Ions;on SPARC wt Allele Osteonectin SPARC gene On (qualifier value) Upon - dosing instruction fragment;Admission Admission activity Hospital admission;Dat SLC6A3 gene SLC6A3 wt Allele dopamine transporter Direct Coombs test SLC6A3 protein, human Test Date cytarabine/daunorubicin/thioguanine Alzheimer's Disease;mission Religious Missions;"
-}}\\
-
-Here the various suffixes and their concepts are seperated by the symbol ``;", however together they form one sentence, for which an embedded vector is generated.
+Here the various suffixes and their concepts are separated by the symbol ``;'', however together they form one sentence, for which an embedded vector is generated.
 
@@
 -1 indicates, inverse relationship between the attributes, while 1 indicates the two attributes are very much the same.
-For producing our schema maps, we are interested in three types of relationships, ``equal" (the two attributes are same), ``related" (the two attributes are related to each other), and ``unrelated" (no relationship between the attributes).
-In order to classify the similarity results, into one of these three classes, we then calculated the best thresholds, using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal", ``related", and ``unrelated".
+For producing our schema maps, we are interested in three types of relationships, ``equal'' (the two attributes are same), ``related'' (the two attributes are related to each other), and ``unrelated'' (no relationship between the attributes).
+In order to classify the similarity results, into one of these three classes, we then calculated the best thresholds, using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal'', ``related'', and ``unrelated''.
 
 \begin{equation}
+\resizebox{0.9\hsize}{!}{$%
 	MCC = \frac{(TP.FN) - (FP.FN)}{\sqrt{(TP+FP)(TP+FN)(TN+FP)(TN+FN)}}\longrightarrow [-1,1]
+	$%
+}%
 \end{equation}
@@
 This measurement is markedly different from accuracy, that fails to account for imbalanced datasets and $F_1$ measure which is not affected by the true negative scores.
-As a result, MCC provides an acceptable alternate, in our current scenario comprising of imbalanced dataset (largely in favour of class ``unrelated") to measuring the true performance of the models, used for threshold selection and model evaluation.
+As a result, MCC provides an acceptable alternate, in our current scenario comprising of imbalanced dataset (largely in favour of class ``unrelated'') to measuring the true performance of the models, used for threshold selection and model evaluation.
 Finally on a test dataset we evaluated our multi-class classification approach, using MCC and Cohen's Kappa coefficient ($\kappa$) \cite{gwet2014handbook} to identify the relationships between each pair of attributes.
@@
 Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
-The code to generate this data set is available at ``uhp\_map\_generation"\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhpr\_storage}.
+The code to generate this data set is available at ``uhp\_map\_generation''\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhpr\_storage}.
 This application produces three custom formatted files, containing an index for patients, an index for their medical fragments, and the medical fragment, corresponding to the EMR data.
 Using the medical fragments file, we then generate the semantically enriched attribute \footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhp\_map\_generation}, which contains the suffixes and their concepts corresponding to each EMR data attribute.
-The resulting set of enriched attributes are temporarily stored in a ``json" file, which is then read by the same application to partially generate the schema maps.
+The resulting set of enriched attributes are temporarily stored in a JSON file, which is then read by the same application to partially generate the schema maps.
 This process, is used to create 20,349 distinct pairs of attributes, across $s$.
-Each pair also contains the ``relationshipList", which stores the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
-The ``json" file thus produced, is then used by a python script to generate the semantically enriched sentences and their embedded vectors using Word2Vec, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
-The BERT models include 'bert-base-nli-stsb-mean-tokens', 'bert-large-nli-stsb-mean-tokens', 'roberta-base-nli-stsb-mean-tokens', 'roberta-large-nli-stsb-mean-tokens', 'distilbert-base-nli-stsb-mean-tokens', 'bert-base-nli-mean-tokens', 'bert-large-nli-mean-tokens', 'roberta-base-nli-mean-tokens', 'roberta-large-nli-mean-tokens', and 'distilbert-base-nli-mean-tokens'.
+Each pair also contains the ``relationshipList'', which stores the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
+The JSON file thus produced, is then used by a python script to generate the semantically enriched sentences and their embedded vectors using Word2Vec, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
+The BERT models include ``bert-base-nli-stsb-mean-tokens'', ``bert-large-nli-stsb-mean-tokens'', ``roberta-base-nli-stsb-mean-tokens'', ``roberta-large-nli-stsb-mean-tokens'', ``distilbert-base-nli-stsb-mean-tokens'', ``bert-base-nli-mean-tokens'', ``bert-large-nli-mean-tokens'', ``roberta-base-nli-mean-tokens'', ``roberta-large-nli-mean-tokens'', and ``distilbert-base-nli-mean-tokens''.
 The embedding vectors are then compared using cosine similarity, which produces a score between -1 and 1.
@@
 Additionally, since python provides better support for easy generation of embedding vectors, it was thus preferred over the Java based implementation, which is otherwise very beneficial for other tools.
-These applications were executed on a workstation running Ubuntu 20.04.2 on top of AMD Ryzen 3 2200G, and 32GB ram.
+%These applications were executed on a workstation running Ubuntu 20.04.2 on top of AMD Ryzen 3 2200G, and 32GB ram.%
 
@@
 \subsection{Dataset Annotation}
-In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal", ``related", or ``unrelated" 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
-In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-".
-Following this, the annotators, marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells, with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0", exactly similar as ``1", row attribute as child of column attribute as ``<", row attribute as a parent of the column attribute as ``>", and finally, unknown as ``~".
+In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal'', ``related'', or ``unrelated'' 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
+In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-''.
+Following this, the annotators, marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells, with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0'', exactly similar as ``1'', row attribute as child of column attribute as ``<'', row attribute as a parent of the column attribute as ``>'', and finally, unknown as ``~''.
 The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
@@
 
-These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0".
+These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0''.
 Using $\kappa$, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
-It can be seen in this plot, that ``Annotator3" has very small correlation with the other 3 annotators.
+It can be seen in this plot, that ``Annotator3'' has very small correlation with the other 3 annotators.
 This difference can be traced back to the number and type of annotations performed by each annotator, which is shown in Table \ref{tab:annotator_marking}.
-The ``Annotator3" has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty.
+The ``Annotator3'' has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty.
 However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness.
 
-This annotated data was then processed, to replace all related entries with ``0.5" ($class_{0.5}$) and all``-" with ``0" ($class_{0}$), while the values for similar at ``1" ($class_{1}$) and ``0" ($class_{0}$) for dissimilar were kept the same.
+This annotated data was then processed, to replace all related entries with ``0.5'' ($class_{0.5}$) and all``-'' with ``0'' ($class_{0}$), while the values for similar at ``1'' ($class_{1}$) and ``0'' ($class_{0}$) for dissimilar were kept the same.
 This conversion was then used to produce a consolidated dataset of 40,698 attribute pairs, using mode scores of all annotators, for each cell.
-We also tested average scores between the annotators, but that would produce scores between ``0", ``0.5", and ``1", greatly increasing the number of classes for classification.
+We also tested average scores between the annotators, but that would produce scores between ``0'', ``0.5'', and ``1'', greatly increasing the number of classes for classification.
 Hence the maximum agreement between the annotators, maintains the final label values within these three classes, which become easier to evaluate.
-Additionally, the original dataset and its mode consolidated form is biased in favour of class "0", since most attribute pairs are not related to each other.
+Additionally, the original dataset and its mode consolidated form is biased in favour of class ''0'', since most attribute pairs are not related to each other.
 This dataset is then split into development and testing partitions with a ratio of 70:30.
-The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal", followed by best scores for class ``related" and finally best of class "unrelated".
+The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal'', followed by best scores for class ``related'' and finally best of class ''unrelated''.
 The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and $F_1$ measure.
@@
 This is to ensure that $t_1$ remains behind $t_2$, for all iterations, measuring MCC score, for the 12 models.
-These models include, ``Fuzzy\_Wuzzy", ``Word2Vec", and 10 BERT based models.
+These models include, ``Fuzzy\_Wuzzy'', ``Word2Vec'', and 10 BERT based models.
 
@@
 		\multirow{3}{*}{roberta-base-nli-stsb-mean-tokens}    & $class_0$                    & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 1.00                              & 0.40                              \\ \cline{2-8}
-		& $class_{0.5}$                     & 0.0,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
 		& $class_1$                       & $class_0$,$class_{0.5}$                & 0.99                                   & 0.26                                    & 0.50                                 & 0.34                              & 0.36                              \\ \hline
@@
 		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & 0.0,$class_{0.5}$                & \textbf{1.00}                          & \textbf{0.59}                           & 0.50                                 & \textbf{0.54}                     & \textbf{0.54}                     \\ \hline
-		\multirow{3}{*}{distilbert-base-nli-stsb-mean-tokens} & 0.0                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.38                              \\ \cline{2-8}
+		& $class_1$                       & $class_0$,$class_{0.5}$                & \textbf{1.00}                          & \textbf{0.59}                           & 0.50                                 & \textbf{0.54}                     & \textbf{0.54}                     \\ \hline
+		\multirow{3}{*}{distilbert-base-nli-stsb-mean-tokens} & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.38                              \\ \cline{2-8}
 		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
@@
 		\multirow{3}{*}{roberta-base-nli-mean-tokens}         & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.96                                   & 1.00                                    & 0.97                                 & 0.98                              & 0.23                              \\ \cline{2-8}
-		& $class_{0.5}$                     & 0.0,1                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
+		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
 		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.96                                   & 0.08                                    & 0.50                                 & 0.13                              & 0.19                              \\ \hline
@@
 \section{Discussion}
+In text classification, production and use of a well annotated corpus for supervised and semi-supervised learning is of utmost importance.
+The same is also useful for evaluating the performance of unsupervised learning techniques.
+However, in the real world the production and maintenance of these corpora is an expensive task, often requiring extensive human effort.
+While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively provide a label to an instance.
+This is also evident in the case of our annotated dataset, whereby the instances have been labeled by four human experts (two medical practioners and two computer science graduates), using their subjective knowledge.
+One example of this subjective classification, is evident in the raw form of the data instances labeled by ``Annotator3''.
+According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child.
+While the selection of this label can be debated from an subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect.
+As a result, the annotations were kept anonymous with random to as not to induce any biasedness.
+Hence, the annotated data in its original form becomes the basis of our threshold selection and model evaluation methodology.
+A side-effect of this choice is the lower scores of agreement between the (annotated data) true labels and predicted labels.
 
@@
 However, research and development of ubiquitous health management systems, still require manual interventions by human experts.
-Such approaches require costly resource allocations, which is not possible for small and medium scaled healthcare service providers.
+These approaches require costly resource allocations, which is not possible for small and medium scaled healthcare service providers.
 In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques.

### 2021-06-04 ManuScript/IEEEAccess/ManuScript.tex
final updates

@@
 \begin{keywords}
-\sout{Electronic medical records, Health information management, Medical information systems,  Text processing, Unsupervised learning}
+Context aware systems, Decision support systems, Electronic medical records,Experts systems,   Health information management, Medical information systems, Ontology engineering, Text processing, Unsupervised learning
 \end{keywords}
@@
 Various abbreviations, used in this manuscript are listed in Table \ref{tab:abbreviations}.
+
+Data interoperability resolves the heterogeneity between data artificats to enable seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International (HL7), and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
+On the other hand, process interoperability regulates the communication among organizational processes to provide compatability between process artifacts within and seamless transformations across different organizations\cite{khan2013process}.
+Lastly, knowledge interoperability provides a sharing mechanism for reusing interpretable medical knowledge, acquired through expert intervention and other mechanisms, across decision support systems \cite{ali2017multi}.
 
@@
 
-Data interoperability resolves the heterogeneity between data artificats to enable seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International (HL7), and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
-On the other hand, process interoperability regulates the communication among organizational processes to provide compatability between process artifacts within and seamless transformations across different organizations\cite{khan2013process}.
-Lastly, knowledge interoperability provides a sharing mechanism for reusing interpretable medical knowledge, acquired through expert intervention and other mechanisms, across decision support systems \cite{ali2017multi}.
 In more tangible terms, healthcare interoperability at data, process, and knowledge level can be exemplified within the healthcare constraints experienced due to the emergence of Covid 19.
@@
 Similarly Medical Logic Module (MLM) provides a standardized way for expressing medical knowledge.
-However, the plethora of standards, necessitates the creation of bridging standards, that can resolve the heterogeniety between the medical standards.
+However, the plethora of standards necessitates the creation of bridging standards that can resolve the heterogeniety between the medical standards.
 Substantial effort has gone into this endeavor with the Clinical Information Modeling Initiative (CIMI) \cite{CIMI2015} taking the lead in bridging the gap between HL7v3 and openEHR.
@@
 This healthcare interoperability solution follows a formal, albiet long process, which is greatly dependent on the human factor.
-However, the current healthcare scenario, requires a quick solution to create a scaffolding of an interoperable bridge between various healthcare providers.
+However, the current healthcare scenario requires a quick solution to create a scaffolding of an interoperable bridge between various healthcare providers.
 It is also important to ensure that this scaffolding should be able to support the formal standardization processes of the future.
-In \cite{Satti2020}we have presented the Ubiquitous Health Platform (UHP), which provides semantic reconciliation-on-read based data curation for resolving data interoperability between various schema.
+In \cite{Satti2020}, we have presented the Ubiquitous Health Platform (UHP), which provides semantic reconciliation-on-read based data curation for resolving data interoperability between various schema.
 This methodology is based on the creation and management of schema maps, that can provide the framework for transforming a source schema into a target schema.
-In the current manuscript, we will present our research work to build and manage the schema map knowledge base.
+In the current study, we will present our research work to build and manage the schema map knowledge base.
 Overall, our methodology is based on the creation, evaluation, and application of a novel schema matching technique to identify the relationships between attributes of the participating medical data schema.
@@
 	\centering
+	\includegraphics[scale=0.60]{methodology}
+	\caption{Methodology for creating schema maps.}
+	\label{fig:methodology}
+\end{figure*}
+
+\section{Methodology}
+\label{methodology}
+Healthcare interoperability, with a focus on non-standard compliant medical schema is dependent on the generation and validation of schema maps as discussed above.
+To this end, the creation of a cohesive workflow is of utmost importance.
+In our earlier work \cite{Satti2020} we used maximum sequence identification and suffix tress based matching for syntactic matching of two distinct data schemas.
+This was followed by semantic concept enrichment and subsequently concept matching for creating rules in the form of schema maps.
+The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data into an interpretable model form.
+In our current methodology as visualized in Figure \ref{methodology}, we have utilized state-of-the-art natural language processing (NLP) techniques to extract the schema mapping rules from semi-structured data schemas.
+This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas.
+Traditional NLP techniques such as Word2Vec are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence \cite{zhu2018exploring}.
+However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
+In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names.
+The bidirectional nature of BERT, allows the creation of contextual embedded vectors, where each target word is affected by its neighboring words.
+Hence to convert the set of suffixes into a sentence, we collected the set of concepts corresponding to each suffix, from UMLS.
+This operation has two effects, firstly it is used to remove any suffix, which does not have a corresponding concept and secondly the extracted concepts are used to add context to each suffix and produce a contextual sentence.
+The following subsections provide the practical details for our methodology from schema acquisition to attribute name expansion, and finally schema map generation.
+
+\subsection{Schema acquisition}
+\label{schema_acq}
+In the first step of our semantic reconciliation methodology, we simulate medical data acquisition from five distinct Electronic Medical Records (EMR) storage systems ($S$).
+These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
+al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$) \ref{ali2017reconciliation}.
+Each of these medical systems as shown in \ref{fig:schema}, follows the relational database design with logical entities such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
+While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.
+
+\begin{figure*}[t!]
+	\centering
 	\includegraphics[scale=0.53]{schemas}
@@
 
-\section{Methodology}
-\label{methodology}
-Healthcare interoperability, with a focus on non-standard compliant medical schema, is dependent on the generation and validation of schema maps, as discussed above.
-To this end, the creation of a cohesive workflow is of utmost importance.
-In our earlier work \cite{Satti2020} we used maximum sequence identification and suffix tress based matching for syntactic matching of two distinct data schemas.
-This was followed by semantic concept enrichment and subsequently concept matching, for creating rules in the form of schema maps.
-The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data, into an interpretable, model form.
-In our current methodology we have utilized state-of-the-art natural language processing (NLP) techniques to extract the schema mapping rules from semi-structured data schemas.
-This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas.
-Traditional NLP techniques such as WordNet are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence \cite{zhu2018exploring}.
-However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
-In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names.
-The bidirectional nature of BERT, allows the creation of contextual embedded vectors, where each target word is affected by its neighboring words.
-Hence to convert the set of suffixes into a sentence, we collected the set of concepts corresponding to each suffix, from UMLS.
-This operation has two effects, firstly it is used to remove any suffix, which does not have a corresponding concept and secondly the extracted concepts are used to add context to each suffix and produce a contextual sentence.
-The following subsections provide the practical details for our methodology, from schema acquisition, to attribute name expansion, and finally schema map generation.
-
-\subsection{Schema acquisition}
-\label{schema_acq}
-In the first step of our semantic reconciliation methodology, we simulate medical data acquisition from five distinct Electronic Medical Records (EMR) storage systems ($S$).
-These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
-al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$).
-Each of these medical systems as shown in \ref{fig:schema}, follows the relational database design, with logical entities, such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
-While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.
-
-A similar notion of data heterogeneity, in terms of medical data schema, is evident across the healthcare domain.
+A similar notion of data heterogeneity, in terms of medical data schema is evident across the healthcare domain.
 This is caused by various factors, including the lack of one all-encompassing, and universally applicable terminological standard and different normalization level for representing attributes.\\
@@
 However, since there is no standard way to represent this attribute, both are considered correct ($s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter).\\
-In the later case, differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others, such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address'', ``City'', ``State'', ``Postal Code'', ``Country'', and others.
+In the later case, differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address'', ``City'', ``State'', ``Postal Code'', ``Country'', and others.
 Similarly, ``EncounterDate'' from $s_5$ is semantically similar to ``BeginDate'' of ``openemr\_MedicalProblems'' table in $s_1$, ``AdmissionStartDate'' of ``LabsCorePopulatedTable'' in $s_2$,
 ``time'' in ``Diagnosis'' table of $s_3$, and  ``dateOfAdmission'' in ``Diagnosis'' and ``CareHistory'' tables of $s_4$.
-Finally, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, $s_5$.
+Finally, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, and $s_5$.
 Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for the EMR/EHR storage systems.
@@
 
-\begin{figure*}[tb!]
-	\centering
-	\includegraphics[scale=0.53]{suffixAttribute}
-	\caption{Suffix attributes.}
-	\label{fig:suffix_attribute}
-\end{figure*}
-
-\subsection{From Attribute to Sentence}
+\subsection{Attribute to Sentence Transformation}
 \label{schema_prepro}
@@
 We then iterate over these fragments, building a set of attributes, distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.
-This entails that ``PatientID'' from each of the four tables in $s_2$, and ``patientID'' from five tables in $s_4$, would result into nine attributes (assuming, as in the current case, of no differences in versions of these systems).
+This entails that ``PatientID'' from each of the four tables in $s_2$, and ``patientID'' from five tables in $s_4$, would result into nine attributes (assuming, as in the current case of no differences in versions of these systems).
 For each attribute, we then generate the suffix array, which provides all possible substring representations contained within the attribute name.
@@
 In this way a large list of suffixes is generated, which is combined using a ``TreeSet'' data structure of Java, which internally sorts this list as well.
-An example of this suffix generation process, using the attribute name ``dateOfAdmission'' as it appears in $s_4$ is shown in \ref{fig:suffix_attribute}.
+An example of this suffix generation process, using the attribute name ``dateOfAdmission'' as it appears in $s_4$ is shown in Figure \ref{fig:suffix_attribute}.
+
+\begin{figure}[tb!]
+	\centering
+	\includegraphics[scale=0.65]{suffixAttribute}
+	\caption{An example of suffix arrays produced for the attribute ``dateOfAdmission''.}
+	\label{fig:suffix_attribute}
+\end{figure}
 
@@
 This process, is only able to generate syntactic suffixes, producing many incoherent and unrelated suffixes.
-In order to counter this problem, and to limit the list of suffixes within the domain, we then query UMLS, with exact search strategy, looking for the existence of any concepts, against each suffix.
+In order to counter this problem, and to limit the list of suffixes within the domain, we then query UMLS with exact search strategy, looking for the existence of any concepts against each suffix.
 In case, no semantic concept is found for a particular suffix, it is removed from the final Suffix Array.
@@
 Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
-The set of suffixes and their corresponding concepts are then used to build the sentence, where by each concept, corresponding to a suffix is appended next to the suffix.
+The set of suffixes and their corresponding concepts are then used to build the sentence, where by each concept corresponding to a suffix is appended next to the suffix.
 An example of the resultant sentence for the attribute ``DateOfAdmission'' is shown in Table \ref{tab:sentence_example}.
@@
 	\label{tab:sentence_example}
-	\begin{tabular}{p{\linewidth}}
-		Date Value type - Date date allergenic extract Date in time Data types - Date Date Fruit;Of SPI1 wt Allele SPI1 gene TAF1 wt Allele BRIP1 gene Within Degrees fahrenheit Oral contraception BRIP1 wt Allele;Da Displacement of abomasum dalton Anterior descending branch of left coronary artery deca units cytarabine/daunorubicin protocol Dai Chinese Asymptomatic diagnosis of Drug Accountability Domain;ion Iontophoresis Route of Drug Administration Ions;on SPARC wt Allele Osteonectin SPARC gene On (qualifier value) Upon - dosing instruction fragment;Admission Admission activity Hospital admission;Dat SLC6A3 gene SLC6A3 wt Allele dopamine transporter Direct Coombs test SLC6A3 protein, human Test Date cytarabine/daunorubicin/thioguanine Alzheimer's Disease;mission Religious Missions;
+	\begin{tabular}{|p{\linewidth}|}
+		\hline
+		Date Value type - Date date allergenic extract Date in time Data types - Date Date Fruit;Of SPI1 wt Allele SPI1 gene TAF1 wt Allele BRIP1 gene Within Degrees fahrenheit Oral contraception BRIP1 wt Allele;Da Displacement of abomasum dalton Anterior descending branch of left coronary artery deca units cytarabine/daunorubicin protocol Dai Chinese Asymptomatic diagnosis of Drug Accountability Domain;ion Iontophoresis Route of Drug Administration Ions;on SPARC wt Allele Osteonectin SPARC gene On (qualifier value) Upon - dosing instruction fragment;Admission Admission activity Hospital admission;Dat SLC6A3 gene SLC6A3 wt Allele dopamine transporter Direct Coombs test SLC6A3 protein, human Test Date cytarabine/daunorubicin/thioguanine Alzheimer's Disease;mission Religious Missions;\\
+		\hline
 	\end{tabular}
@@
 
-Schema Maps, provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the semantic relationship between their participating attributes.
-This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences, corresponding to each data attribute.
-While the embedded vectors can be generated using any methodology (we tested 11 methodologies, with WordNet and 10 models based on BERT (including BERT base, BERT large, distilBert, and RoBERTa) further detailed in section \ref{experimentalSetup}), the large/STSb version of RoBERTa\cite{reimers-2019-sentence-bert},provides the best results.
+Schema Maps provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the semantic relationship between their participating attributes.
+This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences corresponding to each data attribute.
+While the embedded vectors can be generated using any methodology, we tested 11 methodologies with Word2Vec and 10 models based on BERT (including BERT base, BERT large, distilBert, and RoBERTa) further detailed in section \ref{experimentalSetup}, the large/STSb version of RoBERTa\cite{reimers-2019-sentence-bert}, provides the best results.
 The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them.
@@
 Cosine similarity score of 0 indicates orthogonal relationship between the two vectors, which in our scenario indicates that the two sentences, and by extension their attributes are not related to each other.
--1 indicates, inverse relationship between the attributes, while 1 indicates the two attributes are very much the same.
+-1 indicates inverse relationship between the attributes, while 1 indicates the two attributes are very much the same.
 For producing our schema maps, we are interested in three types of relationships, ``equal'' (the two attributes are same), ``related'' (the two attributes are related to each other), and ``unrelated'' (no relationship between the attributes).
-In order to classify the similarity results, into one of these three classes, we then calculated the best thresholds, using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal'', ``related'', and ``unrelated''.
+In order to classify the similarity results into one of these three classes, we then calculated the best thresholds using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal'', ``related'', and ``unrelated''.
 
@@
 MCC provides a fair measure of the ability with which a classifier can correctly predict both positive and negative instances \cite{chicco2020advantages}.
-MCC score of 0 represents random classification, however, with an increase in the number of true positives and true negatives, MCC moves closer to 1.
+MCC score of 0 represents random classification, however, with an increase in the number of true positives and true negatives MCC moves closer to 1.
 It also takes into account the false positives and false negatives, which shift the mcc score towards -1.
-This measurement is markedly different from accuracy, that fails to account for imbalanced datasets and $F_1$ measure which is not affected by the true negative scores.
-As a result, MCC provides an acceptable alternate, in our current scenario comprising of imbalanced dataset (largely in favour of class ``unrelated'') to measuring the true performance of the models, used for threshold selection and model evaluation.
-Finally on a test dataset we evaluated our multi-class classification approach, using MCC and Cohen's Kappa coefficient ($\kappa$) \cite{gwet2014handbook} to identify the relationships between each pair of attributes.
+This measurement is markedly different from accuracy that fails to account for imbalanced datasets and $F_1$ measure which is not affected by the true negative scores.
+As a result, MCC provides an acceptable alternate in our current scenario comprising of imbalanced dataset (largely in favour of class ``unrelated'') to measuring the true performance of the models, used for threshold selection and model evaluation.
+Finally on a test dataset we evaluated our multi-class classification approach using MCC and Cohen's Kappa coefficient ($\kappa$) \cite{gwet2014handbook} to identify the relationships between each pair of attributes.
 
@@
 We extended the same setup to create an additional 100,000 records, for 1000 patients with 3 medical fragments for $s_1$, $s_2$, and $s_4$, and 97 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$.
-These fragments, follow various design elements, supporting a variety of valid relational storage architectures.
+These fragments follow various design elements supporting a variety of valid relational storage architectures.
 Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
 The code to generate this data set is available at ``uhp\_map\_generation''\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhpr\_storage}.
-This application produces three custom formatted files, containing an index for patients, an index for their medical fragments, and the medical fragment, corresponding to the EMR data.
+This application produces three custom formatted files containing an index for patients, an index for their medical fragments, and the medical fragment corresponding to the EMR data.
 Using the medical fragments file, we then generate the semantically enriched attribute \footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhp\_map\_generation}, which contains the suffixes and their concepts corresponding to each EMR data attribute.
 The resulting set of enriched attributes are temporarily stored in a JSON file, which is then read by the same application to partially generate the schema maps.
-This process, is used to create 20,349 distinct pairs of attributes, across $s$.
+This process is used to create 20,349 distinct pairs of attributes across $s$.
 Each pair also contains the ``relationshipList'', which stores the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
-The JSON file thus produced, is then used by a python script to generate the semantically enriched sentences and their embedded vectors using Word2Vec, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
+The JSON file thus produced is then used by a python script to generate the semantically enriched sentences and their embedded vectors using Word2Vec, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
 The BERT models include ``bert-base-nli-stsb-mean-tokens'', ``bert-large-nli-stsb-mean-tokens'', ``roberta-base-nli-stsb-mean-tokens'', ``roberta-large-nli-stsb-mean-tokens'', ``distilbert-base-nli-stsb-mean-tokens'', ``bert-base-nli-mean-tokens'', ``bert-large-nli-mean-tokens'', ``roberta-base-nli-mean-tokens'', ``roberta-large-nli-mean-tokens'', and ``distilbert-base-nli-mean-tokens''.
 The embedding vectors are then compared using cosine similarity, which produces a score between -1 and 1.
-The rationale behind switching the applications at various stages, is to cache the results and create checkpoints for restarting any failed stages, easily.
+The rationale behind switching the applications at various stages is to cache the results and create checkpoints for restarting any failed stages, easily.
 Additionally, since python provides better support for easy generation of embedding vectors, it was thus preferred over the Java based implementation, which is otherwise very beneficial for other tools.
@@
 
-The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed semantic matching process with fuzzy string matching, embedded vector generation and comparison using Word2Vec, and 10 BERT nli models.
+The validity of our proposed approach has been evaluated using several techniques including comparison of the proposed semantic matching process with fuzzy string matching, embedded vector generation and comparison using Word2Vec, and 10 BERT nli models.
 
@@
 \subsection{Dataset Annotation}
-In order to compare our computed models with ground truth, and to identify the best thresholds for classifying each instance as ``equal'', ``related'', or ``unrelated'' 4 human annotators were utilized, to anonymously, score the similarity of each pair of attribute names.
-In order to support this process, we first repurposed one of our generated data matrix, by marking all attribute pairs belonging to the same schema with the symbol ``-''.
-Following this, the annotators, marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells, with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0'', exactly similar as ``1'', row attribute as child of column attribute as ``<'', row attribute as a parent of the column attribute as ``>'', and finally, unknown as ``~''.
-The data sheets generated after this extensive human effort, have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
+In order to compare our computed models with ground truth and to identify the best thresholds for classifying each instance as ``equal'', ``related'', or ``unrelated'' 4 human annotators were utilized to anonymously, score the similarity of each pair of attribute names.
+In order to support this process, we first repurposed one of our generated data matrix by marking all attribute pairs belonging to the same schema with the symbol ``-''.
+Following this, the annotators marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0'', exactly similar as ``1'', row attribute as child of column attribute as ``<'', row attribute as a parent of the column attribute as ``>'', and finally, unknown as ``~''.
+The data sheets generated after this extensive human effort have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
 
@@
 
-These sheets, additionally contain some missing values, which were left out by the annotators, but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0''.
+These sheets, additionally contain some missing values, which were left out by the annotators but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0''.
 Using $\kappa$, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
@@
 
-This annotated data was then processed, to replace all related entries with ``0.5'' ($class_{0.5}$) and all``-'' with ``0'' ($class_{0}$), while the values for similar at ``1'' ($class_{1}$) and ``0'' ($class_{0}$) for dissimilar were kept the same.
-This conversion was then used to produce a consolidated dataset of 40,698 attribute pairs, using mode scores of all annotators, for each cell.
+This annotated data was then processed to replace all related entries with ``0.5'' ($class_{0.5}$) and all ``-'' with ``0'' ($class_{0}$), while the values for similar at ``1'' ($class_{1}$) and ``0'' ($class_{0}$) for dissimilar were kept the same.
+This conversion was then used to produce a consolidated dataset of 40,698 attribute pairs using mode scores of all annotators for each cell.
 We also tested average scores between the annotators, but that would produce scores between ``0'', ``0.5'', and ``1'', greatly increasing the number of classes for classification.
-Hence the maximum agreement between the annotators, maintains the final label values within these three classes, which become easier to evaluate.
+Hence the maximum agreement between the annotators maintains the final label values within these three classes, which become easier to evaluate.
 Additionally, the original dataset and its mode consolidated form is biased in favour of class ''0'', since most attribute pairs are not related to each other.
 This dataset is then split into development and testing partitions with a ratio of 70:30.
-The development partition is used for threshold selection, based on the best MCC score for identifying class ``equal'', followed by best scores for class ``related'' and finally best of class ''unrelated''.
+The development partition is used for threshold selection based on the best MCC score for identifying class ``equal'', followed by best scores for class ``related'' and finally best of class ''unrelated''.
 The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and $F_1$ measure.
@@
 	\includegraphics[scale=0.83]{thresholdSelection}
-	\caption{Thresholds selection.}
+	\caption{Thresholds selection using MCC scores where t1 indicates the similarity threshold between $class_0$ and $class_{0.5}$, and t2 indicate the similarity threshold between $class_{0.5}$ and $class_1$.}
 	\label{fig:thresholdSelection}
@@
 A good text classification methodology is dependent on the correct choice of a threshold, which can maximize the target class participation.
-In case of independent labels, area under the precision recall curve can provide this optimal measure, however as in our case, for dependent classes on a biased dataset the Matthews Correlation Coefficient (MCC), is better\cite{chicco2020advantages}.
+In case of independent labels, area under the precision recall curve can provide this optimal measure, however as in our case, for dependent classes on a biased dataset the MCC, is better\cite{chicco2020advantages}.
 Since our aim is to apply an optimal text similarity classifier to resolve this multi-class problem ($class_0$, $class_{0.5}$, and $class_1$), we have to test various threshold scores for separating the instances between $class_0$ and $class_{0.5}$ ($t_1$), and then $class_{0.5}$ and $class_1$ ($t_2$).
@@
 
-Threshold values for Word2Vec are placed at the lower end of the spectrum, indicating a very large number of instances are classified as similar (above similarity score of \textit{0.1}), while a small number of instances (with similarity score \textit{0.05}) are classified as dissimilar.
+Threshold values for Word2Vec are placed at the lower end of the spectrum indicating a very large number of instances are classified as similar (above similarity score of \textit{0.1}), while a small number of instances (with similarity score \textit{0.05}) are classified as dissimilar.
 Similarly, the $class_{0.5}$ lies within the similarity threshold of \textit{0.05} similarity points.
-It can be observed that the threshold for selecting the related class, is within \textit{0.05} points, in all except one case (bert-large-nli-mean-tokens where the difference is \textit{0.15} points).
+It can be observed that the threshold for selecting the related class is within \textit{0.05} points, in all except one case (bert-large-nli-mean-tokens where the difference is \textit{0.15} points).
 Five BERT based models, trained on the STSb dataset, all have minimum threshold values of \textit{0.85} and maximum of \textit{0.9}, while the 4 remaining BERT models, lie between \textit{0.9} and \textit{0.95}.
-These results show a general trend, of how the cosine similarity varies/maintains itself, against embedded vectors generated from various pre-trained models.
-In absolute terms, however these threshold values provide the mechanism for classifying the test dataset, which is evaluated for performance, in the next subsection.
+These results show a general trend of how the cosine similarity varies/maintains itself, against embedded vectors generated from various pre-trained models.
+In absolute terms, however these threshold values provide the mechanism for classifying the test dataset, which is evaluated for performance in the next subsection.
 
 \subsection{Model Evaluation}
-On unseen test dataset, with thresholds selected in the previous step and the 12 models, we measured the performance score, using one vs all binarization of the multi-classes.
-As evident in Table \ref{tab:evaluations}, very high values of accuracy are visible across all models, with all three positive classes.
-In all, except the case of Word2Vec, Precision and recall, also show values close to \textit{1.0}.
+On unseen test dataset with thresholds selected in the previous step and the 12 models, we measured the performance score using one vs all binarization of the multi-classes.
+As evident in Table \ref{tab:evaluations}, very high values of accuracy are visible across all models with all three positive classes.
+In all, except the case of Word2Vec, Precision and recall also show values close to \textit{1.0}.
 However, these measures are very misleading, since the dataset is greatly biased in favour of $class_0$.
-In terms of $F_1$ measure $class_{0.5}$ shows the worst possible results, independently, with all except Word2Vec and bert-large-nli-mean-tokens, having a score of \textit{0.0}.
-Bert-large-nli-mean-tokens, provides the best $F_1$ measure at \textit{0.49}.
+In terms of $F_1$ measure $class_{0.5}$ shows the worst possible results, independently, with all except Word2Vec and bert-large-nli-mean-tokens having a score of \textit{0.0}.
+Bert-large-nli-mean-tokens provides the best $F_1$ measure at \textit{0.49}.
 These metrics are thus not useful to gauge the performance of the evaluated models.
-Instead, focusing on the MCC score, provides a good picture of the model performance, for individual classes, when all other instances are negative.
+Instead, focusing on the MCC score, provides a good picture of the model performance for individual classes when all other instances are negative.
 
@@
 	\centering
-	\caption{One vs all binary classifications results}
+	\caption{Performance matrix for individual classes using one vs all binarization technique}
 	\label{tab:evaluations}
@@
 		\hline
-		\textbf{Model}                                        & \textbf{Class Positive} & \textbf{Class Negative} & \multicolumn{1}{c|}{\textbf{accuracy}} & \multicolumn{1}{c|}{\textbf{precision}} & \multicolumn{1}{c|}{\textbf{recall}} & \multicolumn{1}{c|}{\textbf{f-1}} & \multicolumn{1}{c|}{\textbf{mcc}} \\ \hline
+		\textbf{Model}                                        & \textbf{Class Positive} & \textbf{Class Negative} & \multicolumn{1}{c|}{\textbf{Accuracy}} & \multicolumn{1}{c|}{\textbf{Precision}} & \multicolumn{1}{c|}{\textbf{Recall}} & \multicolumn{1}{c|}{\textbf{F-1}} & \multicolumn{1}{c|}{\textbf{MCC}} \\ \hline
 		\multirow{3}{*}{FUZZY\_MATCH}                         & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.98                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
@@
 	\includegraphics[scale=0.83]{evaluation}
-	\caption{Models evaluation.}
+	\caption{Performance evaluation of various models using MCC and $\kappa$ scores.}
 	\label{fig:evaluation}
@@
 
-$F_1$ score, which provides the harmonic mean of precision and recall, ranges between 0 and 1, while MCC provides a fair measure of the ability with which a classifier can correctly predict both positive and negative instances \cite{chicco2020advantages}.
-
-Normalized MCC -> linear interpolation
-x := (c - a) / (b - a)
+Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the nature of the dataset.
+Even before annotation, the dataset is bias in favour of unrelated attributes.
+As established by the human experts and the machine learning model, for 254 attributes involved in 40698 possible pairs only a little over 300 similar instances are found.
+In these circumstances performance metrics, such as accuracy, precision, and recall are meaningless.
+These metrics are unable to account for the imbalanced datasets and provide an incorrect view of the classifier's accuracy.
+Instead metrics such as $F_1$, MCC, $\kappa$ can provide a true picture of the classifier's accuracy.
+These metrics are also well suited for evaluating multi-class classifiers, using one vs all or one vs one binarizations of the dataset, as well as consolidating the results into a single measure.
+In our experimentations, we also evaluated the area under the Receiver Operating Characteristic (ROC) curve and area under the Precision Recall curve, as a threshold selection metric.
+However these graphs are well suited for independent classes and in our case it is important to maximize the identification of similar attribute pairs, followed by related ones and finally the unrelated ones.
+This kind of dependent classification can then be used in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.
 

### 2021-06-05 ManuScript/IEEEAccess/ManuScript.tex
kappa upated
update

@@
 		MLM                        & Medical Logic Module                                    \\
-		CIMI                       & Clinical Information Modeling Initiative                \\
+		openCIMI                       & Clinical Information Modeling Initiative                \\
 		UHP                        & Ubiquitous Health Platform                              \\
@@
 However, the plethora of standards necessitates the creation of bridging standards that can resolve the heterogeniety between the medical standards.
-Substantial effort has gone into this endeavor with the Clinical Information Modeling Initiative (CIMI) \cite{CIMI2015} taking the lead in bridging the gap between HL7v3 and openEHR.
+Substantial effort has gone into this endeavor with the Clinical Information Modeling Initiative (openCIMI) \cite{CIMI2015} taking the lead in bridging the gap between HL7v3 and openEHR.
 Similarly, SNOMED CT and LOINC are working to resolve the redundancies between the two terminological standards since 2013.
@@
 	\item[$-$] Section \ref{results} presents the results
-	\item[$-$] Section 6 concludes the paper.
+	\item[$-$] Section \ref{discussion} discusses the challenges and limitations of the presented methodology and its evaluations
+	\item[$-$] Section \ref{conclusion} concludes the paper.
 \end{itemize}
@@
 	\includegraphics[scale=0.83]{evaluation}
-	\caption{Performance evaluation of various models using MCC and $\kappa$ scores.}
+	\caption{Performance evaluation of various models using MCC and kappa ($\kappa$) scores.}
 	\label{fig:evaluation}
@@
 \section{Discussion}
+\label{discussion}
 In text classification, production and use of a well annotated corpus for supervised and semi-supervised learning is of utmost importance.
@@
 However, in the real world the production and maintenance of these corpora is an expensive task, often requiring extensive human effort.
-While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively provide a label to an instance.
+While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively provide a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}.
 This is also evident in the case of our annotated dataset, whereby the instances have been labeled by four human experts (two medical practioners and two computer science graduates), using their subjective knowledge.
@@
 According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child.
-While the selection of this label can be debated from an subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect.
-As a result, the annotations were kept anonymous with random to as not to induce any biasedness.
-Hence, the annotated data in its original form becomes the basis of our threshold selection and model evaluation methodology.
-A side-effect of this choice is the lower scores of agreement between the (annotated data) true labels and predicted labels.
+While the selection of this label can be debated from an subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}.
+As a result, the annotations were kept anonymous so as not to induce any bias.
+Thus, the complete annotated data in its original form became the basis of our threshold selection and model evaluation methodology.
+A mode based voting mechanism was then used to resolve the differences between the annotators.
+The consolidated true dataset was then formed based on the agreed upon label by atleast 3 annotators.
+As pointed out in \cite{reidsma2008exploiting}, the net effect of such a voting mechanism is an increase in the precision of the machine learning classifiers in lieu of, their accuracy.
+However, as shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC.
+The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextful and relative manner.
 
@@
 These metrics are unable to account for the imbalanced datasets and provide an incorrect view of the classifier's accuracy.
-Instead metrics such as $F_1$, MCC, $\kappa$ can provide a true picture of the classifier's accuracy.
+Instead metrics such as $F_1$, MCC, and $\kappa$ can provide a true picture of the classifier's accuracy.
 These metrics are also well suited for evaluating multi-class classifiers, using one vs all or one vs one binarizations of the dataset, as well as consolidating the results into a single measure.
-In our experimentations, we also evaluated the area under the Receiver Operating Characteristic (ROC) curve and area under the Precision Recall curve, as a threshold selection metric.
-However these graphs are well suited for independent classes and in our case it is important to maximize the identification of similar attribute pairs, followed by related ones and finally the unrelated ones.
-This kind of dependent classification can then be used in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.
+In our experimentation, we also evaluated the Area Under the Receiver Operating Characteristic (AUROC) curve and Area Under the Precision Recall (AUPR) curve, as a threshold selection metric.
+However these graphs are well suited for independent classes as shown in \cite{espindola2005extending}, and in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$).
+AUROC and AUPR were thus replaced with our current approach for threshold selection.
+The benefit of using this kind of dependent classification is its usefulness in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.
 
 \section{Conclusion}
+\label{conclusion}
 Healthcare information systems are slowly moving towards a standardized approach, whereby the storage, exchange, and usage of health data, information, and knowledge is becoming interoperable.

### 2021-06-05 ManuScript/IEEEAccess/draft/ManuScript.tex
formatted output

--- 2021-06-05 ManuScript/IEEEAccess/ManuScript.tex
@@
 \usepackage{ulem}
+\usepackage{hyperref}
 
@@
 \markboth
-{Fahad \headeretal:Ensemble feature ranking for cost-based non-overlapping groups}
-{Fahad \headeretal:Ensemble feature ranking for cost-based non-overlapping groups}
+{Fahad \headeretal:Unsupervised Semantic Mapping for Healthcare Data Stroage Schema}
+{Fahad \headeretal:Unsupervised Semantic Mapping for Healthcare Data Stroage Schema}
 
-\corresp{Corresponding authors: Sungyoung Lee (e-mail: sylee@oslab.khu.ac.kr) and TaeChoog Chung (e-mail: tcchung@@khu.ac.kr)}
+\corresp{Corresponding authors: Sungyoung Lee (e-mail: sylee@oslab.khu.ac.kr) and TaeChoong Chung (e-mail: tcchung@khu.ac.kr)}
 
@@
 	\includegraphics[width=\columnwidth]{kappaInterAnnotatorAgrement}
-	\caption{Cohen's Kappa ($\kappa$) score between the four annotators}
+	\caption{Cohen's Kappa ($\kappa$) score among the four annotators}
 	\label{fig:kappaInterAnnotatorAgrement}
@@
 Following this, the annotators marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0'', exactly similar as ``1'', row attribute as child of column attribute as ``<'', row attribute as a parent of the column attribute as ``>'', and finally, unknown as ``~''.
-The data sheets generated after this extensive human effort have been made available for other researchers\footnote{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}.
+The data sheets generated after this extensive human effort have been made available for other researchers\footnote{\url{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}}.
 
@@
 
-Threshold values for Word2Vec are placed at the lower end of the spectrum indicating a very large number of instances are classified as similar (above similarity score of \textit{0.1}), while a small number of instances (with similarity score \textit{0.05}) are classified as dissimilar.
-Similarly, the $class_{0.5}$ lies within the similarity threshold of \textit{0.05} similarity points.
-It can be observed that the threshold for selecting the related class is within \textit{0.05} points, in all except one case (bert-large-nli-mean-tokens where the difference is \textit{0.15} points).
-Five BERT based models, trained on the STSb dataset, all have minimum threshold values of \textit{0.85} and maximum of \textit{0.9}, while the 4 remaining BERT models, lie between \textit{0.9} and \textit{0.95}.
-These results show a general trend of how the cosine similarity varies/maintains itself, against embedded vectors generated from various pre-trained models.
-In absolute terms, however these threshold values provide the mechanism for classifying the test dataset, which is evaluated for performance in the next subsection.
-
-\subsection{Model Evaluation}
-On unseen test dataset with thresholds selected in the previous step and the 12 models, we measured the performance score using one vs all binarization of the multi-classes.
-As evident in Table \ref{tab:evaluations}, very high values of accuracy are visible across all models with all three positive classes.
-In all, except the case of Word2Vec, Precision and recall also show values close to \textit{1.0}.
-However, these measures are very misleading, since the dataset is greatly biased in favour of $class_0$.
-In terms of $F_1$ measure $class_{0.5}$ shows the worst possible results, independently, with all except Word2Vec and bert-large-nli-mean-tokens having a score of \textit{0.0}.
-Bert-large-nli-mean-tokens provides the best $F_1$ measure at \textit{0.49}.
-These metrics are thus not useful to gauge the performance of the evaluated models.
-Instead, focusing on the MCC score, provides a good picture of the model performance for individual classes when all other instances are negative.
-
 % Please add the following required packages to your document preamble:
@@
 \end{table*}
+
+Threshold values for Word2Vec are placed at the lower end of the spectrum indicating a very large number of instances are classified as similar (above similarity score of \textit{0.1}), while a small number of instances (with similarity score \textit{0.05}) are classified as dissimilar.
+Similarly, the $class_{0.5}$ lies within the similarity threshold of \textit{0.05} similarity points.
+It can be observed that the threshold for selecting the related class is within \textit{0.05} points, in all except one case (bert-large-nli-mean-tokens where the difference is \textit{0.15} points).
+Five BERT based models, trained on the STSb dataset, all have minimum threshold values of \textit{0.85} and maximum of \textit{0.9}, while the 4 remaining BERT models, lie between \textit{0.9} and \textit{0.95}.
+These results show a general trend of how the cosine similarity varies/maintains itself, against embedded vectors generated from various pre-trained models.
+In absolute terms, however these threshold values provide the mechanism for classifying the test dataset, which is evaluated for performance in the next subsection.
+
+\subsection{Model Evaluation}
+On unseen test dataset with thresholds selected in the previous step and the 12 models, we measured the performance score using one vs all binarization of the multi-classes.
+As evident in Table \ref{tab:evaluations}, very high values of accuracy are visible across all models with all three positive classes.
+In all, except the case of Word2Vec, Precision and recall also show values close to \textit{1.0}.
+However, these measures are very misleading, since the dataset is greatly biased in favour of $class_0$.
+In terms of $F_1$ measure $class_{0.5}$ shows the worst possible results, independently, with all except Word2Vec and bert-large-nli-mean-tokens having a score of \textit{0.0}.
+Bert-large-nli-mean-tokens provides the best $F_1$ measure at \textit{0.49}.
+These metrics are thus not useful to gauge the performance of the evaluated models.
+Instead, focusing on the MCC score, provides a good picture of the model performance for individual classes when all other instances are negative.
 

### 2021-06-05 ManuScript/IEEEAccess/submission 0/source/ManuScript.tex
sub 0

--- 2021-06-05 ManuScript/IEEEAccess/draft/ManuScript.tex
@@
 Additionally, the annotated data, collected against five medical schemas and labeled by 4 annotators is made available for helping future researchers.
-Our results indicate, that for biased, dependent multi-class text classification, RoBERTa shows the best performance, achieving a cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
+Our results indicate, that for biased, dependent multi-class text classification, RoBERTa shows the best performance, achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
 \end{abstract}

### 2021-06-05 ManuScript/IEEEAccess/submission 0/source/ManuScript.tex
key word setting

@@
 \begin{keywords}
-Context aware systems, Decision support systems, Electronic medical records,Experts systems,   Health information management, Medical information systems, Ontology engineering, Text processing, Unsupervised learning
+Context awareness, Decision support systems, Expert systems, Health information management, Medical information systems, Ontology engineering, Text processing, Unsupervised learning
 \end{keywords}

### 2021-06-05 ManuScript/IEEEAccess/submission 0/source/ManuScript.tex
cite fixed

@@
 These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
-al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$) \ref{ali2017reconciliation}.
-Each of these medical systems as shown in \ref{fig:schema}, follows the relational database design with logical entities such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
+al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$) \cite{ali2017reconciliation}.
+Each of these medical systems as shown in Figure \ref{fig:schema}, follows the relational database design with logical entities such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
 While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.

### 2021-07-25 ManuScript/IEEEAccess/Revision 1/source/ManuScript.tex
revision 1

--- 2021-06-05 ManuScript/IEEEAccess/submission 0/source/ManuScript.tex
@@
 We present a novel methodology for bridging the gap between various healthcare data management solutions by leveraging the strength of transformer based machine learning models, to create mappings between the data elements.
-Additionally, the annotated data, collected against five medical schemas and labeled by 4 annotators is made available for helping future researchers.
-Our results indicate, that for biased, dependent multi-class text classification, RoBERTa shows the best performance, achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
+Additionally, the annotated data, collected against five medical schemas and labeled by four annotators is made available for helping future researchers.
+Our results indicate, that for biased, dependent multi-class text classification, transformer based models provide better results than linguistic and other classical models.
+In particular, the Robustly Optimized BERT Pretraining Approach (RoBERTa) provides the best schema matching performance by achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
 \end{abstract}
@@
 In this way, successive healthcare treatments can take benefit from earlier diagnosis, treatment, and followup procedures, thereby reducing the stress on healthcare experts and systems.
+\\
 Healthcare Standards such as HL7 - Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
@@
 Similarly Medical Logic Module (MLM) provides a standardized way for expressing medical knowledge.
-However, the plethora of standards necessitates the creation of bridging standards that can resolve the heterogeniety between the medical standards.
+Variety in these and many other healthcare standards necessitates the creation of bridging standards that can resolve the heterogeneity between the medical standards \cite{mohammed2010ubiquitous}.
 Substantial effort has gone into this endeavor with the Clinical Information Modeling Initiative (openCIMI) \cite{CIMI2015} taking the lead in bridging the gap between HL7v3 and openEHR.
 Similarly, SNOMED CT and LOINC are working to resolve the redundancies between the two terminological standards since 2013.
-This healthcare interoperability solution follows a formal, albiet long process, which is greatly dependent on the human factor.
+This healthcare interoperability solution follows a formal, albeit long process, which is greatly dependent on the human factor.
 However, the current healthcare scenario requires a quick solution to create a scaffolding of an interoperable bridge between various healthcare providers.
@@
 This methodology is based on the creation and management of schema maps, that can provide the framework for transforming a source schema into a target schema.
+\\
 In the current study, we will present our research work to build and manage the schema map knowledge base.
@@
 Martono et al.
-\cite{martono2017review} provided overview of previous studies related to linguistic approaches used for schema matching.
-Linguistic methods focused on finding strings and evaluate there similarity in different schemas.
-The string are normally normalized before to align both the strings before similarity comparison.
-The normalized strings are categories based on the information relatedness and element with similar category are compared using various similarity measure including  Jaro-distance, Lavenstein (edit-distance), and many more.
+\cite{martono2017review} provided an overview of a linguistic approach for schema matching.
+The authors presented various linguistic methods to identify token strings in element names, followed by similarity evaluation between various schema.
+The process starts by normalizing the strings, which can be achieved via tokenization, generalization, elimination or semantic tagging.
+The normalized strings are then categorized based on their information relatedness.
+Elements belonging to the same categories are then compared with each other using two similarity measures, which include Lavenstein distance between words and Jaro-distance between 3-grams character sub-strings.
 Alwan et al.
-\cite{alwan2017survey} have summarized the techniques used in the literature for schemas and instances based schema matching.
-The information used for schema matching is categories into  schema information, instance and auxiliary information.
-Most of the searchers have used syntactic techniques (including n-gram, and regular expression), semantic techniques (including Latent Semantic Analysis, WordNet/Thesaurus and Google Similarity) for schema level and instance level matching to achieve the final goal of data/information interoperability.
+\cite{alwan2017survey} has summarized the techniques used in literature for schema matching based on database schemas and instances.
+These techniques can be categorized based on the type of information used for schema matching which includes  schema level, instance level, hybrid (schema and instances) and auxiliary (which can include information from external sources).
+Accordingly, most research is focused towards schema level and instance level approaches which can utilize syntactic techniques (such as n-gram, and/or regular expressions) and/or semantic techniques (such as Latent Semantic Analysis, WordNet/Thesaurus, and Google Similarity), to achieve data/information interoperability.
 Kersloot et al.
 \cite{kersloot2020natural} performed a comprehensive systematic review to evaluate Natural Language Processing (NLP) algorithms used for clinical text mapping onto ontological concepts.
-The findings of the studies were evaluated with respect to five categories; use of NLP algorithms, data used, validation and evaluation performed, result presentation, and generalization of results.
+The authors categorized the findings of various studies based on the use of NLP algorithms, data, validation and evaluation techniques, result presentation, and generalization of results.
 The authors revealed that over one-fourth of the NLP algorithms used were not evaluated and have no validation.
@@
 The experimental results revealed framework effectiveness by achieving more than 90\% precision and recall for direct and indirect link matching.
-
-A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al.
-\cite{moll2020oncology} to check their perspectives regarding Patient Accessible Electronic Health Record (PAEHR).
-The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations.
-The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions.
-However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.
 
@@
 To this end, the creation of a cohesive workflow is of utmost importance.
-In our earlier work \cite{Satti2020} we used maximum sequence identification and suffix tress based matching for syntactic matching of two distinct data schemas.
+In our earlier work \cite{Satti2020} we used maximum sequence identification and suffix trees based matching for syntactic matching of two distinct data schemas.
 This was followed by semantic concept enrichment and subsequently concept matching for creating rules in the form of schema maps.
 The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data into an interpretable model form.
-In our current methodology as visualized in Figure \ref{methodology}, we have utilized state-of-the-art natural language processing (NLP) techniques to extract the schema mapping rules from semi-structured data schemas.
+In our current methodology as visualized in Figure \ref{fig:methodology}, we have utilized state-of-the-art natural language processing (NLP) techniques to extract the schema mapping rules from semi-structured data schemas.
 This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas.
 Traditional NLP techniques such as Word2Vec are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence \cite{zhu2018exploring}.
-However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
+Many of the attribute names within data schemas are represented by terms that are bigger than a word (combination of multiple words) and smaller than a sentence.
 In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names.
@@
 In the former case, while SNOMED-CT provides a mechanism for identifying the standard codes for clinical terms and LOINC can be used for laboratory related terms, most attribute names are created based on the gut feeling of the database designer.
-Additionally, while these codes can be used to represent data instances, the data schema, achieves no benefit from the same.
+Additionally, while these codes can be used to represent elements in the data instances (such as when recording the disease name, a standard code is more beneficial than the text string for semantic interoperability), the elements in a data schema (such as attribute names which are used in queries) achieve no benefit from the same.
 Consider the terms ``name'' and ``patientName'', which refer to the same attribute of the patient entity.
@@
 This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences corresponding to each data attribute.
-While the embedded vectors can be generated using any methodology, we tested 11 methodologies with Word2Vec and 10 models based on BERT (including BERT base, BERT large, distilBert, and RoBERTa) further detailed in section \ref{experimentalSetup}, the large/STSb version of RoBERTa\cite{reimers-2019-sentence-bert}, provides the best results.
+While the embedded vectors can be generated using any methodology, we tested 11 methodologies with Word2Vec and 10 models based on BERT further detailed in section \ref{experimentalSetup}.
+Our results indicate that the large/STSb version of Robustly Optimized BERT Pretraining Approach (RoBERTa)\cite{reimers-2019-sentence-bert}, provides the best matching results.
 The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them.
@@
 \begin{equation}
+\label{eq:mccformula}
 \resizebox{0.9\hsize}{!}{$%
-	MCC = \frac{(TP.FN) - (FP.FN)}{\sqrt{(TP+FP)(TP+FN)(TN+FP)(TN+FN)}}\longrightarrow [-1,1]
+	MCC = \frac{(TP \times TN) - (FP \times FN)}{\sqrt{(TP+FP)\times(TP+FN)\times(TN+FP)\times(TN+FN)}}\longrightarrow [-1,1]
 	$%
@@
 MCC provides a fair measure of the ability with which a classifier can correctly predict both positive and negative instances \cite{chicco2020advantages}.
+The formula for calculating MCC is shown in Equation \ref{eq:mccformula}, which is based on classification performance measures such as true positive (TP), true negative (TN), false positive (FP), and false negative (FN).
 MCC score of 0 represents random classification, however, with an increase in the number of true positives and true negatives MCC moves closer to 1.
-It also takes into account the false positives and false negatives, which shift the mcc score towards -1.
+It also takes into account the false positives and false negatives, which shift the MCC score towards -1.
 This measurement is markedly different from accuracy that fails to account for imbalanced datasets and $F_1$ measure which is not affected by the true negative scores.
@@
 These fragments follow various design elements supporting a variety of valid relational storage architectures.
-Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
+Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
 The code to generate this data set is available at ``uhp\_map\_generation''\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhpr\_storage}.
@@
 The BERT models include ``bert-base-nli-stsb-mean-tokens'', ``bert-large-nli-stsb-mean-tokens'', ``roberta-base-nli-stsb-mean-tokens'', ``roberta-large-nli-stsb-mean-tokens'', ``distilbert-base-nli-stsb-mean-tokens'', ``bert-base-nli-mean-tokens'', ``bert-large-nli-mean-tokens'', ``roberta-base-nli-mean-tokens'', ``roberta-large-nli-mean-tokens'', and ``distilbert-base-nli-mean-tokens''.
-The embedding vectors are then compared using cosine similarity, which produces a score between -1 and 1.
+The embedding vectors are then compared using cosine similarity.
 The rationale behind switching the applications at various stages is to cache the results and create checkpoints for restarting any failed stages, easily.
@@
 \subsection{Dataset Annotation}
-In order to compare our computed models with ground truth and to identify the best thresholds for classifying each instance as ``equal'', ``related'', or ``unrelated'' 4 human annotators were utilized to anonymously, score the similarity of each pair of attribute names.
+In order to compare our computed models with ground truth and to identify the best thresholds for classifying each instance as ``equal'', ``related'', or ``unrelated'' four human annotators were utilized to anonymously, score the similarity of each pair of attribute names.
 In order to support this process, we first repurposed one of our generated data matrix by marking all attribute pairs belonging to the same schema with the symbol ``-''.
@@
 The ``Annotator3'' has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty.
-However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness.
+Even in the presence of these differences, it is pertinent to include the data for all annotators in order to avoid any bias.
 
@@
 These models include, ``Fuzzy\_Wuzzy'', ``Word2Vec'', and 10 BERT based models.
+The optimal thresholds achieved by each of these models is shown in Figure \ref{fig:thresholdSelection}.
 
@@
 As evident in Table \ref{tab:evaluations}, very high values of accuracy are visible across all models with all three positive classes.
-In all, except the case of Word2Vec, Precision and recall also show values close to \textit{1.0}.
+In all, except the case of Word2Vec, precision and recall also show values close to \textit{1.0}.
 However, these measures are very misleading, since the dataset is greatly biased in favour of $class_0$.
@@
 These scores range between [-1,1], providing a measure quantifying the accuracy of the classifier to correctly predict correct and incorrect instances.
-The models Word2Vec, bert-large-nli-mean-tokens, and roberta-base-nli-mean-tokens, with values between [0,0.20] indicate random classification, while $\kappa$ score between [0.21,0.39], achieved by fuzzy wuzzy, bert-base-nli-mean-tokens, roberta-base-nli-sts-mean-tokens, distilbert-base-nli-stsb-mean-tokens, bert-base-nli-mean-tokens, roberta-large-nli-mean-tokens, and distilbert-base-nli-mean-tokens, show only minimal agreement with the annotated data \cite{mchugh2012interrater}.
+As shown in Figure \ref{fig:evaluation}, the models Word2Vec, bert-large-nli-mean-tokens, and roberta-base-nli-mean-tokens, with values between [0,0.20] indicate random classification, while $\kappa$ score between [0.21,0.39], achieved by fuzzy wuzzy, bert-base-nli-mean-tokens, roberta-base-nli-sts-mean-tokens, distilbert-base-nli-stsb-mean-tokens, bert-base-nli-mean-tokens, roberta-large-nli-mean-tokens, and distilbert-base-nli-mean-tokens, show only minimal agreement with the annotated data \cite{mchugh2012interrater}.
 Relative best rates, in this case, are achieved by roberta-large-nli-stsb-mean-tokens, which substantially surpasses the other models, however in absolute terms, it shows only weak agreement.
@@
 As pointed out in \cite{reidsma2008exploiting}, the net effect of such a voting mechanism is an increase in the precision of the machine learning classifiers in lieu of, their accuracy.
-However, as shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC.
+As shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC.
 The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextful and relative manner.
@@
 In our experimentation, we also evaluated the Area Under the Receiver Operating Characteristic (AUROC) curve and Area Under the Precision Recall (AUPR) curve, as a threshold selection metric.
-However these graphs are well suited for independent classes as shown in \cite{espindola2005extending}, and in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$).
+These graphs are well suited for independent classes as shown by \cite{espindola2005extending}.
+Additionally, in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$).
 AUROC and AUPR were thus replaced with our current approach for threshold selection.
 The benefit of using this kind of dependent classification is its usefulness in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.
+
+\textbf{Transparency}
+Through this research we aim to bridge the gap between healthcare schema, which is imperative for providing the medical experts with a complete picture of the patient's health record.
+
+A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al.
+\cite{moll2020oncology} to check their perspectives regarding Patient Accessible Electronic Health Record (PAEHR).
+The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations.
+The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions.
+However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.
 

### 2021-08-02 Implementation/similarity.py
newchanges

@@ -54,17 +54,22 @@ class Similarity:
 
     def __init__(self):
         self.embeddingVectors = {}
-        self.models = ['bert-base-nli-stsb-mean-tokens',
-                       'bert-large-nli-stsb-mean-tokens',
-                       'roberta-base-nli-stsb-mean-tokens',
-                       'roberta-large-nli-stsb-mean-tokens',
-                       'distilbert-base-nli-stsb-mean-tokens',
-                       'bert-base-nli-mean-tokens',
-                       'bert-large-nli-mean-tokens',
-                       'roberta-base-nli-mean-tokens',
-                       'roberta-large-nli-mean-tokens',
-                       'distilbert-base-nli-mean-tokens'
-                       ]
+        # self.models = ['bert-base-nli-stsb-mean-tokens',
+        #                'bert-large-nli-stsb-mean-tokens',
+        #                'roberta-base-nli-stsb-mean-tokens',
+        #                'roberta-large-nli-stsb-mean-tokens',
+        #                'distilbert-base-nli-stsb-mean-tokens',
+        #                'bert-base-nli-mean-tokens',
+        #                'bert-large-nli-mean-tokens',
+        #                'roberta-base-nli-mean-tokens',
+        #                'roberta-large-nli-mean-tokens',
+        #                'distilbert-base-nli-mean-tokens'
+        #                ]
+        self.models = [
+    'roberta-base-nli-mean-tokens',
+    'roberta-large-nli-mean-tokens',
+    'distilbert-base-nli-mean-tokens'
+    ]
         # self.models = ['bert-base-nli-stsb-mean-tokens']
 
     def readData(self, url):
@@ -169,11 +174,11 @@ class Similarity:
     @staticmethod
     def createSentenceForAA(node):
         word_concept_map = {}
-        for concept in node['conceptArray']:
-            if concept['token'] not in word_concept_map:
-                word_concept_map[concept['token']] = []
-            word_concept_map[concept['token']].append(concept['name'])
-        # print(word_concept_map)
+        # for concept in node['conceptArray']:
+        #     if concept['token'] not in word_concept_map:
+        #         word_concept_map[concept['token']] = []
+        #     word_concept_map[concept['token']].append(concept['name'])
+        # # print(word_concept_map)
         sentence = ""
         for suffix in word_concept_map:
[…]

### 2021-08-04 Implementation/results.py
model result

@@ -10,8 +10,8 @@ class Results:
     # BASE_INDEX = 2
     # FUZZY_WUZZY_INDEX = 1
     # SYN_AND_SEM_SIM_INDEX = 0
-    computational_iteration = "1.7"
-    amplified_similarity_execution_index = "0.5"
+    computational_iteration = "4.0"
+    amplified_similarity_execution_index = "4.0"
     models = ['bert-base-nli-stsb-mean-tokens',
               'bert-large-nli-stsb-mean-tokens',
               'roberta-base-nli-stsb-mean-tokens',
@@ -204,6 +204,7 @@ data = resultObj.readData('Data/AmplifiedSimilarity-V'+resultObj.amplified_simil
 print('data')
 print(len(data))
 
+
 #resultObj.generateCSV(data)
 
 
@@ -211,12 +212,12 @@ print(len(data))
 
 #for syn in frange(0.1, 0.9, 0.1):
 
-resultObj.printBaseHeatMap(data, 'FUZZY_MATCH')
+#resultObj.printBaseHeatMap(data, 'FUZZY_MATCH')
 # resultObj.printBaseHeatMap(data, 'Word2Vec')
 
 
 for model_baseline in resultObj.models:
-    resultObj.printBaseHeatMap(data, model_baseline)
+    resultObj.printBaseHeatMap(data, model_baseline, True)
 
 for syn in numpy.arange(0, 1, 0.1):
     syn = round(syn, 1)

### 2021-08-04 Implementation/similarity.py

@@ -54,22 +54,22 @@ class Similarity:
 
     def __init__(self):
         self.embeddingVectors = {}
-        # self.models = ['bert-base-nli-stsb-mean-tokens',
-        #                'bert-large-nli-stsb-mean-tokens',
-        #                'roberta-base-nli-stsb-mean-tokens',
-        #                'roberta-large-nli-stsb-mean-tokens',
-        #                'distilbert-base-nli-stsb-mean-tokens',
-        #                'bert-base-nli-mean-tokens',
-        #                'bert-large-nli-mean-tokens',
-        #                'roberta-base-nli-mean-tokens',
-        #                'roberta-large-nli-mean-tokens',
-        #                'distilbert-base-nli-mean-tokens'
-        #                ]
-        self.models = [
-    'roberta-base-nli-mean-tokens',
-    'roberta-large-nli-mean-tokens',
-    'distilbert-base-nli-mean-tokens'
-    ]
+        self.models = ['bert-base-nli-stsb-mean-tokens',
+                       'bert-large-nli-stsb-mean-tokens',
+                       'roberta-base-nli-stsb-mean-tokens',
+                       'roberta-large-nli-stsb-mean-tokens',
+                       'distilbert-base-nli-stsb-mean-tokens',
+                       'bert-base-nli-mean-tokens',
+                       'bert-large-nli-mean-tokens',
+                       'roberta-base-nli-mean-tokens',
+                       'roberta-large-nli-mean-tokens',
+                       'distilbert-base-nli-mean-tokens'
+                       ]
+    #     self.models = [
+    # 'roberta-base-nli-mean-tokens',
+    # 'roberta-large-nli-mean-tokens',
+    # 'distilbert-base-nli-mean-tokens'
+    # ]
         # self.models = ['bert-base-nli-stsb-mean-tokens']
 
     def readData(self, url):
@@ -180,7 +180,7 @@ class Similarity:
         #     word_concept_map[concept['token']].append(concept['name'])
         # # print(word_concept_map)
         sentence = ""
-        for suffix in word_concept_map:
+        for suffix in node['suffixArray']:
             sentence += suffix + " " #+ " ".join(word_concept_map[suffix]) + ";"
 
         return [sentence]
@@ -362,10 +362,10 @@ class Similarity:
             print('model: ', model)
             attributes = self.calculateAmplifiedSimilarity(attributes, model)
 
[…]

### 2021-08-04 ManuScript/IEEEAccess/Revision 1/final/AuthorsBios.tex

--- 2021-06-05 ManuScript/IEEEAccess/submission 0/source/ManuScript.tex
@@
 \begin{document}
-\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-\doi{10.1109/ACCESS.2017.DOI}
-
-\title{Unsupervised Semantic Mapping for Healthcare Data Storage Schema}
-
-\author{ \uppercase{Fahad Ahmed Satti}\authorrefmark{1,2},
-	\uppercase{Musarrat Hussain}\authorrefmark{1},
-	\uppercase{Jamil Hussain}\authorrefmark{3},
-	\uppercase{Syed Imran Ali}\authorrefmark{1}, % \IEEEmembership{} 
-	\uppercase{Taqdir Ali}\authorrefmark{1},
-	\uppercase{Hafiz Syed Muhammad Bilal}\authorrefmark{1,2},
-	\uppercase{TaeChoong Chung}\authorrefmark{1},and  \uppercase {Sungyoung Lee}\authorrefmark{1}
-	\IEEEmembership{Member, IEEE}}
-\address[1]{Department of Computer Science and Engineering, Kyung Hee University, Seocheon-dong, Giheung-gu South Korea (e-mail: \{fahad.satti, musarrat.hussain, imran.ali, bilalrizvi, sylee\}@oslab.khu.ac.kr,  tcchung@khu.ac.kr)}
-\address[2]{National Univeristy of Sciences and Technology, School of Electrical Engineering and Computer Science NUST-SEECS, Islamabad, Pakistan (e-mail: \{fahad.satti, bilal.ali\}@seecs.edu.pk)}
-\address[3]{Department of Data Science, Sejong University, Seoul, South Korea (e-mail: jamil@sejong.ac.kr)}
-\tfootnote{}
-
-\markboth
-{Fahad \headeretal:Unsupervised Semantic Mapping for Healthcare Data Stroage Schema}
-{Fahad \headeretal:Unsupervised Semantic Mapping for Healthcare Data Stroage Schema}
-
-\corresp{Corresponding authors: Sungyoung Lee (e-mail: sylee@oslab.khu.ac.kr) and TaeChoong Chung (e-mail: tcchung@khu.ac.kr)}
-
-\begin{abstract}
-Data, information, and knowledge processing systems, in the domain of healthcare are currently plagued by the heterogeneity at various levels.
-Current solutions, have focused on developing a standard based, manual intervention mechanism, which requires a large amount of human resource and necessitate realignment of existing systems.
-State-of-the-art methodologies in the field of natural language processing and machine learning, can help to partially automate this process, reducing the resource requirements and providing a relatively good multi-class based classification algorithm.
-We present a novel methodology for bridging the gap between various healthcare data management solutions by leveraging the strength of transformer based machine learning models, to create mappings between the data elements.
-Additionally, the annotated data, collected against five medical schemas and labeled by 4 annotators is made available for helping future researchers.
-Our results indicate, that for biased, dependent multi-class text classification, RoBERTa shows the best performance, achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
-\end{abstract}
-
-\begin{keywords}
-Context awareness, Decision support systems, Expert systems, Health information management, Medical information systems, Ontology engineering, Text processing, Unsupervised learning
-\end{keywords}
-
-\titlepgskip=-15pt
-
-\maketitle
-
-\section{Introduction}
-\label{intro}
-\PARstart{D}{ata} and Information modeling in the healthcare domain have witnessed significant improvements in the last decade owing to advances in the development of state-of-the-art Information and Communication Technologies (ICT) and formalization of storage and messaging standards.
-Subsequently, the scope of Healthcare Management Information Systems (HMIS), medical ontologies, and Clinical Decision Support Systems (CDSS) has broadened, beyond the operational capabilities of traditional rule based systems.
-One of the major reasons behind this limitation is due to the numerous heterogeneities in healthcare at data, knowledge, and process level.
-Thus, healthcare interoperability which aims to provide a solution to this problem, can be compartmentalized into data interoperability, process interoperability, and knowledge interoperability.
-Various abbreviations, used in this manuscript are listed in Table \ref{tab:abbreviations}.
-
-Data interoperability resolves the heterogeneity between data artificats to enable seamless and interpretable communcation among source and target organizations, while preserving the data's original intention during storage, communication, and usage (as defined by IEEE 610.12 \cite{geraci1991ieee}, Health Level Seven International (HL7), and Healthcare Information and Management Systems Society HIMSS \cite{Himss_url2013}).
-On the other hand, process interoperability regulates the communication among organizational processes to provide compatability between process artifacts within and seamless transformations across different organizations\cite{khan2013process}.
-Lastly, knowledge interoperability provides a sharing mechanism for reusing interpretable medical knowledge, acquired through expert intervention and other mechanisms, across decision support systems \cite{ali2017multi}.
-
-\begin{table}[]
-	\centering
-	\caption{Abbreviations}
-	\label{tab:abbreviations}
-	\begin{tabular}{ll}
-		\hline
-		Abbreviations              & Full Form                                               \\ \hline
-		ICT                        & Information and Communication Technologies              \\
-		HMIS                       & Healthcare Management Information Systems               \\
-		CDSS                       & Clinical Decision Support Systems                       \\
-		HL7                        & Health Level Seven International                        \\
-		HIMSS                      & Healthcare Information and Management Systems Society   \\
-		FHIR                       & Fast Healthcare Interoperability Resources              \\
-		Snomed-CT                  & Systematized Nomenclature of Medicine—Clinical Terms    \\
-		LOINC                      & Logical Observation Identifiers Names and Codes         \\
-		MLM                        & Medical Logic Module                                    \\
-		openCIMI                       & Clinical Information Modeling Initiative                \\
-		UHP                        & Ubiquitous Health Platform                              \\
-		NLP                        & Natural Language Processing                             \\
-		BERT                       & Bidirectional Encoder Representations from Transformers \\
-		UMLS                       & Unified Medical Language System                         \\
-		EMR 					   & Electronic Medical Records                              \\
-		EHR						   & Electronic Health Records                               \\
-		MCC                        & Matthews Correlation coefficient                        \\
-		NLI                        & Natural Language Inference                              \\ \hline
-	\end{tabular}
-\end{table}
-
-In more tangible terms, healthcare interoperability at data, process, and knowledge level can be exemplified within the healthcare constraints experienced due to the emergence of Covid 19.
-The operational capabilities of the current healthcare service delivery infrastructure has gone under tremendous stress due to Covid 19.
-World over, large primary healthcare units have managed to create separate units for managing patients, suffering from extreme cases of the novel coronavirus.
-For secondary and tertiary care units, government involvement has become necessary to filter coronavirus patients and adhering to a national pandemic response policy.
-These complex circumstances have enhanced the need for sharing patient data and state-of-the-art medical knowledge in real-time, to provide the medical experts with a tool to make accurate and timely decisions.
-Data interoperability can enable the front line medical workers to fetch, understand, and use patient data, especially comorbidities, across organizational and physical boundaries, without suffering from societal taboos that may prevent the patient from sharing their complete and accurate medical histories.
-Knowledge interoperability can improve the knowledge acquisition and sharing protocols to provide the medical experts such as epidieomologists and vaccinologist, with latest information on affected population trends, disease diagnosis, treatment, and followup procedures, and interpretable decisions leading to positive or negative outcomes.
-Process interoperability can help reduce and in some cases remove the operational redundancies between health centers.
-In this way, successive healthcare treatments can take benefit from earlier diagnosis, treatment, and followup procedures, thereby reducing the stress on healthcare experts and systems.
-Healthcare Standards such as HL7 - Fast Healthcare Interoperability Resources (FHIR), and openEHR provide the foundations for storing and communicating medical data, through the use of well defined protocols.
-While Systematized Nomenclature of Medicine—Clinical Terms (Snomed-CT) \cite{snomedct_url} and Logical Observation Identifiers Names and Codes (LOINC) \cite{loinc} provide a standard definition for clinical terminologies and laboratory tests, respectively.
-Similarly Medical Logic Module (MLM) provides a standardized way for expressing medical knowledge.
-However, the plethora of standards necessitates the creation of bridging standards that can resolve the heterogeniety between the medical standards.
-Substantial effort has gone into this endeavor with the Clinical Information Modeling Initiative (openCIMI) \cite{CIMI2015} taking the lead in bridging the gap between HL7v3 and openEHR.
-Similarly, SNOMED CT and LOINC are working to resolve the redundancies between the two terminological standards since 2013.
-This healthcare interoperability solution follows a formal, albiet long process, which is greatly dependent on the human factor.
-However, the current healthcare scenario requires a quick solution to create a scaffolding of an interoperable bridge between various healthcare providers.
-It is also important to ensure that this scaffolding should be able to support the formal standardization processes of the future.
-In \cite{Satti2020}, we have presented the Ubiquitous Health Platform (UHP), which provides semantic reconciliation-on-read based data curation for resolving data interoperability between various schema.
-This methodology is based on the creation and management of schema maps, that can provide the framework for transforming a source schema into a target schema.
-In the current study, we will present our research work to build and manage the schema map knowledge base.
-Overall, our methodology is based on the creation, evaluation, and application of a novel schema matching technique to identify the relationships between attributes of the participating medical data schema.
-Since the terms used to identify attributes in the data schemas are not defined in any standard way, it is important to first identify the component words of the attribute term and then to append semantic concepts with these to create a meaningful sentence.
-This process is based on word expansion using concept lookup from Unified Medical Language System (UMLS).
-Once the sentence has been created, it is then trivial to create its embedded vectors representation using transformer based pre-trained models.
-The cosine similarity of any two embedded vectors can then indicate the degree of similarity between the original attributes.
-The motivation behind this methodology along with its development and evaluation details will be presented in the following flow:
-
-\begin{itemize}
-	\item[$-$] Section \ref{relatedwork} presents the related work
-	\item[$-$] Section \ref{methodology} contains the details of our methodology
-	\item[$-$] Section \ref{experimentalSetup} provides the experimental setup
-	\item[$-$] Section \ref{results} presents the results
-	\item[$-$] Section \ref{discussion} discusses the challenges and limitations of the presented methodology and its evaluations
-	\item[$-$] Section \ref{conclusion} concludes the paper.
-\end{itemize}
-
-\section{Related Work}
-\label{relatedwork}
-Althubait et al.
-\cite{althubaiti2020combining} proposed an ontology expansion methodology that identifies and extracts new class from text articles using word embedding and machine learning techniques.
-The authors identified the similarity of tokens and phrases of the text articles with the exiting classes of the ontology.
-The target ontology is expanded with classes from text articles having greater similarity with that of already added classes.
-A similar word embedding technique was also used by Nozaki et al.
-\cite{nozaki2019semantic}, where the authors used instance based schema matching technique to identify the semantic similarity between two instances.
-The results of the study showed the possibility of detecting similar string attributes of different schemas.
-Yousfi et al.
-\cite{yousfi2020xmatcher} also utilized semantic base techniques and proposed xMatcher XML schemas matching approach.
-xMatcher transforms schemas into a set of words, followed by measuring words context, and relatedness score using WordNet.
-The terms from different schemas having similarities greater or equal to 0.8 are considered similar.
-Bylygin et al.
-\cite{bulygin2018combining} devised an ontology and schema matching approach by combining lexical and semantic similarity with machine learning approaches.
-The authors used lexical and semantic measures as features and trained various machine learning algorithms including Naive Bayes, logistic regression, and gradient boosted tree.
-The result achieved showed that the combination of algorithms outperformed the single modal.
-
-Martono et al.
-\cite{martono2017review} provided overview of previous studies related to linguistic approaches used for schema matching.
-Linguistic methods focused on finding strings and evaluate there similarity in different schemas.
-The string are normally normalized before to align both the strings before similarity comparison.
-The normalized strings are categories based on the information relatedness and element with similar category are compared using various similarity measure including  Jaro-distance, Lavenstein (edit-distance), and many more.
-Alwan et al.
-\cite{alwan2017survey} have summarized the techniques used in the literature for schemas and instances based schema matching.
-The information used for schema matching is categories into  schema information, instance and auxiliary information.
-Most of the searchers have used syntactic techniques (including n-gram, and regular expression), semantic techniques (including Latent Semantic Analysis, WordNet/Thesaurus and Google Similarity) for schema level and instance level matching to achieve the final goal of data/information interoperability.
-Kersloot et al.
-\cite{kersloot2020natural} performed a comprehensive systematic review to evaluate Natural Language Processing (NLP) algorithms used for clinical text mapping onto ontological concepts.
-The findings of the studies were evaluated with respect to five categories; use of NLP algorithms, data used, validation and evaluation performed, result presentation, and generalization of results.
-The authors revealed that over one-fourth of the NLP algorithms used were not evaluated and have no validation.
-The systems that claimed generalization, were self evaluated and having no external validation.
-
-Xu et al.
-\cite{xu2003discovering} presented a framework for discovering indirect links besides direct links among schema elements.
-The indirect matches were detected for relations such as union, composition, decomposition, selection, and boolean.
-The indirect links are useful to handle concepts merge, split, generalization, and specialization.
-The matching techniques utilized in the study considered terminological relationships (word synonym and hypernym), structural characteristics, data-value characteristics, and expected data values.
-The experimental results revealed framework effectiveness by achieving more than 90\% precision and recall for direct and indirect link matching.
-
-A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al.
-\cite{moll2020oncology} to check their perspectives regarding Patient Accessible Electronic Health Record (PAEHR).
-The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations.
-The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions.
-However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[scale=0.60]{methodology}
-	\caption{Methodology for creating schema maps.}
-	\label{fig:methodology}
-\end{figure*}
-
-\section{Methodology}
-\label{methodology}
-Healthcare interoperability, with a focus on non-standard compliant medical schema is dependent on the generation and validation of schema maps as discussed above.
-To this end, the creation of a cohesive workflow is of utmost importance.
-In our earlier work \cite{Satti2020} we used maximum sequence identification and suffix tress based matching for syntactic matching of two distinct data schemas.
-This was followed by semantic concept enrichment and subsequently concept matching for creating rules in the form of schema maps.
-The simplified mapping functions, thereby created, provided a simple methodology for converting semi-structured medical data into an interpretable model form.
-In our current methodology as visualized in Figure \ref{methodology}, we have utilized state-of-the-art natural language processing (NLP) techniques to extract the schema mapping rules from semi-structured data schemas.
-This methodology is based on identifying similarity between vector representations of two attributes, belonging to different medical schemas.
-Traditional NLP techniques such as Word2Vec are able to convert a word into an embedded vector, while Bidirectional Encoder Representations from Transformers (BERT) extracts an embedded vector from a sentence \cite{zhu2018exploring}.
-However, the terms forming the attribute names are bigger than a word (combination of multiple words) and smaller than a sentence.
-In order to resolve this problem, we extracted the set of suffixes from the terms forming the attribute names.
-The bidirectional nature of BERT, allows the creation of contextual embedded vectors, where each target word is affected by its neighboring words.
-Hence to convert the set of suffixes into a sentence, we collected the set of concepts corresponding to each suffix, from UMLS.
-This operation has two effects, firstly it is used to remove any suffix, which does not have a corresponding concept and secondly the extracted concepts are used to add context to each suffix and produce a contextual sentence.
-The following subsections provide the practical details for our methodology from schema acquisition to attribute name expansion, and finally schema map generation.
-
-\subsection{Schema acquisition}
-\label{schema_acq}
-In the first step of our semantic reconciliation methodology, we simulate medical data acquisition from five distinct Electronic Medical Records (EMR) storage systems ($S$).
-These include patient reports from OpenEMR ($s_1$), 100,000 patient records from EMRBOTS ($s_2$) \cite{kartoun2016methodology}, custom database design by Pan et.
-al($s_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($s_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($s_5$) \ref{ali2017reconciliation}.
-Each of these medical systems as shown in \ref{fig:schema}, follows the relational database design with logical entities such as demographics, diagnosis, medicine or others, placed into tables which can be further linked to one or more tables.
-While the database design implemented by each of these systems, fulfills the need of their respective information processing applications, the lack of interoperability, in terms of identifying similar attributes or exchanging the medical data is very much evident here.
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[scale=0.53]{schemas}
-	\caption{The five medical schemas used for achieving data interoperability.}
-	\label{fig:schema}
-\end{figure*}
-
-A similar notion of data heterogeneity, in terms of medical data schema is evident across the healthcare domain.
-This is caused by various factors, including the lack of one all-encompassing, and universally applicable terminological standard and different normalization level for representing attributes.\\
-In the former case, while SNOMED-CT provides a mechanism for identifying the standard codes for clinical terms and LOINC can be used for laboratory related terms, most attribute names are created based on the gut feeling of the database designer.
-Additionally, while these codes can be used to represent data instances, the data schema, achieves no benefit from the same.
-Consider the terms ``name'' and ``patientName'', which refer to the same attribute of the patient entity.
-However, since there is no standard way to represent this attribute, both are considered correct ($s_1$ and $s_3$ use the former representation, while $s_2$ and $s_5$ use the latter).\\
-In the later case, differences in normalization cause semantic differences, due to which some data could be available in one schema but absent in others such as OpenEMR demographics identifying the patient's residential location using specific attributes like ``Address'', ``City'', ``State'', ``Postal Code'', ``Country'', and others.
-Similarly, ``EncounterDate'' from $s_5$ is semantically similar to ``BeginDate'' of ``openemr\_MedicalProblems'' table in $s_1$, ``AdmissionStartDate'' of ``LabsCorePopulatedTable'' in $s_2$,
-``time'' in ``Diagnosis'' table of $s_3$, and  ``dateOfAdmission'' in ``Diagnosis'' and ``CareHistory'' tables of $s_4$.
-Finally, $s_1$ and $s_3$ have separate tables containing the medicinal prescription details, however the same details are unavailable in $s_2$, $s_4$, and $s_5$.
-Once again, this is not an incorrect behavior since this information, might not be a part of the context or the requirements for the EMR/EHR storage systems.
-In fact, the change in context of the medical data storage system from the initial time of development to a later stage of collaborative processing systems, is the main cause of heterogeneity.
-In order to provide an interoperable solution, it is therefore necessary to enhance the semantics of each data attribute by its contextually equivalent sentence.
-
-\subsection{Attribute to Sentence Transformation}
-\label{schema_prepro}
-In order to process the EMR/EHR schema set $S$ and produce a set of corresponding semantically enriched sentences, we use the data representation $s_i$, generated through the process explained in sequence acquisition to collect the various medical fragments in memory.
-We then iterate over these fragments, building a set of attributes, distinguished by their name, schema's name, table's name, schema's version, source, and recorded data.
-This entails that ``PatientID'' from each of the four tables in $s_2$, and ``patientID'' from five tables in $s_4$, would result into nine attributes (assuming, as in the current case of no differences in versions of these systems).
-For each attribute, we then generate the suffix array, which provides all possible substring representations contained within the attribute name.
-In order to generate the set of suffixes, we employ three strategies, forward suffix generation, whereby for a word $w$ of length $n$, $n-1$ suffixes of size 2 to $n-1$ are produced, backward suffix generation, to produce $n-1$ suffixes in reverse order with size $n-1$ to 2, and regular expression based suffix generation, which splits each word on, change of case, special characters(such as -, \_, !, and others), and numbers.
-In this way a large list of suffixes is generated, which is combined using a ``TreeSet'' data structure of Java, which internally sorts this list as well.
-An example of this suffix generation process, using the attribute name ``dateOfAdmission'' as it appears in $s_4$ is shown in Figure \ref{fig:suffix_attribute}.
-
-\begin{figure}[tb!]
-	\centering
-	\includegraphics[scale=0.65]{suffixAttribute}
-	\caption{An example of suffix arrays produced for the attribute ``dateOfAdmission''.}
-	\label{fig:suffix_attribute}
-\end{figure}
-
-Suffix strings for similar attributes such as ``AdmissionStartDate''.
-``diseaseNameOnAdmission'', and ``AdmissionEndDate'' appear in $s_2$, produce many, synctactically similar suffixes, to the presented example.
-This process, is only able to generate syntactic suffixes, producing many incoherent and unrelated suffixes.
-In order to counter this problem, and to limit the list of suffixes within the domain, we then query UMLS with exact search strategy, looking for the existence of any concepts against each suffix.
-In case, no semantic concept is found for a particular suffix, it is removed from the final Suffix Array.
-On the other hand, if atleast one semantic concept is found against the queried suffix, it is retained.
-Meanwhile the process continues for the next attribute, then the next table, and finally the next system, till no further processing is possible.
-The set of suffixes and their corresponding concepts are then used to build the sentence, where by each concept corresponding to a suffix is appended next to the suffix.
-An example of the resultant sentence for the attribute ``DateOfAdmission'' is shown in Table \ref{tab:sentence_example}.
-
-\begin{table}[]
-	\centering
-	\caption{Sentence created from the attribute name ``DateOfAdmission''}
-	\label{tab:sentence_example}
-	\begin{tabular}{|p{\linewidth}|}
-		\hline
-		Date Value type - Date date allergenic extract Date in time Data types - Date Date Fruit;Of SPI1 wt Allele SPI1 gene TAF1 wt Allele BRIP1 gene Within Degrees fahrenheit Oral contraception BRIP1 wt Allele;Da Displacement of abomasum dalton Anterior descending branch of left coronary artery deca units cytarabine/daunorubicin protocol Dai Chinese Asymptomatic diagnosis of Drug Accountability Domain;ion Iontophoresis Route of Drug Administration Ions;on SPARC wt Allele Osteonectin SPARC gene On (qualifier value) Upon - dosing instruction fragment;Admission Admission activity Hospital admission;Dat SLC6A3 gene SLC6A3 wt Allele dopamine transporter Direct Coombs test SLC6A3 protein, human Test Date cytarabine/daunorubicin/thioguanine Alzheimer's Disease;mission Religious Missions;\\
-		\hline
-	\end{tabular}
-\end{table}
-
-Here the various suffixes and their concepts are separated by the symbol ``;'', however together they form one sentence, for which an embedded vector is generated.
-
-\subsection{Schema Map generation}
-\label{schema_map_gen}
-
-Schema Maps provide an interoperable bridge between two medical systems ($s_i \wedge s_j$), by identifying the semantic relationship between their participating attributes.
-This identification is based on the similarity between the embedded vectors, of the semantically enriched sentences corresponding to each data attribute.
-While the embedded vectors can be generated using any methodology, we tested 11 methodologies with Word2Vec and 10 models based on BERT (including BERT base, BERT large, distilBert, and RoBERTa) further detailed in section \ref{experimentalSetup}, the large/STSb version of RoBERTa\cite{reimers-2019-sentence-bert}, provides the best results.
-The pair of embedded vectors thus produced are then used to calculate cosine similarity, which is based on the inverse cosine distance between them.
-For our classification, we used the raw results (unnormalized) of cosine similarity, which produces a score between -1, and 1.
-Cosine similarity score of 0 indicates orthogonal relationship between the two vectors, which in our scenario indicates that the two sentences, and by extension their attributes are not related to each other.
--1 indicates inverse relationship between the attributes, while 1 indicates the two attributes are very much the same.
-For producing our schema maps, we are interested in three types of relationships, ``equal'' (the two attributes are same), ``related'' (the two attributes are related to each other), and ``unrelated'' (no relationship between the attributes).
-In order to classify the similarity results into one of these three classes, we then calculated the best thresholds using Matthews Correlation coefficient (MCC) \cite{chicco2020advantages} for classifying each instance as ``equal'', ``related'', and ``unrelated''.
-
-\begin{equation}
-\resizebox{0.9\hsize}{!}{$%
-	MCC = \frac{(TP.FN) - (FP.FN)}{\sqrt{(TP+FP)(TP+FN)(TN+FP)(TN+FN)}}\longrightarrow [-1,1]
-	$%
-}%
-\end{equation}
-MCC provides a fair measure of the ability with which a classifier can correctly predict both positive and negative instances \cite{chicco2020advantages}.
-MCC score of 0 represents random classification, however, with an increase in the number of true positives and true negatives MCC moves closer to 1.
-It also takes into account the false positives and false negatives, which shift the mcc score towards -1.
-This measurement is markedly different from accuracy that fails to account for imbalanced datasets and $F_1$ measure which is not affected by the true negative scores.
-As a result, MCC provides an acceptable alternate in our current scenario comprising of imbalanced dataset (largely in favour of class ``unrelated'') to measuring the true performance of the models, used for threshold selection and model evaluation.
-Finally on a test dataset we evaluated our multi-class classification approach using MCC and Cohen's Kappa coefficient ($\kappa$) \cite{gwet2014handbook} to identify the relationships between each pair of attributes.
-
-\section{Experimental Setup}
-\label{experimentalSetup}
-In our earlier work \cite{Satti2020} $s_1$, $s_2$, and $s_5$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS).
-We extended the same setup to create an additional 100,000 records, for 1000 patients with 3 medical fragments for $s_1$, $s_2$, and $s_4$, and 97 randomly selected and generated medical fragments amongst $s_1$, $s_2$, $s_3$, $s_4$ and $s_5$.
-These fragments follow various design elements supporting a variety of valid relational storage architectures.
-Such as, $s_1$, $s_2$ and $s_4$ are represented by creating a separate medical fragment for each participating table, $s_3$ utilizes its medical fragment to generate a linked record (from a linked object graph), where by the attributes can refer to other objects besides the elements of $t$, mimicking the application of explicit foreign keys, and $s_5$ is a flat table structure.
-The code to generate this data set is available at ``uhp\_map\_generation''\footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhpr\_storage}.
-This application produces three custom formatted files containing an index for patients, an index for their medical fragments, and the medical fragment corresponding to the EMR data.
-Using the medical fragments file, we then generate the semantically enriched attribute \footnote{https://github.com/desertzebra/UHP\_v4/tree/main/uhp\_map\_generation}, which contains the suffixes and their concepts corresponding to each EMR data attribute.
-The resulting set of enriched attributes are temporarily stored in a JSON file, which is then read by the same application to partially generate the schema maps.
-This process is used to create 20,349 distinct pairs of attributes across $s$.
-Each pair also contains the ``relationshipList'', which stores the results of fuzzy string matching\cite{FuzzyWuzzy} \footnote{Java Library: https://github.com/xdrop/fuzzywuzzy} between the attribute names.
-The JSON file thus produced is then used by a python script to generate the semantically enriched sentences and their embedded vectors using Word2Vec, and 10 pre-trained BERT NLI models \cite{reimers-2019-sentence-bert}.
-The BERT models include ``bert-base-nli-stsb-mean-tokens'', ``bert-large-nli-stsb-mean-tokens'', ``roberta-base-nli-stsb-mean-tokens'', ``roberta-large-nli-stsb-mean-tokens'', ``distilbert-base-nli-stsb-mean-tokens'', ``bert-base-nli-mean-tokens'', ``bert-large-nli-mean-tokens'', ``roberta-base-nli-mean-tokens'', ``roberta-large-nli-mean-tokens'', and ``distilbert-base-nli-mean-tokens''.
-The embedding vectors are then compared using cosine similarity, which produces a score between -1 and 1.
-The rationale behind switching the applications at various stages is to cache the results and create checkpoints for restarting any failed stages, easily.
-Additionally, since python provides better support for easy generation of embedding vectors, it was thus preferred over the Java based implementation, which is otherwise very beneficial for other tools.
-%These applications were executed on a workstation running Ubuntu 20.04.2 on top of AMD Ryzen 3 2200G, and 32GB ram.%
-
-\section{Results}
-\label{results}
-
-The validity of our proposed approach has been evaluated using several techniques including comparison of the proposed semantic matching process with fuzzy string matching, embedded vector generation and comparison using Word2Vec, and 10 BERT nli models.
-
-\begin{figure}[htb!]
-	\centering
-	\includegraphics[width=\columnwidth]{kappaInterAnnotatorAgrement}
-	\caption{Cohen's Kappa ($\kappa$) score among the four annotators}
-	\label{fig:kappaInterAnnotatorAgrement}
-\end{figure}
-
-\subsection{Dataset Annotation}
-In order to compare our computed models with ground truth and to identify the best thresholds for classifying each instance as ``equal'', ``related'', or ``unrelated'' 4 human annotators were utilized to anonymously, score the similarity of each pair of attribute names.
-In order to support this process, we first repurposed one of our generated data matrix by marking all attribute pairs belonging to the same schema with the symbol ``-''.
-Following this, the annotators marked each cell corresponding to a pair of attributes (conversely, each attribute pair corresponds to two cells with the positioning of the pair-participants swapped; which is used for clarity and identify correct relationships between the attribute on left and attribute on right), by determining the similarity in terms of dissimilar as ``0'', exactly similar as ``1'', row attribute as child of column attribute as ``<'', row attribute as a parent of the column attribute as ``>'', and finally, unknown as ``~''.
-The data sheets generated after this extensive human effort have been made available for other researchers\footnote{\url{https://github.com/desertzebra/EMR-Interoperability/tree/master/Implemenation/Data/Annotated}}.
-
-\begin{table*}
-	\centering
-	\caption{Annotations performed by the four annotators on five medical schema}
-	\label{tab:annotator_marking}
-	\begin{tabular}{|l|l|l|l|l|l|}
-		\hline
-		Method     & Total Matches & Marked as Equal & Marked as Related & Marked as Unrelated & Not Marked \\ \hline
-		Annotator1 & 40698         & 238             & 109               & 40351               & 0          \\
-		Annotator2 & 40698         & 241             & 116               & 40341               & 0          \\
-		Annotator3 & 40698         & 260             & 2103              & 38182               & 153        \\
-		Annotator4 & 40698         & 225             & 62                & 40400               & 11         \\ \hline
-	\end{tabular}
-\end{table*}
-
-These sheets, additionally contain some missing values, which were left out by the annotators but in order to maintain their originality, these values were not filled; instead during our evaluation for these datasets, the missing values were considered as having the score ``0''.
-Using $\kappa$, we evaluated the inter-rater agreement of these annotations, which have been visualized in Figure \ref{fig:kappaInterAnnotatorAgrement}.
-It can be seen in this plot, that ``Annotator3'' has very small correlation with the other 3 annotators.
-This difference can be traced back to the number and type of annotations performed by each annotator, which is shown in Table \ref{tab:annotator_marking}.
-The ``Annotator3'' has marked 2103 cells as related (one of >, < , or ~) and left 153 as empty.
-However, even in the presence of these difference, it is pertinent to include the data for all annotators in order to avoid any biasedness.
-
-This annotated data was then processed to replace all related entries with ``0.5'' ($class_{0.5}$) and all ``-'' with ``0'' ($class_{0}$), while the values for similar at ``1'' ($class_{1}$) and ``0'' ($class_{0}$) for dissimilar were kept the same.
-This conversion was then used to produce a consolidated dataset of 40,698 attribute pairs using mode scores of all annotators for each cell.
-We also tested average scores between the annotators, but that would produce scores between ``0'', ``0.5'', and ``1'', greatly increasing the number of classes for classification.
-Hence the maximum agreement between the annotators maintains the final label values within these three classes, which become easier to evaluate.
-Additionally, the original dataset and its mode consolidated form is biased in favour of class ''0'', since most attribute pairs are not related to each other.
-This dataset is then split into development and testing partitions with a ratio of 70:30.
-The development partition is used for threshold selection based on the best MCC score for identifying class ``equal'', followed by best scores for class ``related'' and finally best of class ''unrelated''.
-The optimal threshold thus achieved is used to classify the instances of the test dataset, which is finally evaluated on its MCC and $F_1$ measure.
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[scale=0.83]{thresholdSelection}
-	\caption{Thresholds selection using MCC scores where t1 indicates the similarity threshold between $class_0$ and $class_{0.5}$, and t2 indicate the similarity threshold between $class_{0.5}$ and $class_1$.}
-	\label{fig:thresholdSelection}
-\end{figure*}
-
-\subsection{Threshold Selection}
-A good text classification methodology is dependent on the correct choice of a threshold, which can maximize the target class participation.
-In case of independent labels, area under the precision recall curve can provide this optimal measure, however as in our case, for dependent classes on a biased dataset the MCC, is better\cite{chicco2020advantages}.
-Since our aim is to apply an optimal text similarity classifier to resolve this multi-class problem ($class_0$, $class_{0.5}$, and $class_1$), we have to test various threshold scores for separating the instances between $class_0$ and $class_{0.5}$ ($t_1$), and then $class_{0.5}$ and $class_1$ ($t_2$).
-Additionally, since our aim is to correctly identify the similar attribute instances, it is pertinent to maximize the classification performance of $class_1$ (similar), followed by $class_{0.5}$ (related), and finally $class_0$ (unrelated).
-With a step size of \textit{0.05} ($step$), and starting from $t_1$ as 0.0 and $t_2$ as $t_1$ + $step$, we move the thresholds until $t_2$ reaches \textit{1.0}, followed by increase in $t_1$ by step size.
-Eventually, $t_1$, reaches \textit{0.95} and $t_2$ reaches \textit{1.0}, at which point, the process stops.
-This is to ensure that $t_1$ remains behind $t_2$, for all iterations, measuring MCC score, for the 12 models.
-These models include, ``Fuzzy\_Wuzzy'', ``Word2Vec'', and 10 BERT based models.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-\begin{table*}[h!]
-	\centering
-	\caption{Performance matrix for individual classes using one vs all binarization technique}
-	\label{tab:evaluations}
-	\begin{tabular}{|c|c|c|l|l|l|l|l|}
-		\hline
-		\textbf{Model}                                        & \textbf{Class Positive} & \textbf{Class Negative} & \multicolumn{1}{c|}{\textbf{Accuracy}} & \multicolumn{1}{c|}{\textbf{Precision}} & \multicolumn{1}{c|}{\textbf{Recall}} & \multicolumn{1}{c|}{\textbf{F-1}} & \multicolumn{1}{c|}{\textbf{MCC}} \\ \hline
-		\multirow{3}{*}{FUZZY\_MATCH}                         & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.98                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.98                                   & 0.20                                    & 0.59                                 & 0.29                              & 0.33                              \\ \hline
-		\multirow{3}{*}{Word2Vec}                             & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.24                                   & 0.99                                    & 0.24                                 & 0.38                              & 0.01                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.15                                    & 0.10                                 & 0.12                              & 0.12                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.35                                   & 0.01                                    & \textbf{0.84}                        & 0.01                              & 0.03                              \\ \hline
-		\multirow{3}{*}{bert-base-nli-stsb-mean-tokens}       & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.37                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.22                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
-		\multirow{3}{*}{bert-large-nli-stsb-mean-tokens}      & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.51                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.41                                    & 0.50                                 & 0.45                              & 0.45                              \\ \hline
-		\multirow{3}{*}{roberta-base-nli-stsb-mean-tokens}    & $class_0$                    & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 1.00                              & 0.40                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                & 0.99                                   & 0.26                                    & 0.50                                 & 0.34                              & 0.36                              \\ \hline
-		\multirow{3}{*}{roberta-large-nli-stsb-mean-tokens}   & $class_0$                     & $class_{0.5}$,$class_1$                   & 1.00                                   & 1.00                                    & 1.00                                 & 1.00                              & 0.61                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                & \textbf{1.00}                          & \textbf{0.59}                           & 0.50                                 & \textbf{0.54}                     & \textbf{0.54}                     \\ \hline
-		\multirow{3}{*}{distilbert-base-nli-stsb-mean-tokens} & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.38                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.23                                    & 0.50                                 & 0.32                              & 0.33                              \\ \hline
-		\multirow{3}{*}{bert-base-nli-mean-tokens}            & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.35                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.99                                   & 0.20                                    & 0.50                                 & 0.29                              & 0.31                              \\ \hline
-		\multirow{3}{*}{bert-large-nli-mean-tokens}           & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.28                                   & 1.00                                    & 0.27                                 & 0.43                              & 0.05                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 0.99                                   & 0.34                                    & 0.90                                 & 0.49                              & 0.55                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.57                                   & 0.00                                    & 0.50                                 & 0.01                              & 0.01                              \\ \hline
-		\multirow{3}{*}{roberta-base-nli-mean-tokens}         & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.96                                   & 1.00                                    & 0.97                                 & 0.98                              & 0.23                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                 & 0.96                                   & 0.08                                    & 0.50                                 & 0.13                              & 0.19                              \\ \hline
-		\multirow{3}{*}{roberta-large-nli-mean-tokens}        & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.39                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$                & 0.99                                   & 0.20                                    & 0.50                                 & 0.28                              & 0.31                              \\ \hline
-		\multirow{3}{*}{distilbert-base-nli-mean-tokens}      & $class_0$                     & $class_{0.5}$,$class_1$                   & 0.99                                   & 1.00                                    & 0.99                                 & 0.99                              & 0.36                              \\ \cline{2-8}
-		& $class_{0.5}$                     & $class_0$,$class_1$                   & 1.00                                   & 0.00                                    & 0.00                                 & 0.00                              & 0.00                              \\ \cline{2-8}
-		& $class_1$                       & $class_0$,$class_{0.5}$           & 0.99                                   & 0.21                                    & 0.50                                 & 0.30                              & 0.32                              \\ \hline
-	\end{tabular}
-\end{table*}
-
-Threshold values for Word2Vec are placed at the lower end of the spectrum indicating a very large number of instances are classified as similar (above similarity score of \textit{0.1}), while a small number of instances (with similarity score \textit{0.05}) are classified as dissimilar.
-Similarly, the $class_{0.5}$ lies within the similarity threshold of \textit{0.05} similarity points.
-It can be observed that the threshold for selecting the related class is within \textit{0.05} points, in all except one case (bert-large-nli-mean-tokens where the difference is \textit{0.15} points).
-Five BERT based models, trained on the STSb dataset, all have minimum threshold values of \textit{0.85} and maximum of \textit{0.9}, while the 4 remaining BERT models, lie between \textit{0.9} and \textit{0.95}.
-These results show a general trend of how the cosine similarity varies/maintains itself, against embedded vectors generated from various pre-trained models.
-In absolute terms, however these threshold values provide the mechanism for classifying the test dataset, which is evaluated for performance in the next subsection.
-
-\subsection{Model Evaluation}
-On unseen test dataset with thresholds selected in the previous step and the 12 models, we measured the performance score using one vs all binarization of the multi-classes.
-As evident in Table \ref{tab:evaluations}, very high values of accuracy are visible across all models with all three positive classes.
-In all, except the case of Word2Vec, Precision and recall also show values close to \textit{1.0}.
-However, these measures are very misleading, since the dataset is greatly biased in favour of $class_0$.
-In terms of $F_1$ measure $class_{0.5}$ shows the worst possible results, independently, with all except Word2Vec and bert-large-nli-mean-tokens having a score of \textit{0.0}.
-Bert-large-nli-mean-tokens provides the best $F_1$ measure at \textit{0.49}.
-These metrics are thus not useful to gauge the performance of the evaluated models.
-Instead, focusing on the MCC score, provides a good picture of the model performance for individual classes when all other instances are negative.
-
-Finally, we evaluated the overall $\kappa$ coefficient and MCC score to evaluate the performance of each model on the test dataset.
-These scores range between [-1,1], providing a measure quantifying the accuracy of the classifier to correctly predict correct and incorrect instances.
-The models Word2Vec, bert-large-nli-mean-tokens, and roberta-base-nli-mean-tokens, with values between [0,0.20] indicate random classification, while $\kappa$ score between [0.21,0.39], achieved by fuzzy wuzzy, bert-base-nli-mean-tokens, roberta-base-nli-sts-mean-tokens, distilbert-base-nli-stsb-mean-tokens, bert-base-nli-mean-tokens, roberta-large-nli-mean-tokens, and distilbert-base-nli-mean-tokens, show only minimal agreement with the annotated data \cite{mchugh2012interrater}.
-Relative best rates, in this case, are achieved by roberta-large-nli-stsb-mean-tokens, which substantially surpasses the other models, however in absolute terms, it shows only weak agreement.
-Similarly, MCC scores show a similar result, with roberta-large-nli-stsb-mean-tokens, achieving the relative best performance amongst all classifiers.
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[scale=0.83]{evaluation}
-	\caption{Performance evaluation of various models using MCC and kappa ($\kappa$) scores.}
-	\label{fig:evaluation}
-\end{figure*}
-
-\section{Discussion}
-\label{discussion}
-In text classification, production and use of a well annotated corpus for supervised and semi-supervised learning is of utmost importance.
-The same is also useful for evaluating the performance of unsupervised learning techniques.
-However, in the real world the production and maintenance of these corpora is an expensive task, often requiring extensive human effort.
-While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively provide a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}.
-This is also evident in the case of our annotated dataset, whereby the instances have been labeled by four human experts (two medical practioners and two computer science graduates), using their subjective knowledge.
-One example of this subjective classification, is evident in the raw form of the data instances labeled by ``Annotator3''.
-According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child.
-While the selection of this label can be debated from an subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}.
-As a result, the annotations were kept anonymous so as not to induce any bias.
-Thus, the complete annotated data in its original form became the basis of our threshold selection and model evaluation methodology.
-A mode based voting mechanism was then used to resolve the differences between the annotators.
-The consolidated true dataset was then formed based on the agreed upon label by atleast 3 annotators.
-As pointed out in \cite{reidsma2008exploiting}, the net effect of such a voting mechanism is an increase in the precision of the machine learning classifiers in lieu of, their accuracy.
-However, as shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC.
-The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextful and relative manner.
-
-Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the nature of the dataset.
-Even before annotation, the dataset is bias in favour of unrelated attributes.
-As established by the human experts and the machine learning model, for 254 attributes involved in 40698 possible pairs only a little over 300 similar instances are found.
-In these circumstances performance metrics, such as accuracy, precision, and recall are meaningless.
-These metrics are unable to account for the imbalanced datasets and provide an incorrect view of the classifier's accuracy.
-Instead metrics such as $F_1$, MCC, and $\kappa$ can provide a true picture of the classifier's accuracy.
-These metrics are also well suited for evaluating multi-class classifiers, using one vs all or one vs one binarizations of the dataset, as well as consolidating the results into a single measure.
-In our experimentation, we also evaluated the Area Under the Receiver Operating Characteristic (AUROC) curve and Area Under the Precision Recall (AUPR) curve, as a threshold selection metric.
-However these graphs are well suited for independent classes as shown in \cite{espindola2005extending}, and in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$).
-AUROC and AUPR were thus replaced with our current approach for threshold selection.
-The benefit of using this kind of dependent classification is its usefulness in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.
-
-\section{Conclusion}
-\label{conclusion}
-Healthcare information systems are slowly moving towards a standardized approach, whereby the storage, exchange, and usage of health data, information, and knowledge is becoming interoperable.
-However, research and development of ubiquitous health management systems, still require manual interventions by human experts.
-These approaches require costly resource allocations, which is not possible for small and medium scaled healthcare service providers.
-In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques.
-Using transformer based pre-trained BERT models, we show the applicability of these techniques on creating the, as yet non-validated, schema maps.
-Resultantly, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
-In future, we shall look towards developing a mechanism for schema map storage and evolution, along with expert validation to finally close this loop.
-We shall also work on re-training some of the existing pre-trained models, to improve the performance of schema map creation.
-
-\section*{Acknowledgment}
-This research was supported by the MSIT(Ministry of Science and ICT), Korea, under the ITRC(Information Technology Research Center) support program(IITP-2017-0-01629) supervised by the IITP(Institute for Information \& communications Technology Promotion), IITP-2017-0-00655, NRF-2016K1A3A7A03951968, and NRF-2019R1A2C2090504.
-
-\bibliographystyle{unsrt}
-\bibliography{references}
-
 % orcid: 0000-0002-9883-3355

### 2021-08-04 ManuScript/IEEEAccess/Revision 1/final/ManuScript.tex

--- 2021-07-25 ManuScript/IEEEAccess/Revision 1/source/ManuScript.tex
@@
 \begin{abstract}
-Data, information, and knowledge processing systems, in the domain of healthcare are currently plagued by the heterogeneity at various levels.
-Current solutions, have focused on developing a standard based, manual intervention mechanism, which requires a large amount of human resource and necessitate realignment of existing systems.
-State-of-the-art methodologies in the field of natural language processing and machine learning, can help to partially automate this process, reducing the resource requirements and providing a relatively good multi-class based classification algorithm.
-We present a novel methodology for bridging the gap between various healthcare data management solutions by leveraging the strength of transformer based machine learning models, to create mappings between the data elements.
+Data, information, and knowledge processing systems, in the domain of healthcare, are currently plagued by heterogeneity at various levels.
+Current solutions have focused on developing a standard-based, manual intervention mechanism, which requires a large number of human resources and necessitates the realignment of existing systems.
+State-of-the-art methodologies in the field of natural language processing and machine learning can help to partially automate this process, reducing the resource requirements and providing a relatively good multi-class-based classification algorithm.
+We present a novel methodology for bridging the gap between various healthcare data management solutions by leveraging the strength of transformer-based machine learning models, to create mappings between the data elements.
 Additionally, the annotated data, collected against five medical schemas and labeled by four annotators is made available for helping future researchers.
-Our results indicate, that for biased, dependent multi-class text classification, transformer based models provide better results than linguistic and other classical models.
-In particular, the Robustly Optimized BERT Pretraining Approach (RoBERTa) provides the best schema matching performance by achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
+Our results indicate, that for biased, dependent multi-class text classification, transformer-based models provide better results than linguistic and other classical models.
+In particular, the Robustly Optimized BERT Pretraining Approach (RoBERTa) provides the best schema matching performance by achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human-annotated data.
 \end{abstract}
@@
 	\centering
-	\includegraphics[scale=0.60]{methodology}
+	\includegraphics[scale=0.60]{methodology_final}
 	\caption{Methodology for creating schema maps.}
@@
 	\centering
-	\includegraphics[scale=0.53]{schemas}
+	\includegraphics[scale=0.53]{schemas_final}
 	\caption{The five medical schemas used for achieving data interoperability.}
@@
 	\centering
-	\includegraphics[scale=0.65]{suffixAttribute}
+	\includegraphics[scale=0.65]{suffixAttribute_final}
 	\caption{An example of suffix arrays produced for the attribute ``dateOfAdmission''.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{kappaInterAnnotatorAgrement}
+	\includegraphics[width=\columnwidth]{kappaInterAnnotatorAgrement_final}
 	\caption{Cohen's Kappa ($\kappa$) score among the four annotators}
@@
 	\centering
-	\includegraphics[scale=0.83]{thresholdSelection}
+	\includegraphics[scale=0.83]{thresholdSelection_final}
 	\caption{Thresholds selection using MCC scores where t1 indicates the similarity threshold between $class_0$ and $class_{0.5}$, and t2 indicate the similarity threshold between $class_{0.5}$ and $class_1$.}
@@
 	\centering
-	\includegraphics[scale=0.83]{evaluation}
+	\includegraphics[scale=0.83]{evaluation_final}
 	\caption{Performance evaluation of various models using MCC and kappa ($\kappa$) scores.}
@@
 The same is also useful for evaluating the performance of unsupervised learning techniques.
-However, in the real world the production and maintenance of these corpora is an expensive task, often requiring extensive human effort.
-While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively provide a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}.
-This is also evident in the case of our annotated dataset, whereby the instances have been labeled by four human experts (two medical practioners and two computer science graduates), using their subjective knowledge.
+In the real world, the production and maintenance of these corpora is an expensive task, often requiring extensive human effort and conformance to ethical principles, which can restrict access to critical data for the researchers.
+While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively assign a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}.
+Data validity is especially important in the domain of healthcare, where the acquisition, curation, and sharing processes are all encapsulated by the need to ensure correctness as well as privacy and security of the user.
+Consequently, the availability of healthcare data, its accuracy, and transparency are major concerns for most researchers associated with this domain \cite{Joshi2018}.
+It is not only important to access the data but also to understand how it was produced, the caveats associated with it, and any assumptions made during or after its acquisition.
+In the case of our annotated dataset, the instances have been labeled by four human experts (two medical practitioners and two computer science graduates), using their subjective knowledge.
 One example of this subjective classification, is evident in the raw form of the data instances labeled by ``Annotator3''.
 According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child.
-While the selection of this label can be debated from an subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}.
+While the selection of this label can be debated from a subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}.
 As a result, the annotations were kept anonymous so as not to induce any bias.
@@
 As shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC.
-The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextful and relative manner.
+The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextual and relative manner.
 
-Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the nature of the dataset.
+Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the dataset's nature.
 Even before annotation, the dataset is bias in favour of unrelated attributes.
@@
 
-\textbf{Transparency}
-Through this research we aim to bridge the gap between healthcare schema, which is imperative for providing the medical experts with a complete picture of the patient's health record.
-
-A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al.
-\cite{moll2020oncology} to check their perspectives regarding Patient Accessible Electronic Health Record (PAEHR).
-The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations.
-The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions.
-However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.
-
 \section{Conclusion}
@@
 However, research and development of ubiquitous health management systems, still require manual interventions by human experts.
-These approaches require costly resource allocations, which is not possible for small and medium scaled healthcare service providers.
+These approaches require costly resource allocations, which are not possible for small and medium scaled healthcare service providers.
 In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques.
 Using transformer based pre-trained BERT models, we show the applicability of these techniques on creating the, as yet non-validated, schema maps.
-Resultantly, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
+As a result, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
 In future, we shall look towards developing a mechanism for schema map storage and evolution, along with expert validation to finally close this loop.
@@
 \section*{Acknowledgment}
-This research was supported by the MSIT(Ministry of Science and ICT), Korea, under the ITRC(Information Technology Research Center) support program(IITP-2017-0-01629) supervised by the IITP(Institute for Information \& communications Technology Promotion), IITP-2017-0-00655, NRF-2016K1A3A7A03951968, and NRF-2019R1A2C2090504.
+This research was supported by ITRC(Information Technology Research Center) support program(IITP-2017-0-01629), Grand Information Technology Research Center support program(IITP-2021-2020-0-01489), and IITP-2017-0-00655 supervised by IITP(Institute of Information \& communications Technology Planning \& Evaluation), and National Research Foundation of Korea(NRF) NRF-2019R1A2C2090504 funded by the Korea government(MSIT).
 
-\bibliographystyle{unsrt}
-\bibliography{references}
+\begin{thebibliography}{10}
+
+	\bibitem{geraci1991ieee}
+	Anne Geraci, Freny Katki, Louise McMonegal, Bennett Meyer, John Lane, Paul
+	Wilson, Jane Radatz, Mary Yee, Hugh Porteous, and Fredrick Springsteel.
+	\newblock {\em IEEE standard computer dictionary: Compilation of IEEE standard
+		computer glossaries}.
+	\newblock IEEE Press, 1991.
+
+	\bibitem{Himss_url2013}
+	{Healthcare Information and Management Systems Society}.
+	\newblock {Definition of Interoperability}, 2013.
+
+	\bibitem{khan2013process}
+	Wajahat~Ali Khan, Maqbool Hussain, Khalid Latif, Muhammad Afzal, Farooq Ahmad,
+	and Sungyoung Lee.
+	\newblock Process interoperability in healthcare systems with dynamic semantic
+	web services.
+	\newblock {\em Computing}, 95(9):837--862, 2013.
+
+	\bibitem{ali2017multi}
+	Taqdir Ali, Maqbool Hussain, Wajahat~Ali Khan, Muhammad Afzal, Jamil Hussain,
+	Rahman Ali, Waseem Hassan, Arif Jamshed, Byeong~Ho Kang, and Sungyoung Lee.
+	\newblock Multi-model-based interactive authoring environment for creating
+	shareable medical knowledge.
+	\newblock {\em Computer Methods and Programs in Biomedicine}, 150:41--72, 2017.
+
+	\bibitem{snomedct_url}
+	{SNOMED Clinical Terminologies}.
+
+	\bibitem{loinc}
+	{LOINC}.
+
+	\bibitem{mohammed2010ubiquitous}
+	Sabah Mohammed and Jinan Fiaidhi.
+	\newblock {\em Ubiquitous Health and Medical Informatics: The Ubiquity 2.0
+		Trend and Beyond: The Ubiquity 2.0 Trend and Beyond}.
+	\newblock IGI Global, 2010.
+
+	\bibitem{CIMI2015}
+	David Johnson.
+	\newblock {Clinical Information Modeling Initiative (CIMI)}.
+	\newblock Accessed:2021-06-05.
+
+	\bibitem{Satti2020}
+	Fahad~Ahmed Satti, Taqdir Ali, Jamil Hussain, Wajahat~Ali Khan, Asad~Masood
+	Khattak, and Sungyoung Lee.
+	\newblock {Ubiquitous Health Profile (UHPr): a big data curation platform for
+		supporting health data interoperability}.
+	\newblock {\em Computing}, 2020.
+
+	\bibitem{althubaiti2020combining}
+	Sara Althubaiti, {\c{S}}enay Kafkas, Marwa Abdelhakim, and Robert Hoehndorf.
+	\newblock Combining lexical and context features for automatic ontology
+	extension.
+	\newblock {\em Journal of biomedical semantics}, 11(1):1--13, 2020.
+
+	\bibitem{nozaki2019semantic}
+	Kenji Nozaki, Teruhisa Hochin, and Hiroki Nomiya.
+	\newblock Semantic schema matching for string attribute with word vectors.
+	\newblock In {\em 2019 6th International Conference on Computational
+		Science/Intelligence and Applied Informatics (CSII)}, pages 25--30. IEEE,
+	2019.
+
+	\bibitem{yousfi2020xmatcher}
+	Aola Yousfi, Moulay~Hafid El~Yazidi, and Ahmed Zellou.
+	\newblock xmatcher: Matching extensible markup language schemas using
+	semantic-based techniques.
+	\newblock {\em International Journal of Advanced Computer Science and
+		Applications}, 11(8):655--665, 2020.
+
+	\bibitem{bulygin2018combining}
+	Lev Bulygin.
+	\newblock Combining lexical and semantic similarity measures with machine
+	learning approach for ontology and schema matching problem.
+	\newblock In {\em Proceedings of the XX International Conference “Data
+		Analytics and Management in Data Intensive Domains”(DAMDID/RCDL’2018)},
+	pages 245--249, 2018.
+
+	\bibitem{martono2017review}
+	Galih~Hendro Martono and SN~Azhari.
+	\newblock Review implementation of linguistic approach in schema matching.
+	\newblock {\em International Journal of Advances in Intelligent Informatics},
+	3(1):1--9, 2017.
+
+	\bibitem{alwan2017survey}
+	Ali~A Alwan, Azlin Nordin, Mogahed Alzeber, and Abedallah~Zaid Abualkishik.
+	\newblock A survey of schema matching research using database schemas and
+	instances.
+	\newblock {\em International Journal of Advanced Computer Science and
+		Applications}, 8(10), 2017.
+
+	\bibitem{kersloot2020natural}
+	Martijn~G Kersloot, Florentien~JP van Putten, Ameen Abu-Hanna, Ronald Cornet,
+	and Derk~L Arts.
+	\newblock Natural language processing algorithms for mapping clinical text
+	fragments onto ontology concepts: a systematic review and recommendations for
+	future studies.
+	\newblock {\em Journal of biomedical semantics}, 11(1):1--21, 2020.
+
+	\bibitem{xu2003discovering}
+	Li~Xu and David~W Embley.
+	\newblock Discovering direct and indirect matches for schema elements.
+	\newblock In {\em Eighth International Conference on Database Systems for
+		Advanced Applications, 2003.(DASFAA 2003). Proceedings.}, pages 39--46. IEEE,
+	2003.
+
+	\bibitem{zhu2018exploring}
+	Xunjie Zhu, Tingfeng Li, and Gerard De~Melo.
+	\newblock Exploring semantic properties of sentence embeddings.
+	\newblock In {\em Proceedings of the 56th Annual Meeting of the Association for
+		Computational Linguistics (Volume 2: Short Papers)}, pages 632--637, 2018.
+
+	\bibitem{kartoun2016methodology}
+	Uri Kartoun.
+	\newblock A methodology to generate virtual patient repositories.
+	\newblock {\em arXiv preprint arXiv:1608.00570}, 2016.
+
+	\bibitem{pan2016design}
+	Lijun Pan, Xiaoting Fu, Fangfang Cai, Yu~Meng, and Changjiang Zhang.
+	\newblock Design a novel electronic medical record system for regional clinics
+	and health centers in china.
+	\newblock In {\em 2016 2nd IEEE International Conference on Computer and
+		Communications (ICCC)}, pages 38--41. IEEE, 2016.
+
+	\bibitem{inokuchi2007medtakmi}
+	Akihiro Inokuchi, Koichi Takeda, Noriko Inaoka, and Fumihiko Wakao.
+	\newblock Medtakmi-cdi: interactive knowledge discovery for clinical decision
+	intelligence.
+	\newblock {\em IBM Systems Journal}, 46(1):115--133, 2007.
+
+	\bibitem{ali2017reconciliation}
+	Taqdir Ali and Sungyoung Lee.
+	\newblock Reconciliation of snomed ct and domain clinical model for
+	interoperable medical knowledge creation.
+	\newblock In {\em 2017 39th Annual International Conference of the IEEE
+		Engineering in Medicine and Biology Society (EMBC)}, pages 2654--2657. IEEE,
+	2017.
+
+	\bibitem{reimers-2019-sentence-bert}
+	Nils Reimers and Iryna Gurevych.
+	\newblock Sentence-bert: Sentence embeddings using siamese bert-networks.
+	\newblock In {\em Proceedings of the 2019 Conference on Empirical Methods in
+		Natural Language Processing}. Association for Computational Linguistics, 11
+	2019.
+
+	\bibitem{chicco2020advantages}
+	Davide Chicco and Giuseppe Jurman.
+	\newblock The advantages of the matthews correlation coefficient (mcc) over f1
+	score and accuracy in binary classification evaluation.
+	\newblock {\em BMC genomics}, 21(1):1--13, 2020.
+
+	\bibitem{gwet2014handbook}
+	Kilem~L Gwet.
+	\newblock {\em Handbook of inter-rater reliability: The definitive guide to
+		measuring the extent of agreement among raters}.
+	\newblock Advanced Analytics, LLC, 2014.
+
+	\bibitem{FuzzyWuzzy}
+	{Adam Cohen}.
+	\newblock Fuzzywuzzy: Fuzzy string matching in python, Jul 8th, 2011.
+
+	\bibitem{mchugh2012interrater}
+	Mary~L McHugh.
+	\newblock Interrater reliability: the kappa statistic.
+	\newblock {\em Biochemia medica}, 22(3):276--282, 2012.
+
+	\bibitem{reidsma2008exploiting}
+	Dennis Reidsma and Rieks op~den Akker.
+	\newblock Exploiting ‘subjective’annotations.
+	\newblock In {\em Coling 2008: Proceedings of the workshop on Human Judgements
+		in Computational Linguistics}, pages 8--16, 2008.
+
+	\bibitem{velupillai2010towards}
+	Sumithra Velupillai.
+	\newblock Towards a better understanding of uncertainties and speculations in
+	swedish clinical text--analysis of an initial annotation trial.
+	\newblock In {\em Proceedings of the Workshop on Negation and Speculation in
+		Natural Language Processing}, pages 14--22, 2010.
+
+	\bibitem{Joshi2018}
+	Mohit Joshi and Payal Bhardwaj.
+	\newblock {Impact of data transparency: Scientific publications}.
+	\newblock {\em Perspectives in Clinical Research}, 9(1):31--36, 2018.
+
+	\bibitem{pavlick2019inherent}
+	Ellie Pavlick and Tom Kwiatkowski.
+	\newblock Inherent disagreements in human textual inferences.
+	\newblock {\em Transactions of the Association for Computational Linguistics},
+	7:677--694, 2019.
+
+	\bibitem{espindola2005extending}
+	Rog{\'e}rio~P Esp{\'\i}ndola and Nelson~FF Ebecken.
+	\newblock On extending f-measure and g-mean metrics to multi-class problems.
+	\newblock {\em WIT Transactions on Information and Communication Technologies},
+	35, 2005.
+
+	\bibitem{moll2020oncology}
+	Jonas Moll and {\AA}sa Cajander.
+	\newblock Oncology health-care professionals’ perceived effects of patient
+	accessible electronic health records 6 years after launch: a survey study at
+	a major university hospital in sweden.
+	\newblock {\em Health informatics journal}, 26(2):1392--1403, 2020.
+
+\end{thebibliography}
 
@@
 \end{IEEEbiography}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{prof_tcc.jpg}}]{Tae-Choong Chung}  received his B.S.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{prof_tcc.jpg}}]{TaeChoong Chung}  received his B.S.
 degree in Electronic Engineering from Seoul National University, Republic of Korea, in 1980, and his M.S.

### 2021-08-04 Implementation/AnnotatedDataHandler_4.py
kappa score

@@ -92,9 +92,10 @@ class AnnotatedDataHandler:
         # self.result_indexes = ["0.0-1.0", "0.1-0.9", "0.2-0.8", "0.3-0.7", "0.4-0.6", "0.5-0.5", "0.6-0.4", "0.7-0.3",
         #                        "0.8-0.2", "0.9-0.1"]
         self.result_indexes = ["0.0-1.0"]
-        self.computational_iteration = "1.7"
-        self.result_iteration = ".5"
-        self.notSynAndSem = ["FUZZY_MATCH", "Word2Vec"]
+        self.computational_iteration = "4.0"
+        self.result_iteration = "4.0"
+        #self.notSynAndSem = ["FUZZY_MATCH", "Word2Vec"]
+        self.notSynAndSem = []
         self.computed_method = ['bert-base-nli-stsb-mean-tokens',
                                 'bert-large-nli-stsb-mean-tokens',
                                 'roberta-base-nli-stsb-mean-tokens',
@@ -351,11 +352,11 @@ class AnnotatedDataHandler:
                                                                                                  _thresholds)
         # Read other methods
         # annotatedDataHandler.log(['-'] * 80)
-        for model in self.notSynAndSem:
-            syn_sem_threshold = "0-0"
-            self.computed_data[model][syn_sem_threshold] = self.read_computed_data_for_model(model, read_headers,
-                                                                                             syn_sem_threshold,
-                                                                                             _thresholds)
+        # for model in self.notSynAndSem:
+        #     syn_sem_threshold = "0-0"
+        #     self.computed_data[model][syn_sem_threshold] = self.read_computed_data_for_model(model, read_headers,
+        #                                                                                      syn_sem_threshold,
+        #                                                                                      _thresholds)
         # annotatedDataHandler.log(['*'] * 80)
 
     def calculate_pearson_score_between_annotators(self):
@@ -915,7 +916,7 @@ annotatedDataHandler = AnnotatedDataHandler()
 # Now to convert the datasets into 1d
 annotatedDataHandler.readAllAnnotatorsData(True)
 annotatedDataHandler.calculateKappaScoreBetweenAnnotators()
-exit()
+#exit()
 
 
 
@@ -950,7 +951,6 @@ annotatedDataHandler.read_all_computed_data(read_headers=True)
 
[…]
